### 2024-07-22 main_morse_response_functions.tex
add abstract

\documentclass[12pt]{article}

\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
\usepackage{amssymb}
\usepackage{physics}
%\usepackage{cite} % may be useful for different formats of numerical citation
\usepackage{hyperref} % for hyperlinks in references

\usepackage{caption} % for \caption*

\textwidth 160mm
\textheight 230mm
\voffset = -20mm

\title{Thermodynamic response functions in a cell fluid model}

\author{O.A.Dobush, M.P.Kozlovskii, R.V.~Romanik
	\\ \small Institute for Condensed Matter Physics, NAS of Ukraine 
	\\ \small 1~Svientsitskii Street, 79011, Lviv, Ukraine 
	\\ \small romanik@icmp.lviv.ua}
%\author{R.V.~Romanik \\ Institute for Condensed Matter Physics, NAS of Ukraine}

\begin{document}

	\maketitle

	%\begin{multicols}{2}

	\abstract{Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential. These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble. The calculated quantities are presented graphically as functions of density and chemical potential.
	\\	
	\textbf{Keywords:} Simple fluids, Morse potential, Thermodynamic response functions.
	}
	\section{Introduction}

	%\bibliographystyle{cmpj} % still looking for the best style
	%\bibliography{fluids_general} % BibTeX / BibLaTeX should be used

\end{document}

### 2024-07-22 main_morse_response_functions.tex
add intro, potential overview, structure by sections, and pressure figures

@@
 
+	In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~[Kozytskii et al.
+(2018); Kozytskii et al.
+(2020)].
+In~[Kozlovskii $\&$ Dobush (2020); Pylyuk $\&$ Dobush (2020); Pylyuk at al., J.
+Mol.
+Liq.
+(2023); Pylyuk at al., Ukr.
+J.
+Phys.
+(2023)] this model was used with a modified Morse potential describing the particle interaction.
+In particular, the equation of state was obtained in~[Kozlovskii $\&$ Dobush (2020)] in the zero-mode approximation.
+This equation of state is used in the current work to calculate thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient.
+
+	\section{The interaction potential}
+	The potential of interaction between particles is taken in a form of a modified Morse potential
+	\begin{equation}
+		U(r) = C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
+	\end{equation}
+	where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model.
+Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
+	\begin{equation*}
+		C_{H} = \frac{\varepsilon n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
+	\end{equation*}
+	where $\varepsilon$ is the depth of the potential well at $r=R_0$.
+This potential is reduced to the ordinary Morse potential~[Morse (1929)] at $\gamma=2$.
+For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~[Kozlovskii $\&$ Dobush (2020)].
+
+	Modifications of the Morse potential were used in other works as well.
+For example, in~[Martinez-Valencia at al.
+(2013)] a repulsive term in a form of a power of $r^{-1}$ was added to the ordinary Morse potential, and the influence of the softness of such a term was investigated on the coordinates of the critical point.
+The generalized form of the Morse potential was suggested in~[Biswas $\&$ Hamann (1985)]
+	\begin{equation}
+		U(r) = A_1 {\rm e}^{-\lambda_1 r} + A_2 {\rm e}^{-\lambda_2 r}
+	\end{equation} 
+	with application to silicon structural energies, and was also considered in~[Lim, Acta Chim. Slov. (2005)] as the potential for Be-S and H-Na compounds.
+
+	Our modification contains an additional repulsive term, similar to~[Martinez-Valencia at al.
+(2013)], as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential.
+Including the repulsive term enables us to single out a reference system and apply the method of collective variables to calculating the grand partition function~[REFERENCE NEEDED].
+
+	\section{The equation of state}
+	The equation of state obtained in [Kozlovskii $\&$ Dobush (2020)] reads
+	\begin{equation}
+		\label{eq:eos}
+		Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
+	\end{equation}
+
+	[EXPLICIT EXPRESSIONS FOR QUANTITIES ENTERING THE EQUATION OF STATE FOLLOW HERE OR REFERENCE IS MADE TO AN APPENDIX].
+
+	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state~\eqref{eq:eos}
+	\begin{figure}[h!]
+		\centering \includegraphics[width=0.446\textwidth]{f1a1.pdf} 
+		\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
+		\vskip-3mm\caption{Plots of isotherms of the pressure $P$ as a function of the density $\bar n$ (on the lefthand side) and a function of the effective chemical potential $M$ (on the righthand side) at $T \geq T_c$ represented by black lines.
+Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from \cite{refa}.
+		}\label{fig1}
+	\end{figure}
+
+	\section{Thermodynamic response functions (coefficients)}
+
+	\subsection{Isothermal compressibility}
+	The isothermal compressibility is defined by
+	\begin{equation}
+		\label{def:isotherm_compres}
+		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_T
+	\end{equation}
+
+	\subsection{Thermal pressure coefficient}
+	The thermal pressure coefficient is defined by
+	\begin{equation}
+		\label{def:therm_pres_coef}
+		\beta_V = \left( \frac{\partial P}{\partial T} \right)_V
+	\end{equation}
+
+	\subsection{Thermal expansion coefficient}
+	The thermal expansion coefficient is defined by
+	\begin{equation}
+		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_P
+	\end{equation}
+
+	\section{Conclusions}
+
 	%\bibliographystyle{cmpj} % still looking for the best style

### 2024-07-22 main_morse_response_functions.tex
add compressibility figures

@@
 		\vskip-3mm\caption{Plots of isotherms of the pressure $P$ as a function of the density $\bar n$ (on the lefthand side) and a function of the effective chemical potential $M$ (on the righthand side) at $T \geq T_c$ represented by black lines.
-Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from \cite{refa}.
+Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from [Kozlovskii $\&$ Dobush (2020)].
 		}\label{fig1}
@@
 	\end{equation}
+
+	\begin{figure}[h!]
+		\centering \includegraphics[width=0.5\textwidth]{f2a.pdf}
+		\vskip-3mm\caption{The isothermal compressibility $K_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
+		}\label{fig2a}
+	\end{figure}
+
+	\begin{figure}[h!]
+		\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
+		\includegraphics[width=0.475\textwidth]{f2c.pdf}
+		\vskip-3mm\caption{The isothermal compressibility $K_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+The two figures differ in the scale of $M$.
+The left-hand side figure covers a wider range of $M$, while the right-hand side one focuses on a range of $M$ around its critical value $0$.
+		}\label{fig2b}
+	\end{figure}
 

### 2024-07-22 main_morse_response_functions.tex
add thermal pressure coefficient figure

@@
 The two figures differ in the scale of $M$.
-The left-hand side figure covers a wider range of $M$, while the right-hand side one focuses on a range of $M$ around its critical value $0$.
+The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
 		}\label{fig2b}
@@
 	\end{equation}
+
+	\begin{figure}[h!]
+		\centering \includegraphics[width=0.5\textwidth]{f3.pdf}
+		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
+		}\label{fig3}
+	\end{figure}
 

### 2024-07-23 main_morse_response_functions.tex
add termal expansion coefficient figure
add package graphicx

@@
 
-\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
+%\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
 \usepackage{amssymb}
-\usepackage{physics}
+%\usepackage{physics}
 %\usepackage{cite} % may be useful for different formats of numerical citation
@@
 \usepackage{caption} % for \caption*
+
+%**************
+\usepackage[pdftex]{graphicx}
+%**************
 
@@
 Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
-	\begin{equation*}
+	\begin{equation}
 		C_{H} = \frac{\varepsilon n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
-	\end{equation*}
+	\end{equation}
 	where $\varepsilon$ is the depth of the potential well at $r=R_0$.
@@
 
-	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state~\eqref{eq:eos}
+	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state~\ref{eq:eos}
 	\begin{figure}[h!]
-		\centering \includegraphics[width=0.446\textwidth]{f1a1.pdf} 
+		%\centering 
+		\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
 		\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
@@
 
+	\begin{figure}[h!]
+		\centering \includegraphics[width=0.5\textwidth]{f4.pdf}
+		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
+		}\label{fig4}
+	\end{figure}
+
 	\section{Conclusions}

### 2024-07-23 main_morse_response_functions.tex
start conclusions
add extracted.bib file

@@
 %**************
-\usepackage[pdftex]{graphicx}
+\usepackage{graphicx}
 %**************
@@
 
-	In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~[Kozytskii et al.
-(2018); Kozytskii et al.
-(2020)].
-In~[Kozlovskii $\&$ Dobush (2020); Pylyuk $\&$ Dobush (2020); Pylyuk at al., J.
-Mol.
-Liq.
-(2023); Pylyuk at al., Ukr.
-J.
-Phys.
-(2023)] this model was used with a modified Morse potential describing the particle interaction.
-In particular, the equation of state was obtained in~[Kozlovskii $\&$ Dobush (2020)] in the zero-mode approximation.
+	In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}.
+In works~\cite{KozlovskiiDobush2020,PylyukDobush2020,PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} this model was used with a modified Morse potential describing the particle interaction.
+In particular, the equation of state was obtained in~\cite{KozlovskiiDobush2020} in the zero-mode approximation.
 This equation of state is used in the current work to calculate thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient.
@@
 	where $\varepsilon$ is the depth of the potential well at $r=R_0$.
-This potential is reduced to the ordinary Morse potential~[Morse (1929)] at $\gamma=2$.
-For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~[Kozlovskii $\&$ Dobush (2020)].
+This potential is reduced to the ordinary Morse potential~\cite{Morse1929} at $\gamma=2$.
+For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~\cite{KozlovskiiDobush2020}.
 
 	Modifications of the Morse potential were used in other works as well.
-For example, in~[Martinez-Valencia at al.
-(2013)] a repulsive term in a form of a power of $r^{-1}$ was added to the ordinary Morse potential, and the influence of the softness of such a term was investigated on the coordinates of the critical point.
-The generalized form of the Morse potential was suggested in~[Biswas $\&$ Hamann (1985)]
+For example, in~\cite{MartinezValenciaEtAl2013} a repulsive term in a form of a power of $r^{-1}$ was added to the ordinary Morse potential, and the influence of the softness of such a term was investigated on the coordinates of the critical point.
+The generalized form of the Morse potential was suggested in~\cite{BiswasHamann1985}
 	\begin{equation}
@@
 	\end{equation} 
-	with application to silicon structural energies, and was also considered in~[Lim, Acta Chim. Slov. (2005)] as the potential for Be-S and H-Na compounds.
+	with application to silicon structural energies, and was also considered in~\cite{Lim2005} as the potential for Be-S and H-Na compounds.
 
-	Our modification contains an additional repulsive term, similar to~[Martinez-Valencia at al.
-(2013)], as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential.
+	Our modification contains an additional repulsive term, similar to~\cite{MartinezValenciaEtAl2013}, as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential.
 Including the repulsive term enables us to single out a reference system and apply the method of collective variables to calculating the grand partition function~[REFERENCE NEEDED].
@@
 	\section{The equation of state}
-	The equation of state obtained in [Kozlovskii $\&$ Dobush (2020)] reads
+	The equation of state obtained in~\cite{KozlovskiiDobush2020} reads
 	\begin{equation}
@@
 		\vskip-3mm\caption{Plots of isotherms of the pressure $P$ as a function of the density $\bar n$ (on the lefthand side) and a function of the effective chemical potential $M$ (on the righthand side) at $T \geq T_c$ represented by black lines.
-Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from [Kozlovskii $\&$ Dobush (2020)].
+Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
 		}\label{fig1}
@@
 	\section{Conclusions}
+	Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
 
-	%\bibliographystyle{cmpj} % still looking for the best style
-	%\bibliography{fluids_general} % BibTeX / BibLaTeX should be used
+	\bibliographystyle{cmpj} % still looking for the best style
+	%\bibliography{fluids_general,fluids_cv} % BibTeX / BibLaTeX should be used
+	\bibliography{extracted}
 

### 2024-07-24 main_morse_response_functions.tex
remove abstracts from extracted.bib; set bibliographystyle to elsarticle-num
add smth to eos section, need more

--- 2024-07-23 main_morse_response_functions.tex
@@
 \usepackage[pdftex]{graphicx}
+\usepackage{amsmath}    % for "\eqref" macro
 %**************
@@
 	\end{equation}
-
 	[EXPLICIT EXPRESSIONS FOR QUANTITIES ENTERING THE EQUATION OF STATE FOLLOW HERE OR REFERENCE IS MADE TO AN APPENDIX].
+	The latter expression links the pressure $P$, the temperature $T$ ($\beta = 1/T$ is the inverse temperature), the cell's volume $v$ and the effective chemical potential $M$.
+In general $M$ is a function of the real chemical potential $\mu$:
+	\begin{align}
+		&	M = \frac{\tilde\mu}{W(0)} + g_1 + n_c \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
+		&	\tilde\mu=\mu-\mu^*(1+\tau),
+	\end{align}
+	here $\mu^*$ is some positive constant, and $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$,
+	$T_c$ is the critical temperature. $W(0)$ is what we call an effective interaction potential\footnote{\textbf{explain} what is the effective interaction potential in a few words} at ${\bf k} = 0$:
+	\begin{equation}
+	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right].
+	\end{equation}
+	Here $\chi_0$ is a constant parameter, the quantities $B$ and $A_\gamma$ reads
+	\begin{align} 
+		& B = 2 \gamma^3 e^{(1-\gamma)/\alpha},\nonumber \\
+		& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3.
+	\end{align}
+	The coefficients $g_n$ are given by the formulas:
+	\begin{align}
+		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
+		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2,
+	\end{align}
+	where $T_n(p,\alpha^*)$ are the following special functions
+	\begin{equation}
+	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
+	\end{equation}
+	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
+	\begin{equation}
+	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
+	\end{equation} 
+	Note that we denote $\beta_c$ as the inverse critical temperature.
+Since $p$ fails to be the function of temperature, the coefficients $g_n$ are also temperature-free.
+The quantity $\tilde D(0)$ which has already appeared in both equations \eqref{eq:eos} and \eqref{3d2} is a function of temperature
+	\begin{equation}
+	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)},
+	\end{equation}
+	which equals zero at $T=T_c$. This circumstance gives us an expression for determining the critical temperature 
+	\begin{equation}
+		T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
+	\end{equation}    
+	The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by
+	\begin{align}
+		& E_\mu (M, T) = - \frac{1}{2 N_v} \ln (2\pi \beta W(0)) +  g_0 - \frac{\beta W(0)}{2} \!\!
+\left( \!
+\frac{\tilde\mu}{W(0)} \!
+\right)^{\!
+2} \!\!\!
+- \frac{g_3}{g_4} {M} \!
+- \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}.
+	\end{align}
+	Note that for all $ \tau> 0 $ there are no restrictions on the value of $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
+	\begin{equation}\label{2d18}
+	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
+	\end{equation}
+	where
+	\begin{equation}
+	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3\bar{M}}{g_4}\right)^2, \qquad g_4<0.
+	\end{equation}  
+	...
+	\begin{equation}\label{3d3}
+	\bar n = n_g - \bar{M} + \tilde g_2 \gamma_\tau \bar \rho_0,
+	\end{equation}
+	where
+	\begin{equation}\label{3d4}
+	n_g = g_1 + n_c \tilde g_2 - \frac{1}{6} g_3^3 / g_4^2.
+	\end{equation}
+	...
 
@@
 	\section{Conclusions}
+	Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
 

### 2024-07-24 main_morse_response_functions.tex

--- 2024-07-23 main_morse_response_functions.tex
@@
 %**************
+%<<<<<<< HEAD
+\usepackage[pdftex]{graphicx}
+\usepackage{amsmath}    % for "\eqref" macro
+%=======
 \usepackage{graphicx}
+%>>>>>>> 3a31f0b6bd43223c1786eb91b76133393bfa7c2a
 %**************
@@
 	\end{equation}
-
 	[EXPLICIT EXPRESSIONS FOR QUANTITIES ENTERING THE EQUATION OF STATE FOLLOW HERE OR REFERENCE IS MADE TO AN APPENDIX].
+	The latter expression links the pressure $P$, the temperature $T$ ($\beta = 1/T$ is the inverse temperature), the cell's volume $v$ and the effective chemical potential $M$.
+In general $M$ is a function of the real chemical potential $\mu$:
+	\begin{align}\label{chem_pot}
+		&	M = \frac{\tilde\mu}{W(0)} + g_1 + n_c \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
+		&	\tilde\mu=\mu-\mu^*(1+\tau),
+	\end{align}
+	here $\mu^*$ is some positive constant, and $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$,
+	$T_c$ is the critical temperature. $W(0)$ is what we call an effective interaction potential\footnote{\textbf{explain} what is the effective interaction potential in a few words} at ${\bf k} = 0$:
+	\begin{equation}
+	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right].
+	\end{equation}
+	Here $\chi_0$ is a constant parameter, the quantities $B$ and $A_\gamma$ reads
+	\begin{align} 
+		& B = 2 \gamma^3 e^{(1-\gamma)/\alpha},\nonumber \\
+		& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3.
+	\end{align}
+	The coefficients $g_n$ are given by the formulas:
+	\begin{align}
+		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
+		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2,
+	\end{align}
+	where $T_n(p,\alpha^*)$ are the following special functions
+	\begin{equation}
+	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
+	\end{equation}
+	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
+	\begin{equation}
+	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
+	\end{equation} 
+	Note that we denote $\beta_c$ as the inverse critical temperature.
+Since $p$ fails to be the function of temperature, the coefficients $g_n$ are also temperature-free.
+The quantity $\tilde D(0)$ which has already appeared in both equations \eqref{eq:eos} and \eqref{chem_pot} is a function of temperature
+	\begin{equation}
+	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)},
+	\end{equation}
+	which equals zero at $T=T_c$. This circumstance gives us an expression for determining the critical temperature 
+	\begin{equation}
+		T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
+	\end{equation}    
+	The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by
+	\begin{align}
+		& E_\mu (M, T) = - \frac{1}{2 N_v} \ln (2\pi \beta W(0)) +  g_0 - \frac{\beta W(0)}{2} \!\!
+\left( \!
+\frac{\tilde\mu}{W(0)} \!
+\right)^{\!
+2} \!\!\!
+- \frac{g_3}{g_4} {M} \!
+- \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}.
+	\end{align}
+	Note that for all $ \tau> 0 $ there are no restrictions on the value of $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
+	\begin{equation}\label{2d18}
+	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
+	\end{equation}
+	where
+	\begin{equation}
+	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3\bar{M}}{g_4}\right)^2, \qquad g_4<0.
+	\end{equation}  
+	...
+	\begin{equation}\label{3d3}
+	\bar n = n_g - \bar{M} + \tilde g_2 \gamma_\tau \bar \rho_0,
+	\end{equation}
+	where
+	\begin{equation}\label{3d4}
+	n_g = g_1 + n_c \tilde g_2 - \frac{1}{6} g_3^3 / g_4^2.
+	\end{equation}
+	...
 
@@
 
-	\bibliographystyle{cmpj} % still looking for the best style
+	%\bibliographystyle{cmpj} % still looking for the best style
+	\bibliographystyle{elsarticle-num}
+	%\bibliographystyle{unsrturl}
 	%\bibliography{fluids_general,fluids_cv} % BibTeX / BibLaTeX should be used

### 2024-07-31 main_morse_response_functions.tex
update text after equation of state

@@
 \usepackage{amssymb}
-%\usepackage{physics}
+\usepackage{physics}
 %\usepackage{cite} % may be useful for different formats of numerical citation
@@
 	\begin{equation}
+		\label{def:mod_morse}
 		U(r) = C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
@@
 	\end{equation}
-	[EXPLICIT EXPRESSIONS FOR QUANTITIES ENTERING THE EQUATION OF STATE FOLLOW HERE OR REFERENCE IS MADE TO AN APPENDIX].
-	The latter expression links the pressure $P$, the temperature $T$ ($\beta = 1/T$ is the inverse temperature), the cell's volume $v$ and the effective chemical potential $M$.
-In general $M$ is a function of the real chemical potential $\mu$:
+	The quantities in the left-hand side of the equation are $P$, the pressure; $\beta$, the inverse temperature; $v$, cell volume.
+The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential $\mu$.
+Let us present their expressions explicitly.
+
+	First, the quantity $M$ depends linearly on the chemical potential
 	\begin{align}\label{chem_pot}
@@
 	\end{align}
-	here $\mu^*$ is some positive constant, and $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$,
-	$T_c$ is the critical temperature. $W(0)$ is what we call an effective interaction potential\footnote{\textbf{explain} what is the effective interaction potential in a few words} at ${\bf k} = 0$:
+	where $\mu^*$ is some positive constant, $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$, $T_c$ is the critical temperature. We will call $M$ the effective chemical potential.
+
+	The quantity $W(0)$ is expressed via parameters of the potential~(\ref{def:mod_morse}) as follows
 	\begin{equation}
-	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right].
+	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right],
 	\end{equation}
-	Here $\chi_0$ is a constant parameter, the quantities $B$ and $A_\gamma$ reads
+	where
 	\begin{align} 
 		& B = 2 \gamma^3 e^{(1-\gamma)/\alpha},\nonumber \\
-		& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3.
+		& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3,
 	\end{align}
+	and $\Phi^{(r)}(0)$ is the Fourier transform of the repulsive part of the potential at $\abs{\vb k}=0$.
+The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a term in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$.
+
 	The coefficients $g_n$ are given by the formulas:
@@
 
-	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state~\ref{eq:eos}
+	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state~(\ref{eq:eos})
 	\begin{figure}[h!]

### 2024-08-07 main_morse_response_functions.tex
describe coefficients entering eos

@@
 
-%**************
-%<<<<<<< HEAD
-\usepackage[pdftex]{graphicx}
 \usepackage{amsmath}    % for "\eqref" macro
-%=======
 \usepackage{graphicx}
-%>>>>>>> 3a31f0b6bd43223c1786eb91b76133393bfa7c2a
-%**************
 
@@
 		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
-		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2,
+		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, \\
+		& n_c = -g_3/g_4, \nonumber
 	\end{align}
@@
 	\end{equation} 
-	Note that we denote $\beta_c$ as the inverse critical temperature.
-Since $p$ fails to be the function of temperature, the coefficients $g_n$ are also temperature-free.
-The quantity $\tilde D(0)$ which has already appeared in both equations \eqref{eq:eos} and \eqref{chem_pot} is a function of temperature
+	The quantity $\beta_c$ denotes the critical value of the inverse temperature.
+	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature.
+The quantity $\tilde D(0)$ entering equations~\eqref{eq:eos} and~\eqref{chem_pot} is a function of temperature
 	\begin{equation}
-	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)},
+	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
 	\end{equation}
-	which equals zero at $T=T_c$. This circumstance gives us an expression for determining the critical temperature 
+	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite{KozlovskiiDobush2020}
 	\begin{equation}
@@
 	\end{equation}
+
 	The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by

### 2024-08-07 main_morse_response_functions.tex
add numerical values for coefficients alpha, gamma, n_0
add new figures to the text

--- 2024-07-31 main_morse_response_functions.tex
@@
 
-%\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
+\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
 \usepackage{amssymb}
 \usepackage{physics}
-%\usepackage{cite} % may be useful for different formats of numerical citation
+\usepackage{cite} % may be useful for different formats of numerical citation
 \usepackage{hyperref} % for hyperlinks in references
@@
 %**************
-%<<<<<<< HEAD
-\usepackage[pdftex]{graphicx}
-\usepackage{amsmath}    % for "\eqref" macro
-%=======
+%\usepackage[pdftex]{graphicx}
+%\usepackage{amsmath}    % for "\eqref" macro
 \usepackage{graphicx}
-%>>>>>>> 3a31f0b6bd43223c1786eb91b76133393bfa7c2a
 %**************
@@
 		\label{def:isotherm_compres}
-		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_T
+		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,<N>}
 	\end{equation}
@@
 		\label{def:therm_pres_coef}
-		\beta_V = \left( \frac{\partial P}{\partial T} \right)_V
+		\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,<N>}
 	\end{equation}
@@
 	\begin{figure}[h!]
-		\centering \includegraphics[width=0.5\textwidth]{f3.pdf}
-		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
-		}\label{fig3}
+		\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
+		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+		}\label{fig3a}
+	\end{figure}
+	\begin{figure}[h!]
+		\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
+		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+		}\label{fig3b}
+	\end{figure}
+	\begin{figure}[h!]
+		\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
+		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the relative temperature $\tau$ at different values of the density $\eta$. 
+		}\label{fig3c}
 	\end{figure}
@@
 	\begin{equation}
-		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_P
+		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,<N>}
 	\end{equation}
@@
 	\begin{figure}[h!]
-		\centering \includegraphics[width=0.5\textwidth]{f4.pdf}
-		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
-		}\label{fig4}
+		\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
+		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+		}\label{fig4a}
 	\end{figure}
+
+		\begin{figure}[h!]
+		\centering \includegraphics[width=0.45\textwidth]{f4b.pdf}
+		\includegraphics[width=0.475\textwidth]{f4c.pdf}
+		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+The two figures differ in the scale of $M$.
+The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
+		}\label{fig4b}
+	\end{figure}
+
+	\newpage
 

### 2024-08-07 main_morse_response_functions.tex

@@
 \usepackage{hyperref} % for hyperlinks in references
-
 \usepackage{caption} % for \caption*
-
-%**************
-%\usepackage[pdftex]{graphicx}
-%\usepackage{amsmath}    % for "\eqref" macro
+\usepackage{amsmath}    % for "\eqref" macro
 \usepackage{graphicx}
-%**************
 
@@
 	\end{equation} 
-	Note that we denote $\beta_c$ as the inverse critical temperature.
-Since $p$ fails to be the function of temperature, the coefficients $g_n$ are also temperature-free.
-The quantity $\tilde D(0)$ which has already appeared in both equations \eqref{eq:eos} and \eqref{chem_pot} is a function of temperature
+	The quantity $\beta_c$ denotes the critical value of the inverse temperature.
+	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature.
+The numerical values for other coefficients used in this paper are the same as those in~\cite{KozlovskiiDobush2020}:
+	\begin{equation*}
+		\alpha^* = 5.0, \quad \gamma = 1.65, \quad n_0 = 1.521.
+	\end{equation*}
+
+	The quantity $\tilde D(0)$ entering equations~\eqref{eq:eos} and~\eqref{chem_pot} is a function of temperature
 	\begin{equation}
-	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)},
+	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
 	\end{equation}
-	which equals zero at $T=T_c$. This circumstance gives us an expression for determining the critical temperature 
+	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite{KozlovskiiDobush2020}
 	\begin{equation}

### 2024-08-10 main_morse_response_functions.tex
introduced density and eos in terms of density and temperature, needs refinement

@@
 	\begin{equation}
-		\label{eq:eos}
+		\label{eq:eosMT}
 		Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
@@
 	\begin{align}\label{chem_pot}
-		&	M = \frac{\tilde\mu}{W(0)} + g_1 + n_c \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
+		&	M = \frac{\tilde\mu}{W(0)} + g_1 - \frac{g_3}{g_4} \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
 		&	\tilde\mu=\mu-\mu^*(1+\tau),
@@
 		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
-		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, \\
-		& n_c = -g_3/g_4, \nonumber
+		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, 
 	\end{align}
@@
 
-	The quantity $\tilde D(0)$ entering equations~\eqref{eq:eos} and~\eqref{chem_pot} is a function of temperature
+	The quantity $\tilde D(0)$ entering equations~\eqref{eq:eosMT} and~\eqref{chem_pot} is a function of temperature
 	\begin{equation}
@@
 
-	The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by
+	The function $E_\mu(M, T)$ from the equation \eqref{eq:eosMT} is provided by
 	\begin{align}
-		& E_\mu (M, T) = - \frac{1}{2 N_v} \ln (2\pi \beta W(0)) +  g_0 - \frac{\beta W(0)}{2} \!\!
+		& E_\mu (M, T) = - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 - \frac{\beta W(0)}{2} \!\!
 \left( \!
@@
 	\end{align}
-	Note that for all $ \tau> 0 $ there are no restrictions on the value of $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
-	\begin{equation}\label{2d18}
+	The connection between the effective chemical potential $M$ and the quantity $ \bar \rho_0 $ follows from the cubic equation
+	\begin{equation}\label{eq:ro_M}
+	\bar M + \tilde D(0) \bar\rho_0 - \frac{a_4}{6} \bar\rho_0^3 = 0,
+	\end{equation}
+	Note that for all $ \tau> 0 $ the later equation has one real root.
+Consequently, there are no restrictions on the value of the quantity $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
+	\begin{equation}\label{eq:ro_MT}
 	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
@@
 	\end{equation}  
-	...
-	\begin{equation}\label{3d3}
-	\bar n = n_g - \bar{M} + \tilde g_2 \gamma_\tau \bar \rho_0,
+	........................................................
+
+	The density of the many-particle system is the ratio of the average number of particles $\left\langle N \right\rangle$  to the total volume of the system $V$.
+	In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to the product $\beta \mu$.
+Using the general relation for the equation of state $PV\beta = \ln \Xi $ the density reads
+	\begin{equation}
+	\eta = \frac{<N>}{v N_v} = \frac{1}{v} \frac{\partial}{\partial\beta\mu} Pv\beta = \frac{\bar n}{v},
 	\end{equation} 
 	where	
-	\begin{equation}\label{3d4}
-	n_g = g_1 + n_c \tilde g_2 - \frac{1}{6} g_3^3 / g_4^2.
+	\begin{equation}\label{eq:density}
+	\bar n = n_g - \bar{M} + \frac{ \bar \rho_0}{\beta W(0)}.
 	\end{equation}
-	...
+	The quantity $n_g$ in the equation \eqref{eq:density} is the critical density
+	\begin{equation}\label{eq:crit_dens}
+	n_g = g_1 - \frac{g_3}{g_4}\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right) - \frac{1}{6} \frac{g_3^3}{g_4^2}.
+	\end{equation}
+	Combination of the equations \eqref{eq:density} and \eqref{eq:ro_M} reveals the explicit expression for the effective chemical potential $M$ as a function of the density and the temperature
+	\begin{equation}\label{eq:M_nT}
+		\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g),
+	\end{equation}
 
-	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state~(\ref{eq:eos})
+	........................................................
+
+	********************************************************
+
+	[THE FOLLOWING NEEDS REFINEMENT, OKSANA WILL DO IT SOON]
+
+	where
+	\begin{equation} \label{eq:ro_nT}
+		 \rho_{n} = - 2 \left(\frac{-2\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right)}{g_4}\right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \qquad 	\alpha_n = \arccos \left( \frac{3}{2} \left( - \frac{g_4}{2\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right).
+	\end{equation}
+
+	At $T>T_c$ the equation of state of a cell fluid model in terms of density has the following form
+	\begin{equation}\label{eq:eosNT}
+	Pv\beta = E_\mu^{(2)}(n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4,
+	\end{equation}
+	where
+	\begin{equation}\label{3d30}
+	\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g)
+	\end{equation}
+	is a function of density and temperature. Recall the formula \eqref{2d22} to find
+	\begin{equation}\label{3d31}
+	\frac{\tilde\mu}{W(0)} = \bar M - n_g + n_c \tilde g_2 \gamma_\tau,
+	\end{equation}
+	where $n_g$ is defined in \eqref{3d4}. Therefore,
+	\begin{align}\label{3d32}
+		E_\eta (\bar n,T) & = - \frac{\ln (2\pi \beta W(0))}{2 N_v} + g_0 - \frac{1}{2\tilde g_2 \gamma_\tau} \left( \frac{\tilde\mu}{W(0)}\right)  + n_c \bar M- \nonumber \\
+		& - \frac{1}{2} n_c^2 \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}.
+	\end{align}
+
+	********************************************************
+
+	........................................................
+
+	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state ~\eqref{eq:eosMT} in terms of (chemical potential, temperature)  and \eqref{eq:eosNT} in terms of (density, temperature).
 	\begin{figure}[h!]

### 2024-08-11 main_morse_response_functions.tex
add fourier transform for repulsive part of interaction potential

@@
 		\label{def:mod_morse}
-		U(r) = C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
+		U(r) = \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
 	\end{equation}
@@
 	\begin{equation}
-		C_{H} = \frac{\varepsilon n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
+		C_{H} = \frac{n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
 	\end{equation}
@@
 	\section{The equation of state}
-	The equation of state obtained in~\cite{KozlovskiiDobush2020} reads
+	The equation of state obtained in~\cite[see Eq.(42)]{KozlovskiiDobush2020} reads
 	\begin{equation}
@@
 	where
-	\begin{align} 
-		& B = 2 \gamma^3 e^{(1-\gamma)/\alpha},\nonumber \\
-		& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3,
-	\end{align}
-	and $\Phi^{(r)}(0)$ is the Fourier transform of the repulsive part of the potential at $\abs{\vb k}=0$.
-The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a term in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$.
+	\begin{align*} 
+		& B = 2 \gamma^3 e^{(1-\gamma)R_0/\alpha},
+		\nonumber \\
+		& A_\gamma = A e^{(n_0-\gamma)R_0/\alpha} \left( \gamma / n_0\right)^3, 
+	\end{align*}
+	and $\Phi^{(r)}(0)$ is the Fourier transform of the repulsive part of the potential at $\abs{\vb k}=0$
+	\begin{equation*}
+		\Phi^{(r)}(0) = \varepsilon C_H 8\pi {\rm e}^{\gamma R_0/\alpha} \left(\frac{\alpha}{\gamma}\right)^3.
+	\end{equation*}
+
+	The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a contribution in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$~\cite[see Eq.(24)]{KozlovskiiDobush2020}.
 
@@
 	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature.
-The numerical values for other coefficients used in this paper are the same as those in~\cite{KozlovskiiDobush2020}:
-	\begin{equation*}
-		\alpha^* = 5.0, \quad \gamma = 1.65, \quad n_0 = 1.521.
-	\end{equation*}
+The numerical values for other coefficients used in this paper are the same as those in~\cite[see Eqs.(5), (23), and (24)]{KozlovskiiDobush2020}:
+	\begin{eqnarray*}
+		\alpha^* = 5.0, & \quad \gamma = 1.65, \\
+		n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \\
+		\chi_0 = 0.07.
+	\end{eqnarray*}
 

### 2024-08-11 main_morse_response_functions.tex
add critical temperature values; add note about dimensionality of p and alpha*

@@
 \usepackage{graphicx}
+
+\usepackage[dvipsnames]{xcolor} % temporary
 
@@
 	\end{equation}
-	The quantities in the left-hand side of the equation are $P$, the pressure; $\beta$, the inverse temperature; $v$, cell volume.
+	The quantities in the left-hand side of the equation are $P$, the pressure; $\beta = (k_{\rm B} T)^{-1}$, the inverse temperature; $k_{\rm B}$, the Boltzmann constant; $T$, the temperature; $v$, cell volume.
 The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential $\mu$.
@@
 	\end{equation} 
-	The quantity $\beta_c$ denotes the critical value of the inverse temperature.
+	{\color{Red} {\bf{NOTE: }} Both quantities $p$ and $\alpha^*$ have the dimensions of volume. }
+
+	The quantity $\beta_c$ denotes the critical value of the inverse temperature. In~\cite[see Eq.(31)]{KozlovskiiDobush2020} it was found that
+	\begin{equation*}
+		\varepsilon\beta_c = 0.200, \quad \frac{k_{\rm B} T_c}{\varepsilon} = 4.995.
+	\end{equation*}
 	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature.
@@
 	\begin{eqnarray*}
-		\alpha^* = 5.0, & \quad \gamma = 1.65, \\
+		\chi_0 = 0.07, & \quad \gamma = 1.65, \\
 		n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \\
-		\chi_0 = 0.07.
+		\alpha^* = 5.0 & \quad p = 1.0.
 	\end{eqnarray*}
@@
 	\end{equation}
-	Note that for all $ \tau> 0 $ the later equation has one real root.
+	Note that for all $ \tau> 0 $ the latter equation has one real root.
 Consequently, there are no restrictions on the value of the quantity $ \bar \rho_0 $, which is a function of the temperature and the chemical potential

### 2024-08-11 main_morse_response_functions.tex
add minus in exponent of spec function
note about dimensions of critical temperature

@@
 	\begin{equation}
-	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
+		T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n {\rm e}^{-pm^2}.
 	\end{equation}
@@
 	\end{equation} 
-	{\color{Red} {\bf{NOTE: }} Both quantities $p$ and $\alpha^*$ have the dimensions of volume. }
+	{\color{Red} {\bf{NOTE 1: }} Both quantities $p$ and $\alpha^*$ have the dimensions of volume. }
 
@@
 	\end{equation}
-	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite{KozlovskiiDobush2020}
+	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite[see Eq.(31)]{KozlovskiiDobush2020}
 	\begin{equation}
-		T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
+		k_{\rm B}T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
 	\end{equation} 
+	{\color{Red} {\bf{NOTE 2: }} In such representation, the critical temperature $k_{\rm B}T_c$ seems to have dimension of $energy\times volume$. }
 

### 2024-08-11 main_morse_response_functions.tex
add definition of Nv

@@
 		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
-		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, 
+		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, \nonumber\\
+		& a_4 = -g_4,
 	\end{align}
@@
 	\end{equation} 
-	{\color{Red} {\bf{NOTE 2: }} In such representation, the critical temperature $k_{\rm B}T_c$ seems to have dimension of $energy\times volume$. }
+	{\color{Red} {\bf{NOTE 2: }} In such representation, the critical temperature $k_{\rm B}T_c$ seems to have dimension of $[energy\times volume]$. }
 
@@
 	\end{align}
-	The connection between the effective chemical potential $M$ and the quantity $ \bar \rho_0 $ follows from the cubic equation
+	Here the quantity $N_v$ defines the number of cubic cells in volume $V$ for the initial model.
+	In the thermodynamic limit, $N_v \to \infty$.
+
+	The quantity $\bar{\rho}_0$ is a solution to the following cubic equation
 	\begin{equation}\label{eq:ro_M}
-	\bar M + \tilde D(0) \bar\rho_0 - \frac{a_4}{6} \bar\rho_0^3 = 0,
+	M + \tilde D(0) \bar\rho_0 - \frac{a_4}{6} \bar\rho_0^3 = 0.
 	\end{equation}
-	Note that for all $ \tau> 0 $ the latter equation has one real root.
-Consequently, there are no restrictions on the value of the quantity $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
+	For any $\tau > 0$, the latter equation has one real root
 	\begin{equation}\label{eq:ro_MT}
-	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
+	\bar \rho_0 = \left(- \frac{3 M}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3 M}{g_4} + \sqrt{Q_t} \right)^{1/3},
 	\end{equation}
@@
 	\begin{equation}
-	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3\bar{M}}{g_4}\right)^2, \qquad g_4<0.
+	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3 M}{g_4}\right)^2, \qquad g_4<0.
 	\end{equation}
+	Thus, $\bar{\rho}_0$ is a function of the temperature and the chemical potential.
+
 	........................................................

### 2024-08-12 main_morse_response_functions.tex
rewrite compressibility in terms of second pressure derivative with respect to chemical potential

@@
 	\begin{equation}
-	\eta = \frac{<N>}{v N_v} = \frac{1}{v} \frac{\partial}{\partial\beta\mu} Pv\beta = \frac{\bar n}{v},
+	\eta = \frac{\langle N\rangle}{v N_v} = \frac{1}{v} \frac{\partial}{\partial\beta\mu} Pv\beta = \frac{\bar n}{v},
 	\end{equation} 
@@
 		\label{def:isotherm_compres}
-		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,<N>}
+		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}
+	\end{equation}
+	Let us perform some transformations to rewrite the definition for $K_T$ into a form that is more suitable for the equation of state~\eqref{eq:eosMT}.
+	\begin{eqnarray*}
+		K_T & = & - \frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}
+		\\
+		& = & -\rho \left(\frac{\partial \left(\frac{1}{\rho}\right)}{\partial P}\right)_{T,\langle N\rangle}
+		\\
+		& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,\langle N\rangle}
+		\\
+		& = & \frac{1}{\rho} \frac{\left(\partial \rho / \partial \mu\right)_{T,\langle N\rangle}}
+		{\left(\partial P / \partial \mu\right)_{T,\langle N\rangle}},
+	\end{eqnarray*}
+	where $\rho = \langle N \rangle / V$ is the particle number density.
+	Applying the Gibbs--Duhem equation at $T = const$, one has
+	\begin{equation*}
+		{\rm d} P = \rho {\rm d} \mu,
+	\end{equation*}
+	or
+	\begin{equation}
+		\label{eq:rho_dpdm}
+		\rho = \left(\frac{\partial P}{\partial \mu}\right)_T.
+	\end{equation}
+	Substituting this into the last expression for $K_T$, one gets
+	\begin{equation}
+		K_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T,\langle N\rangle}
+	\end{equation}
+	Finally, from~\eqref{eq:rho_dpdm} it follows that
+	\begin{equation}
+		\left(\frac{\partial \rho}{\partial \mu}\right)_T = \left(\frac{\partial^2 P}{\partial \mu^2}\right)_T
+	\end{equation}
+	and ultimately we arrive at the very useful expression for the isothermal compressibility
+	\begin{equation}
+		K_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T,\langle N\rangle}
 	\end{equation}
@@
 		\label{def:therm_pres_coef}
-		\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,<N>}
+		\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,\langle N \rangle}
 	\end{equation}
@@
 	\begin{equation}
-		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,<N>}
+		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}
 	\end{equation}

### 2024-08-14 main_morse_response_functions.tex
add formulas for density and average number of particles
made refinement to eos via dens and temp

@@
 	The function $E_\mu(M, T)$ from the equation \eqref{eq:eosMT} is provided by
-	\begin{align}
+	\begin{align}\label{eq:E_mu}
 		& E_\mu (M, T) = - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 - \frac{\beta W(0)}{2} \!\!
@@
 
-	The density of the many-particle system is the ratio of the average number of particles $\left\langle N \right\rangle$  to the total volume of the system $V$.
+	The density $\eta$ of the many-particle system is the ratio of the average number of particles $\left\langle N \right\rangle$  to the total volume of the system $V$.
 	In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to the product $\beta \mu$.
@@
 	\end{equation}
-
-	........................................................
-
-	********************************************************
-
-	[THE FOLLOWING NEEDS REFINEMENT, OKSANA WILL DO IT SOON]
-
 	where
-	\begin{equation} \label{eq:ro_nT}
-		 \rho_{n} = - 2 \left(\frac{-2\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right)}{g_4}\right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \qquad 	\alpha_n = \arccos \left( \frac{3}{2} \left( - \frac{g_4}{2\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right).
-	\end{equation}
-
-	At $T>T_c$ the equation of state of a cell fluid model in terms of density has the following form
-	\begin{equation}\label{eq:eosNT}
-	Pv\beta = E_\mu^{(2)}(n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4,
-	\end{equation}
-	where
-	\begin{equation}\label{3d30}
-	\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g)
-	\end{equation}
-	is a function of density and temperature. Recall the formula \eqref{2d22} to find
-	\begin{equation}\label{3d31}
-	\frac{\tilde\mu}{W(0)} = \bar M - n_g + n_c \tilde g_2 \gamma_\tau,
-	\end{equation}
-	where $n_g$ is defined in \eqref{3d4}. Therefore,
-	\begin{align}\label{3d32}
-		E_\eta (\bar n,T) & = - \frac{\ln (2\pi \beta W(0))}{2 N_v} + g_0 - \frac{1}{2\tilde g_2 \gamma_\tau} \left( \frac{\tilde\mu}{W(0)}\right)  + n_c \bar M- \nonumber \\
-		& - \frac{1}{2} n_c^2 \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}.
+	\begin{align} \label{eq:ro_nT}
+		 & \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
+		 & \alpha_n = \arccos \left( \frac{3}{2} \left( - \frac{g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber
 	\end{align}
 
-	********************************************************
-
-	........................................................
+	At $T>T_c$ the equation of state of a cell fluid model in terms of the density and the temperature has the following form
+	\begin{equation}\label{eq:eosNT}
+	Pv\beta = E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4,
+	\end{equation}
+ The function $E_\nu (\bar n, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}.
 

### 2024-08-14 main_morse_response_functions.tex

@@
 
-	The density $\eta$ of the many-particle system is the ratio of the average number of particles $\left\langle N \right\rangle$  to the total volume of the system $V$.
+	The density of the many-particle system is the ratio of the average number of particles $\left\langle N \right\rangle$  to the total volume of the system $V$.
 	In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to the product $\beta \mu$.
+	\begin{eqnarray*}
+		\langle N \rangle & = & \left(\frac{\partial \ln\Xi}{\partial \beta \mu}\right)_{T,V} 
+		\\
+		& = & \left(\frac{\partial (PV)}{\partial \beta \mu}\right)_{T,V}
+		\\
+		& = & V \left(\frac{\partial P}{\partial \beta \mu}\right)_{T,V}.
+	\end{eqnarray*}
+	From this equation it follows
+	\begin{equation*}
+		\frac{\langle N \rangle}{V} = \frac{\langle N \rangle}{v N_v} = \left(\frac{\partial P}{\partial \beta \mu}\right)_{T,V}
+	\end{equation*}
+	and thus
+	\begin{equation*}
+		\bar{n} \equiv \frac{\langle N \rangle}{V} v = \frac{\langle N \rangle}{N_v} = v \left(\frac{\partial P}{\partial \beta \mu}\right)_{T,V}
+	\end{equation*}
+
 	Using the general relation for the equation of state $PV\beta = \ln \Xi $ the density reads

### 2024-08-21 main_morse_response_functions.tex
remove not-needed beta
split eos into two subsections - in terms of temperature and chem potential, and another in terms of temperature and density

--- 2024-08-14 main_morse_response_functions.tex
@@
 	\section{The equation of state}
+	\subsection{Pressure as a function of temperature and chemical potential}
 	The equation of state obtained in~\cite[see Eq.(42)]{KozlovskiiDobush2020} reads
@@
 	\begin{equation*}
-		\Phi^{(r)}(0) = \varepsilon C_H 8\pi {\rm e}^{\gamma R_0/\alpha} \left(\frac{\alpha}{\gamma}\right)^3.
+		\Phi^{(r)}(0) = \varepsilon C_H 8\pi {\rm e}^{\gamma R_0/\alpha} \left(\frac{\alpha}{\gamma R_0}\right)^3.
 	\end{equation*}
@@
 	\end{equation} 
-	{\color{Red} {\bf{NOTE 1: }} Both quantities $p$ and $\alpha^*$ have the dimensions of volume. }
+	{\color{Red} {\bf{NOTE 1: }} Quantities $\alpha^*$ has the dimension of volume.}
 
@@
 The numerical values for other coefficients used in this paper are the same as those in~\cite[see Eqs.(5), (23), and (24)]{KozlovskiiDobush2020}:
-	\begin{eqnarray*}
+	\begin{eqnarray}
+		\label{params}
 		\chi_0 = 0.07, & \quad \gamma = 1.65, \\
@@
 		\alpha^* = 5.0 & \quad p = 1.0.
-	\end{eqnarray*}
+	\end{eqnarray}
 
@@
 	\end{equation}
-	{\color{Red} {\bf{NOTE 2: }} In such representation, the critical temperature $k_{\rm B}T_c$ seems to have dimension of $[energy\times volume]$. }
 
@@
 
-	........................................................
-
-	The density $\eta$ of the many-particle system is the ratio of the average number of particles $\left\langle N \right\rangle$  to the total volume of the system $V$.
+	\subsection{Pressure as a function of temperature and density}
+	In this work, by density we mean the particle number density $\rho = \langle N \rangle / V$.
 	In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to the product $\beta \mu$.
-Using the general relation for the equation of state $PV\beta = \ln \Xi $ the density reads
+	\begin{eqnarray*}
+		\langle N \rangle & = & \left(\frac{\partial \ln\Xi}{\partial \beta \mu}\right)_{T,V} 
+		\\
+		& = & \left(\frac{\partial (PV)}{\partial \mu}\right)_{T,V}
+		\\
+		& = & V \left(\frac{\partial P}{\partial \mu}\right)_{T,V}.
+	\end{eqnarray*}
+	From this equation it follows
+	\begin{equation*}
+		\frac{\langle N \rangle}{V} = \frac{\langle N \rangle}{v N_v} = \left(\frac{\partial P}{\partial \mu}\right)_{T,V}
+	\end{equation*}
+	and thus
 	\begin{equation}
-	\eta = \frac{\langle N\rangle}{v N_v} = \frac{1}{v} \frac{\partial}{\partial\beta\mu} Pv\beta = \frac{\bar n}{v},
+		\bar{n} \equiv \frac{\langle N \rangle}{V} v = \frac{\langle N \rangle}{N_v} = v \left(\frac{\partial P}{\partial \mu}\right)_{T,V} 
+		= \left(\frac{\partial (Pv\beta)}{\partial (\beta \mu)}\right)_{T,V}.
 	\end{equation}
-	where	
+	The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density. On the other hand, it is the average number of particles per cell.
+	Taking explicit derivatives, we arrive at
 	\begin{equation}\label{eq:density}
-	\bar n = n_g - \bar{M} + \frac{ \bar \rho_0}{\beta W(0)}.
+	\bar n = n_g - M + \frac{ \bar \rho_0}{\beta W(0)}.
 	\end{equation}
 	The quantity $n_g$ in the equation \eqref{eq:density} is the critical density
-	\begin{equation}\label{eq:crit_dens}
-	n_g = g_1 - \frac{g_3}{g_4}\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right) - \frac{1}{6} \frac{g_3^3}{g_4^2}.
-	\end{equation}
+	\begin{eqnarray}\label{eq:crit_dens}
+	n_g & = & g_1 - \frac{g_3}{g_4}\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right) - \frac{1}{6} \frac{g_3^3}{g_4^2} 
+	\nonumber\\
+	& = & g_1 - \frac{g_2 g_3}{g_4} + \frac{g_3^3}{3g_4^2}
+	\end{eqnarray}
+	Its numerical value for parameters~\eqref{params} is
+	\begin{equation*}
+		n_g = 0.978.
+	\end{equation*}
 	Combination of the equations \eqref{eq:density} and \eqref{eq:ro_M} reveals the explicit expression for the effective chemical potential $M$ as a function of the density and the temperature
@@
 	where $\rho = \langle N \rangle / V$ is the particle number density.
-	Applying the Gibbs--Duhem equation at $T = const$, one has
+	Applying the Gibbs--Duhem equation
+	\begin{equation}
+		N{\rm d}\mu = -S{\rm d}T + V{\rm d}P,
+	\end{equation}
+	at $T = const$ one has 
 	\begin{equation*}

### 2024-08-23 main_morse_response_functions.tex
introduce the reduced pressure

@@
 		\label{params}
-		\chi_0 = 0.07, & \quad \gamma = 1.65, \\
-		n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \\
+		\chi_0 = 0.07, & \quad \gamma = 1.65, \nonumber\\
+		n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \nonumber\\
 		\alpha^* = 5.0 & \quad p = 1.0.
@@
 	The function $E_\mu(M, T)$ from the equation \eqref{eq:eosMT} is provided by
-	\begin{align}\label{eq:E_mu}
-		& E_\mu (M, T) = - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 - \frac{\beta W(0)}{2} \!\!
-\left( \!
-\frac{\tilde\mu}{W(0)} \!
-\right)^{\!
-2} \!\!\!
-- \frac{g_3}{g_4} {M} \!
-- \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}.
-	\end{align}
+	\begin{eqnarray}\label{eq:E_mu}
+		E_\mu (M, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 - \frac{\beta W(0)}{2} 
+		\left(\frac{\tilde\mu}{W(0)} \right)^{2} 
+		\nonumber\\
+		&& - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
+	\end{eqnarray}
 	Here the quantity $N_v$ defines the number of cubic cells in volume $V$ for the initial model.
-	In the thermodynamic limit, $N_v \to \infty$.
+	In the thermodynamic limit, $N_v \to \infty$, and thus the first term can be neglected.
+The term $\tilde{\mu}/W(0)$ can be expressed in terms of $M$ using~\eqref{chem_pot}.
+The temperature and the inverse temperature can always be expressed in terms of the reduced temperature and a corresponding critical value:
+	\begin{equation*}
+		T = T_c(1+\tau), \quad \beta = \beta_c (1 + \tau)^{-1}
+	\end{equation*}
 
@@
 	Thus, $\bar{\rho}_0$ is a function of the temperature and the chemical potential.
+
+	Let us introduce the reduced pressure
+	\begin{equation}
+		\label{def:reduced_pres}
+		P^* \equiv \frac{P v}{\varepsilon}.
+	\end{equation}
+	Considering the equation of state~\eqref{eq:eosMT}, $P^*$ can be written as
+	\begin{equation}
+		\label{eq:reduced_pres}
+		P^* = \frac{1 + \tau}{\varepsilon \beta_c} Pv\beta.
+	\end{equation}
+	This equation can be easily represented graphically.
+Figure~\ref{fig1} illustrates the relationship between the reduced pressure $P^*$ and the effective chemical potential $M$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
+At the critical point $M=0, \tau=0$, $P^*_c = 1.606$.
 
@@
 	\end{equation}
-	The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density. On the other hand, it is the average number of particles per cell.
+	The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density. In the context of the cell model, on the other hand, it is the average number of particles per cell.
 	Taking explicit derivatives, we arrive at
@@
 	\end{equation*}
-	Combination of the equations \eqref{eq:density} and \eqref{eq:ro_M} reveals the explicit expression for the effective chemical potential $M$ as a function of the density and the temperature
+	Equations~\eqref{eq:density} and~\eqref{eq:eosMT} jointly define a parametric relationship between pressure and density, with $M$ serving as the parameter.
+Figure~\ref{fig1} shows the dependency of the reduced pressure $P^*$ on the density $\bar{n}$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
+
+	This dependency can also be expressed explicitly.
+To achieve this, we combine the equations~\eqref{eq:density} and~\eqref{eq:ro_M} to express the effective chemical potential $M$ as a function of density and temperature:
 	\begin{equation}\label{eq:M_nT}
@@
 		\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
-		\vskip-3mm\caption{Plots of isotherms of the pressure $P$ as a function of the density $\bar n$ (on the lefthand side) and a function of the effective chemical potential $M$ (on the righthand side) at $T \geq T_c$ represented by black lines.
+		\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function of the density $\bar n$ (on the left-hand side) and a function of the effective chemical potential $M$ (on the right-hand side) at $T \geq T_c$ represented by black lines.
 Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.

### 2024-08-27 main_morse_response_functions.tex
remove const N where not needed

@@
 	In this work, by density we mean the particle number density $\rho = \langle N \rangle / V$.
-	In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to the product $\beta \mu$.
+	In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to $\beta \mu$
 	\begin{eqnarray*}
@@
 		\label{def:isotherm_compres}
-		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}
+		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}.
 	\end{equation}
-	Let us perform some transformations to rewrite the definition for $K_T$ into a form that is more suitable for the equation of state~\eqref{eq:eosMT}.
+	Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state~\eqref{eq:eosMT}
 	\begin{eqnarray*}
@@
 		\\
-		& = & \frac{1}{\rho} \frac{\left(\partial \rho / \partial \mu\right)_{T,\langle N\rangle}}
-		{\left(\partial P / \partial \mu\right)_{T,\langle N\rangle}},
+		& = & \frac{1}{\rho} \frac{\left(\partial \rho / \partial \mu\right)_{T}}
+		{\left(\partial P / \partial \mu\right)_{T}},
 	\end{eqnarray*}
 	where $\rho = \langle N \rangle / V$ is the particle number density.
+We have omitted the condition of constant $\langle N \rangle$ in the last line of the above equation since we have explicit dependencies on temperature and chemical potential for both pressure $P = P(T, \mu)$, see Eq.~\eqref{eq:eosMT}, and density $\rho = \rho(T, \mu)$, see Eq.~\eqref{eq:density}.
 	Applying the Gibbs--Duhem equation
@@
 	\begin{equation}
-		K_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T,\langle N\rangle}
+		K_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
 	\end{equation}
@@
 	\begin{equation}
-		K_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T,\langle N\rangle}
+		K_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T}
 	\end{equation}
+
+	Let us introduce the reduced isothermal compressibility
+	\begin{equation}
+		K^*_T \equiv \frac{\varepsilon K_T}{v}.
+	\end{equation}
+	The quantity $K^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent.
+Figure~\ref{fig2a} illustrates the dependency of the compressibility $K^*_T$ on the density $\bar{n}$ for various values of temperature above the critical one.
 
@@
 		\centering \includegraphics[width=0.5\textwidth]{f2a.pdf}
-		\vskip-3mm\caption{The isothermal compressibility $K_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
+		\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
 		}\label{fig2a}
@@
 		\includegraphics[width=0.475\textwidth]{f2c.pdf}
-		\vskip-3mm\caption{The isothermal compressibility $K_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+		\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
 The two figures differ in the scale of $M$.

### 2024-08-27 main_morse_response_functions.tex
rewrite the definition of thermal pressure coefficient to be suitable for mu and T varialbes; introduce reduced thermal pressure coefficient

@@
 		\label{def:therm_pres_coef}
-		\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,\langle N \rangle}
+		\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,\langle N \rangle}.
+	\end{equation}
+	We rewrite $\beta_V$ into a form that is suitable for the equation of state~\eqref{eq:eosMT}
+	\begin{eqnarray}
+		\beta_V & = & \left(\frac{\partial P}{\partial T}\right)_{V, N}
+		\nonumber\\
+		& = & \left(\frac{\partial P}{\partial T}\right)_{\mu} + \left(\frac{\partial P}{\partial \mu}\right)_T \left(\frac{\partial \mu}{\partial T}\right)_{V, N}.
+	\end{eqnarray}
+	Applying the chain rule
+	\begin{equation*}
+		\left(\frac{\partial \mu}{\partial T}\right)_{V, N} 
+		\left(\frac{\partial T}{\partial V}\right)_{\mu, N}
+		\left(\frac{\partial V}{\partial \mu}\right)_{T, N}
+		= -1
+	\end{equation*}
+	we obtain
+	\begin{eqnarray*}
+		\left(\frac{\partial \mu}{\partial T}\right)_{V, N} 
+		& = & 
+		- \left(\frac{\partial V}{\partial T}\right)_{\mu, N} 
+		\left(\frac{\partial V}{\partial \mu}\right)^{-1}_{T, N} \\
+		& = & - \left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
+		\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}.		
+	\end{eqnarray*}
+	Substituting this result into the formula for $\beta_V$, we arrive at the final expression for the thermal pressure coefficient
+	\begin{equation}
+		\beta_V = \left(\frac{\partial P}{\partial T}\right)_{\mu} 
+		- \left(\frac{\partial P}{\partial \mu}\right)_T 
+		\left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
+		\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}
+	\end{equation}
+	which is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.
+
+	We introduce the reduced thermal pressure coefficient by
+	\begin{equation}
+		\beta^*_V = \frac{v\beta_V}{k_{\rm B}}.
 	\end{equation}
@@
 		\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
-		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+		\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
 		}\label{fig3a}
@@
 		\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
-		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+		\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
 		}\label{fig3b}
@@
 		\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
-		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the relative temperature $\tau$ at different values of the density $\eta$. 
+		\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\eta$. 
 		}\label{fig3c}
 	\end{figure}
+
+	Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\bar{n}$ for various values of temperature above the critical one.
+The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig3b}.
 

### 2024-08-27 main_morse_response_functions.tex
add reference to Stroker and Meier - Classical stat mech in grand canonical ensemble
rewrite definition of thermal expansion coeff to be suitable for mu and T variables; introduce reduced thermal expansion coefficient

@@
 	\end{equation}
-	which is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.
+	which is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
+	(NB. Compare this equation with Eq.(17) from~\cite{StrokerMeier2021})
 
@@
 	\begin{equation}
-		\beta^*_V = \frac{v\beta_V}{k_{\rm B}}.
+		\beta^*_V = \frac{v}{k_{\rm B}}\beta_V.
 	\end{equation}
@@
 	\end{equation}
+	We rewrite $\alpha_P$ into a form suitable for the equation of state~\eqref{eq:eosMT}
+	\begin{eqnarray*}
+		\alpha_P & = & \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}
+		\\
+		& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{P, N}
+		\\
+		& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{\mu} 
+		 - \frac{1}{\rho} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
+		 \left(\frac{\partial \mu}{\partial T}\right)_{P, N}.
+	\end{eqnarray*}
+	Applying the chain rule
+	\begin{equation*}
+		\left(\frac{\partial \mu}{\partial T}\right)_{P, N}
+		\left(\frac{\partial T}{\partial P}\right)_{\mu, N}
+		\left(\frac{\partial P}{\partial \mu}\right)_{T, N}
+		= -1
+	\end{equation*}
+	we get
+	\begin{eqnarray*}
+		\left(\frac{\partial \mu}{\partial T}\right)_{P, N} & = & 
+		- \left(\frac{\partial P}{\partial T}\right)_{\mu}
+		\left(\frac{\partial P}{\partial \mu}\right)^{-1}_{T}.
+	\end{eqnarray*}
+	Substituting the result into the expression for $\alpha_P$, we arrive at the final formula for the thermal expansion coefficient
+	\begin{equation}
+		\alpha_P = -\frac{1}{\rho}\left(\frac{\partial \rho}{\partial T}\right)_{\mu}
+		+ \frac{1}{\rho} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
+		\left(\frac{\partial P}{\partial T}\right)_{\mu}
+		\left(\frac{\partial P}{\partial \mu}\right)^{-1}_{T}
+	\end{equation}
+	which is readily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
+	(NB. Compare this equation with Eqs.(57)-(58) from~\cite{StrokerMeier2021})
+
+	We introduce the reduced thermal expansion coefficient by
+	\begin{equation}
+		\alpha^*_P = \frac{\varepsilon}{k_{\rm B}} \alpha_P.
+	\end{equation}
+	Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\bar{n}$ for various values of temperature above the critical one.
+The dependency of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Figure~\ref{fig4b}.
 
@@
 		\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
-		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+		\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
 		}\label{fig4a}
@@
 		\includegraphics[width=0.475\textwidth]{f4c.pdf}
-		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+		\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
 The two figures differ in the scale of $M$.

### 2024-09-01 main_morse_response_functions.tex
change terminology from chain rule to cyclic relation
explicitly write that there are two eos - P(T,mu) and P(T,n)

@@
 
-	\section{The equation of state}
+	\section{\label{sec:eos}The equation of state}
 	\subsection{Pressure as a function of temperature and chemical potential}
@@
 	\end{equation}
-	Considering the equation of state~\eqref{eq:eosMT}, $P^*$ can be written as
+	Considering the equation of state~\eqref{eq:eosMT}, $P^*$ is explicitly written as
 	\begin{equation}
-		\label{eq:reduced_pres}
-		P^* = \frac{1 + \tau}{\varepsilon \beta_c} Pv\beta.
+		\label{eq:eosPTM_reduced}
+		P^* = \frac{1 + \tau}{\varepsilon \beta_c} \left( E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4 \right).
 	\end{equation}
@@
 	\end{align}
+	{\color{Red} {\bf{NOTE 2: }} Roma: In my opinion, under {\it{arccos}} we should have 3, not $\frac{3}{2}$}
 
@@
  The function $E_\nu (\bar n, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}.
+For the reduced pressure we write
+ \begin{equation}
+ 	\label{eq:eosPTn_reduced}
+ 	P^* = \frac{1 + \tau}{\varepsilon \beta_c} \left(E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\right).
+ \end{equation}
 
-	Figure~1 shows the isotherms for the pressure $P$ following from the equation of state ~\eqref{eq:eosMT} in terms of (chemical potential, temperature)  and \eqref{eq:eosNT} in terms of (density, temperature).
+	Figure~1 shows the isotherms for the pressure $P^*$ versus density $\bar{n}$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
 	\begin{figure}[h!]
@@
 
-	\section{Thermodynamic response functions (coefficients)}
+	Thus, in this Section, we presented two forms of the equation of state.
+The first one expresses the pressure as a function of temperature and chemical potential, $P = P(T, \mu)$, and is represented by Eqs.~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}.
+The second one expresses the pressure as a function of temperature and density, $P = P(T, \bar{n})$, and is represented by Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
+These equations, together with the explicit dependency of density on temperature and chemical potential, $\bar{n} = \bar{n}(T, \mu)$, see Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}
+
+	\section{\label{sec:respons_functions}Thermodynamic response functions}
 
@@
 	The quantity $K^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent.
+It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
+	\begin{eqnarray}
+		K^*_T & = & \frac{\varepsilon}{\bar{n}^2} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_T
+		\nonumber\\
+		& = & \frac{\varepsilon^2}{\bar{n}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
+	\end{eqnarray}
+	Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $K^*_T$, with the result expressed as a function of temperature and chemical potential.
+
 	Figure~\ref{fig2a} illustrates the dependency of the compressibility $K^*_T$ on the density $\bar{n}$ for various values of temperature above the critical one.
+The dependency of $K^*_T$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig2b}.
 
@@
 	\end{eqnarray}
-	Applying the chain rule
+	Applying the cyclic relation
 	\begin{equation*}
@@
 	\end{eqnarray*}
-	Applying the chain rule
+	Applying the cyclic relation
 	\begin{equation*}

### 2024-09-01 main_morse_response_functions.tex
write two equivalent expressions for K_T suitable for two forms of eos

@@
 	Thus, in this Section, we presented two forms of the equation of state.
-The first one expresses the pressure as a function of temperature and chemical potential, $P = P(T, \mu)$, and is represented by Eqs.~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}.
-The second one expresses the pressure as a function of temperature and density, $P = P(T, \bar{n})$, and is represented by Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
+The first one expresses the pressure as a function of temperature and chemical potential, $P = P(T, \mu)$, and is represented by equivalent Eqs.~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}.
+The second one expresses the pressure as a function of temperature and density, $P = P(T, \bar{n})$, and is represented by equivalent Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
 These equations, together with the explicit dependency of density on temperature and chemical potential, $\bar{n} = \bar{n}(T, \mu)$, see Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}
@@
 	\end{equation}
-	Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state~\eqref{eq:eosMT}
+	Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
 	\begin{eqnarray*}
@@
 	Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $K^*_T$, with the result expressed as a function of temperature and chemical potential.
+
+	If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the isothermal compressibility are
+	\begin{equation}
+		K_T = \frac{1}{\bar{n}} \left(\frac{\partial P}{\partial \bar{n}}\right)^{-1}_T
+	\end{equation}
+	and 
+	\begin{equation}
+		K^*_T = \frac{1}{\bar{n}} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
+	\end{equation}
 

### 2024-09-01 main_morse_response_functions.tex
write two equivalent expressions for beta_V suitable for two forms of eos

@@
 	\end{equation}
-	We rewrite $\beta_V$ into a form that is suitable for the equation of state~\eqref{eq:eosMT}
+	We rewrite $\beta_V$ into a form that is suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
 	\begin{eqnarray}
@@
 		\beta^*_V = \frac{v}{k_{\rm B}}\beta_V.
+	\end{equation}
+	It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
+	\begin{equation}
+		\beta^*_V = \varepsilon\beta_c 
+		\left[ \left(\frac{\partial P^*}{\partial \tau}\right)_{\mu} 
+		- \left(\frac{\partial P^*}{\partial \mu}\right)_T 
+		\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
+		\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T} 
+		\right].
+	\end{equation}
+
+	If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the thermal pressure coefficient follow immediately from the definition~\eqref{def:therm_pres_coef}
+	\begin{equation}
+		\beta_V = \left(\frac{\partial P}{\partial T}\right)_\rho
+	\end{equation}
+	and
+	\begin{equation}
+		\beta^*_V = \varepsilon\beta_c \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}
 	\end{equation}

### 2024-09-01 main_morse_response_functions.tex
write two equivalent expressions for alpha_P suitable for two forms of eos

@@
 	\begin{equation}
-		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}
+		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}.
 	\end{equation}
-	We rewrite $\alpha_P$ into a form suitable for the equation of state~\eqref{eq:eosMT}
-	\begin{eqnarray*}
-		\alpha_P & = & \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}
-		\\
+	We rewrite $\alpha_P$ into a form suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
+	\begin{eqnarray}
+		\alpha_P & = & \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P, N}
+		\nonumber\\
+		\label{eq:alpha_vs_rho}
 		& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{P, N}
@@
 		 \left(\frac{\partial \mu}{\partial T}\right)_{P, N}.
-	\end{eqnarray*}
+	\end{eqnarray}
 	Applying the cyclic relation
@@
 	\end{equation}
+	It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
+	\begin{equation}
+		\alpha^*_P = \varepsilon \beta_c 
+		\left( 
+		-\frac{1}{\bar{n}}\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
+		+ \frac{1}{\bar{n}} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
+		\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
+		\left(\frac{\partial P^*}{\partial \mu}\right)^{-1}_{T} 
+		\right).
+	\end{equation}
+
+	If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then we need to rewrite the definition for $\alpha_P$ accordingly.
+We start with~\eqref{eq:alpha_vs_rho} and apply the cyclic relation
+	\begin{equation}
+		\left(\frac{\partial \rho}{\partial T}\right)_P = - \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T
+	\end{equation}
+	to get for $\alpha_P$
+	\begin{equation}
+		\alpha_P = \frac{1}{\rho} \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T.
+	\end{equation}
+	or for $\alpha^*_P$
+	\begin{equation}
+		\alpha^*_P = \frac{\varepsilon\beta_c}{\bar{n}} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
+	\end{equation}
+
 	Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\bar{n}$ for various values of temperature above the critical one.

### 2024-09-02 main_morse_response_functions.tex
yes, under arccos we should have 3, fixed that
add identity alpha_P/K/beta_V = 1

@@
 		 & \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
-		 & \alpha_n = \arccos \left( \frac{3}{2} \left( - \frac{g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber
+		 & \alpha_n = \arccos \left( \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber 
 	\end{align}
-	{\color{Red} {\bf{NOTE 2: }} Roma: In my opinion, under {\it{arccos}} we should have 3, not $\frac{3}{2}$}
+	{\color{Red} {\bf{NOTE 2: }} Roma: In my opinion, under {\it{arccos}} we should have 3, not $\frac{3}{2}$ \color{Green} Oksana: Yes, you are right, I've fixed that }
 
@@
 
+	\subsection{Relation between response functions}
+	The following thermodynamic identity holds between the calculated response functions
+	\begin{equation}
+		\frac{\alpha_P}{K_T \beta_V} = \frac{\alpha^*_P}{K^*_T \beta^*_V} = 1,
+	\end{equation}
+	which is easily derived from the cyclic relation between $P$, $V$ and $T$.
+In our case, this equality is exactly reproduced by substituting explicit expressions for $K_T$, $\alpha_P$, and $\beta_V$ obtained from the equation of state~\eqref{eq:eosMT} (or~\eqref{eq:eosNT}).
+
 	\newpage

### 2024-09-03 main_morse_response_functions.tex
remove notes
introduce reduced temperature

@@
 	\end{equation}
-	{\color{Red} {\bf{NOTE 1: }} Quantities $\alpha^*$ has the dimension of volume.}
 
@@
 	\end{equation*}
+	We also use the reduced temperature defined as $T = k_{\rm B}T/\varepsilon$, and its critical value $T^*_c = 4.995.$
+
 	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature.
@@
 		\label{eq:eosPTM_reduced}
-		P^* = \frac{1 + \tau}{\varepsilon \beta_c} \left( E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4 \right).
+		P^* = (1 + \tau)T^*_c \left( E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4 \right).
 	\end{equation}
@@
 	\end{align}
-	{\color{Red} {\bf{NOTE 2: }} Roma: In my opinion, under {\it{arccos}} we should have 3, not $\frac{3}{2}$ \color{Green} Oksana: Yes, you are right, I've fixed that }
 
@@
  	\label{eq:eosPTn_reduced}
- 	P^* = \frac{1 + \tau}{\varepsilon \beta_c} \left(E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\right).
+ 	P^* = (1 + \tau)T^*_c \left(E_\eta (\bar{n},T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\right).
  \end{equation}
@@
 	\begin{equation}
-		\beta^*_V = \varepsilon\beta_c 
+		\beta^*_V = \frac{1}{T^*_c} 
 		\left[ \left(\frac{\partial P^*}{\partial \tau}\right)_{\mu} 
@@
 	\begin{equation}
-		\beta^*_V = \varepsilon\beta_c \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}
+		\beta^*_V = \frac{1}{T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}
 	\end{equation}
@@
 	\begin{equation}
-		\alpha^*_P = \varepsilon \beta_c 
+		\alpha^*_P = \frac{1}{T^*_c}
 		\left( 
@@
 	\begin{equation}
-		\alpha^*_P = \frac{\varepsilon\beta_c}{\bar{n}} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
+		\alpha^*_P = \frac{1}{\bar{n} T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
 	\end{equation}

### 2024-09-03 main_morse_response_functions.tex
extend introduction

@@
 
-	\section{The interaction potential}
+	As the problem was considered in the framework of the grand canonical ensemble, the initial equation of state is formulated in terms of pressure $P$, temperature $T$ and the chemical potential $\mu$, $P = P(T,\mu)$.
+To leverage this form of the equation of state for calculation of the response functions, the corresponding definitions should be transformed to proper derivatives with respect to temperature and chemical potential~\cite{StrokerMeier2021}.
+For each response function considered in this paper, we present such transformation in a dedicated subsection.
+On the other hand, within the approach applied here, the chemical potential can be explicitly expressed via the number particle density $\rho$ and temperature.
+This gives rise to the equation of state in the form $P = P(T, \rho)$, in which case it is suitable to re-express the response functions in terms of derivatives with respect to temperature and density.
+
+	In Section~\ref{sec:potential} we present the modified Morse potential used in our work, and briefly compare it with other possible modifications.
+Section~\ref{sec:eos} is dedicated to the explicit expressions for the equation of state.
+In Section~\ref{sec:respons_functions} the expressions for response functions are derived in terms of thermodynamic derivatives suitable for different forms of the equation of state.
+
+	\section{\label{sec:potential}The interaction potential}
 	The potential of interaction between particles is taken in a form of a modified Morse potential

### 2024-09-03 main_morse_response_functions.tex
add appendix for explicit expressions of derivatives

@@
 	\begin{equation}
+	\label{def:D0}
 	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
@@
 
-	\newpage
+	%\newpage
 
@@
 	Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
+
+	\appendix
+	\renewcommand{\theequation}{A.\arabic{equation}}
+	\setcounter{equation}{0}
+
+	\section{\label{sec:app-a} Explicit expressions for derivatives}
+	In this appendinx, explicit expressions are presented for derivatives of quantities entering the equation of state, with respect to temperature.
+This expressions are useful while calculating the response functions in Section~\ref{sec:respons_functions}.
+
+	For the quantity $\bar{M}$ from Eq.~\eqref{eq:M_nT} one has
+	\begin{equation}
+		\left( \frac{\partial \bar{M}}{\partial \tau} \right)_{\bar{n}} =
+		\frac{k_{\rm B}T_c \rho_n}{W(0)} \frac{1 - \omega_0}{1 + \tau\omega_0},
+	\end{equation}
+	where
+	\begin{equation*}
+		\omega_0 = \frac{\chi_0 + A_{\gamma}}{B - 1 + \chi_0}.
+	\end{equation*}
+	For $\tilde{D}(0)$ from~\eqref{def:D0} one has
+	\begin{equation}
+		\frac{\partial \tilde{D}(0)}{\partial \tau} = -\frac{k_{\rm B}T_c}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0}.
+	\end{equation}
 

### 2024-09-03 main_morse_response_functions.tex
add explicit derivative calculation for beta_V

@@
 	\end{equation}
- The function $E_\nu (\bar n, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}.
+ The quantity $E_\nu (\bar n, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}
+	\begin{eqnarray}\label{eq:E_nu}
+ 		E_\nu (\bar{n}, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 
+ 		\nonumber\\
+ 		&& - \frac{\beta W(0)}{2} 
+ 		\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
+ 		\nonumber\\
+ 		&& - \frac{g_3}{g_4} {\bar{M}} - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
+ 	\end{eqnarray}
  For the reduced pressure we write
@@
 	\begin{equation}
+		\label{eq:beta_star_m}
 		\beta^*_V = \frac{1}{T^*_c} 
@@
 	\begin{equation}
+		\label{eq:beta_star_n}
 		\beta^*_V = \frac{1}{T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}
@@
 	\section{\label{sec:app-a} Explicit expressions for derivatives}
-	In this appendinx, explicit expressions are presented for derivatives of quantities entering the equation of state, with respect to temperature.
+	In this appendix, explicit expressions are presented for derivatives of quantities entering the equation of state, with respect to temperature.
 This expressions are useful while calculating the response functions in Section~\ref{sec:respons_functions}.
@@
 	\end{equation}
+	While calculating both derivatives, we take into account
+	\begin{equation}
+		\frac{\partial}{\partial \tau} \left[\beta W(0)\right] = -\frac{\beta_c \Phi^{(r)}(0)}{(1+\tau)^2} (B - 1 - A_{\gamma}).
+	\end{equation}
+	The derivative of the quantity $E_\nu$ from~\eqref{eq:E_nu} with respect to temperature $\tau$ is
+	\begin{eqnarray}
+		\frac{\partial E_\nu}{\partial \tau} & = &  -\frac{1}{2}\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
+		\frac{\partial \beta W(0)}{\partial \tau} 
+		\nonumber\\
+		&&-\beta W(0)\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)
+		\nonumber\\
+		&& \times \left(\frac{\partial \bar{M}}{\partial \tau} + \frac{g_3}{g_4}\frac{\partial\tilde{D}(0)}{\partial \tau}\right)
+		\nonumber\\
+		&& -\frac{g_3}{g_4}\frac{\partial \bar{M}}{\partial \tau} 
+		- \frac{g_3^2}{2g_4^2}\frac{\partial \tilde{D}(0)}{\partial \tau}.
+	\end{eqnarray}
+	Collecting these all formulas together, we can explicitly calculate $\beta^*_V$ from~\eqref{eq:beta_star_n}
+	\begin{eqnarray}
+		\beta^*_V & = & E_\eta (\bar{n},T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
+		\nonumber\\
+		&& + (1+\tau) \left(\frac{\partial E_{\nu}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial \tilde{D}(0)}{\partial \tau}\right).
+	\end{eqnarray}
 

### 2024-09-09 main_morse_response_functions.tex
separated the main text into a dedicated file

--- 2024-09-03 main_morse_response_functions.tex
@@
 
-	\abstract{Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
-These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble.
-The calculated quantities are presented graphically as functions of density and chemical potential.
-	\\	
-	\textbf{Keywords:} Simple fluids, Morse potential, Thermodynamic response functions.
-	}
-	\section{Introduction}
-
-	In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}.
-In works~\cite{KozlovskiiDobush2020,PylyukDobush2020,PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} this model was used with a modified Morse potential describing the particle interaction.
-In particular, the equation of state was obtained in~\cite{KozlovskiiDobush2020} in the zero-mode approximation.
-This equation of state is used in the current work to calculate thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient.
-
-	As the problem was considered in the framework of the grand canonical ensemble, the initial equation of state is formulated in terms of pressure $P$, temperature $T$ and the chemical potential $\mu$, $P = P(T,\mu)$.
-To leverage this form of the equation of state for calculation of the response functions, the corresponding definitions should be transformed to proper derivatives with respect to temperature and chemical potential~\cite{StrokerMeier2021}.
-For each response function considered in this paper, we present such transformation in a dedicated subsection.
-On the other hand, within the approach applied here, the chemical potential can be explicitly expressed via the number particle density $\rho$ and temperature.
-This gives rise to the equation of state in the form $P = P(T, \rho)$, in which case it is suitable to re-express the response functions in terms of derivatives with respect to temperature and density.
-
-	In Section~\ref{sec:potential} we present the modified Morse potential used in our work, and briefly compare it with other possible modifications.
-Section~\ref{sec:eos} is dedicated to the explicit expressions for the equation of state.
-In Section~\ref{sec:respons_functions} the expressions for response functions are derived in terms of thermodynamic derivatives suitable for different forms of the equation of state.
-
-	\section{\label{sec:potential}The interaction potential}
-	The potential of interaction between particles is taken in a form of a modified Morse potential
-	\begin{equation}
-		\label{def:mod_morse}
-		U(r) = \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
-	\end{equation}
-	where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model.
-Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
-	\begin{equation}
-		C_{H} = \frac{n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
-	\end{equation}
-	where $\varepsilon$ is the depth of the potential well at $r=R_0$.
-This potential is reduced to the ordinary Morse potential~\cite{Morse1929} at $\gamma=2$.
-For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~\cite{KozlovskiiDobush2020}.
-
-	Modifications of the Morse potential were used in other works as well.
-For example, in~\cite{MartinezValenciaEtAl2013} a repulsive term in a form of a power of $r^{-1}$ was added to the ordinary Morse potential, and the influence of the softness of such a term was investigated on the coordinates of the critical point.
-The generalized form of the Morse potential was suggested in~\cite{BiswasHamann1985}
-	\begin{equation}
-		U(r) = A_1 {\rm e}^{-\lambda_1 r} + A_2 {\rm e}^{-\lambda_2 r}
-	\end{equation} 
-	with application to silicon structural energies, and was also considered in~\cite{Lim2005} as the potential for Be-S and H-Na compounds.
-
-	Our modification contains an additional repulsive term, similar to~\cite{MartinezValenciaEtAl2013}, as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential.
-Including the repulsive term enables us to single out a reference system and apply the method of collective variables to calculating the grand partition function~[REFERENCE NEEDED].
-
-	\section{\label{sec:eos}The equation of state}
-	\subsection{Pressure as a function of temperature and chemical potential}
-	The equation of state obtained in~\cite[see Eq.(42)]{KozlovskiiDobush2020} reads
-	\begin{equation}
-		\label{eq:eosMT}
-		Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
-	\end{equation}
-	The quantities in the left-hand side of the equation are $P$, the pressure; $\beta = (k_{\rm B} T)^{-1}$, the inverse temperature; $k_{\rm B}$, the Boltzmann constant; $T$, the temperature; $v$, cell volume.
-The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential $\mu$.
-Let us present their expressions explicitly.
-
-	First, the quantity $M$ depends linearly on the chemical potential
-	\begin{align}\label{chem_pot}
-		&	M = \frac{\tilde\mu}{W(0)} + g_1 - \frac{g_3}{g_4} \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
-		&	\tilde\mu=\mu-\mu^*(1+\tau),
-	\end{align}
-	where $\mu^*$ is some positive constant, $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$, $T_c$ is the critical temperature. We will call $M$ the effective chemical potential.
-
-	The quantity $W(0)$ is expressed via parameters of the potential~(\ref{def:mod_morse}) as follows
-	\begin{equation}
-	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right],
-	\end{equation}
-	where
-	\begin{align*} 
-		& B = 2 \gamma^3 e^{(1-\gamma)R_0/\alpha},
-		\nonumber \\
-		& A_\gamma = A e^{(n_0-\gamma)R_0/\alpha} \left( \gamma / n_0\right)^3, 
-	\end{align*}
-	and $\Phi^{(r)}(0)$ is the Fourier transform of the repulsive part of the potential at $\abs{\vb k}=0$
-	\begin{equation*}
-		\Phi^{(r)}(0) = \varepsilon C_H 8\pi {\rm e}^{\gamma R_0/\alpha} \left(\frac{\alpha}{\gamma R_0}\right)^3.
-	\end{equation*}
-
-	The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a contribution in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$~\cite[see Eq.(24)]{KozlovskiiDobush2020}.
-
-	The coefficients $g_n$ are given by the formulas:
-	\begin{align}
-		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
-		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, \nonumber\\
-		& a_4 = -g_4,
-	\end{align}
-	where $T_n(p,\alpha^*)$ are the following special functions
-	\begin{equation}
-		T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n {\rm e}^{-pm^2}.
-	\end{equation}
-	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
-	\begin{equation}
-		p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
-	\end{equation}
-
-	The quantity $\beta_c$ denotes the critical value of the inverse temperature. In~\cite[see Eq.(31)]{KozlovskiiDobush2020} it was found that
-	\begin{equation*}
-		\varepsilon\beta_c = 0.200, \quad \frac{k_{\rm B} T_c}{\varepsilon} = 4.995.
-	\end{equation*}
-	We also use the reduced temperature defined as $T = k_{\rm B}T/\varepsilon$, and its critical value $T^*_c = 4.995.$
-
-	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature.
-The numerical values for other coefficients used in this paper are the same as those in~\cite[see Eqs.(5), (23), and (24)]{KozlovskiiDobush2020}:
-	\begin{eqnarray}
-		\label{params}
-		\chi_0 = 0.07, & \quad \gamma = 1.65, \nonumber\\
-		n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \nonumber\\
-		\alpha^* = 5.0 & \quad p = 1.0.
-	\end{eqnarray}
-
-	The quantity $\tilde D(0)$ entering equations~\eqref{eq:eosMT} and~\eqref{chem_pot} is a function of temperature
-	\begin{equation}
-	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
-	\end{equation}
-	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite[see Eq.(31)]{KozlovskiiDobush2020}
-	\begin{equation}
-		k_{\rm B}T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
-	\end{equation}
-
-	The function $E_\mu(M, T)$ from the equation \eqref{eq:eosMT} is provided by
-	\begin{eqnarray}\label{eq:E_mu}
-		E_\mu (M, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 - \frac{\beta W(0)}{2} 
-		\left(\frac{\tilde\mu}{W(0)} \right)^{2} 
-		\nonumber\\
-		&& - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
-	\end{eqnarray}
-	Here the quantity $N_v$ defines the number of cubic cells in volume $V$ for the initial model.
-	In the thermodynamic limit, $N_v \to \infty$, and thus the first term can be neglected.
-The term $\tilde{\mu}/W(0)$ can be expressed in terms of $M$ using~\eqref{chem_pot}.
-The temperature and the inverse temperature can always be expressed in terms of the reduced temperature and a corresponding critical value:
-	\begin{equation*}
-		T = T_c(1+\tau), \quad \beta = \beta_c (1 + \tau)^{-1}
-	\end{equation*}
-
-	The quantity $\bar{\rho}_0$ is a solution to the following cubic equation
-	\begin{equation}\label{eq:ro_M}
-	M + \tilde D(0) \bar\rho_0 - \frac{a_4}{6} \bar\rho_0^3 = 0.
-	\end{equation}
-	For any $\tau > 0$, the latter equation has one real root
-	\begin{equation}\label{eq:ro_MT}
-	\bar \rho_0 = \left(- \frac{3 M}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3 M}{g_4} + \sqrt{Q_t} \right)^{1/3},
-	\end{equation}
-	where
-	\begin{equation}
-	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3 M}{g_4}\right)^2, \qquad g_4<0.
-	\end{equation}
-	Thus, $\bar{\rho}_0$ is a function of the temperature and the chemical potential.
-
-	Let us introduce the reduced pressure
-	\begin{equation}
-		\label{def:reduced_pres}
-		P^* \equiv \frac{P v}{\varepsilon}.
-	\end{equation}
-	Considering the equation of state~\eqref{eq:eosMT}, $P^*$ is explicitly written as
-	\begin{equation}
-		\label{eq:eosPTM_reduced}
-		P^* = (1 + \tau)T^*_c \left( E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4 \right).
-	\end{equation}
-	This equation can be easily represented graphically.
-Figure~\ref{fig1} illustrates the relationship between the reduced pressure $P^*$ and the effective chemical potential $M$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
-At the critical point $M=0, \tau=0$, $P^*_c = 1.606$.
-
-	\subsection{Pressure as a function of temperature and density}
-	In this work, by density we mean the particle number density $\rho = \langle N \rangle / V$.
-	In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to $\beta \mu$
-	\begin{eqnarray*}
-		\langle N \rangle & = & \left(\frac{\partial \ln\Xi}{\partial \beta \mu}\right)_{T,V} 
-		\\
-		& = & \left(\frac{\partial (PV)}{\partial \mu}\right)_{T,V}
-		\\
-		& = & V \left(\frac{\partial P}{\partial \mu}\right)_{T,V}.
-	\end{eqnarray*}
-	From this equation it follows
-	\begin{equation*}
-		\frac{\langle N \rangle}{V} = \frac{\langle N \rangle}{v N_v} = \left(\frac{\partial P}{\partial \mu}\right)_{T,V}
-	\end{equation*}
-	and thus
-	\begin{equation}
-		\bar{n} \equiv \frac{\langle N \rangle}{V} v = \frac{\langle N \rangle}{N_v} = v \left(\frac{\partial P}{\partial \mu}\right)_{T,V} 
-		= \left(\frac{\partial (Pv\beta)}{\partial (\beta \mu)}\right)_{T,V}.
-	\end{equation}
-	The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density. In the context of the cell model, on the other hand, it is the average number of particles per cell.
-	Taking explicit derivatives, we arrive at
-	\begin{equation}\label{eq:density}
-	\bar n = n_g - M + \frac{ \bar \rho_0}{\beta W(0)}.
-	\end{equation}
-	The quantity $n_g$ in the equation \eqref{eq:density} is the critical density
-	\begin{eqnarray}\label{eq:crit_dens}
-	n_g & = & g_1 - \frac{g_3}{g_4}\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right) - \frac{1}{6} \frac{g_3^3}{g_4^2} 
-	\nonumber\\
-	& = & g_1 - \frac{g_2 g_3}{g_4} + \frac{g_3^3}{3g_4^2}
-	\end{eqnarray}
-	Its numerical value for parameters~\eqref{params} is
-	\begin{equation*}
-		n_g = 0.978.
-	\end{equation*}
-	Equations~\eqref{eq:density} and~\eqref{eq:eosMT} jointly define a parametric relationship between pressure and density, with $M$ serving as the parameter.
-Figure~\ref{fig1} shows the dependency of the reduced pressure $P^*$ on the density $\bar{n}$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
-
-	This dependency can also be expressed explicitly.
-To achieve this, we combine the equations~\eqref{eq:density} and~\eqref{eq:ro_M} to express the effective chemical potential $M$ as a function of density and temperature:
-	\begin{equation}\label{eq:M_nT}
-		\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g),
-	\end{equation}
-	where
-	\begin{align} \label{eq:ro_nT}
-		 & \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
-		 & \alpha_n = \arccos \left( \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber 
-	\end{align}
-
-	At $T>T_c$ the equation of state of a cell fluid model in terms of the density and the temperature has the following form
-	\begin{equation}\label{eq:eosNT}
-	Pv\beta = E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4,
-	\end{equation}
- The function $E_\nu (\bar n, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}.
-For the reduced pressure we write
- \begin{equation}
- 	\label{eq:eosPTn_reduced}
- 	P^* = (1 + \tau)T^*_c \left(E_\eta (\bar{n},T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\right).
- \end{equation}
-
-	Figure~1 shows the isotherms for the pressure $P^*$ versus density $\bar{n}$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
-	\begin{figure}[h!]
-		%\centering 
-		\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
-		\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
-		\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function of the density $\bar n$ (on the left-hand side) and a function of the effective chemical potential $M$ (on the right-hand side) at $T \geq T_c$ represented by black lines.
-Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
-		}\label{fig1}
-	\end{figure}
-
-	Thus, in this Section, we presented two forms of the equation of state.
-The first one expresses the pressure as a function of temperature and chemical potential, $P = P(T, \mu)$, and is represented by equivalent Eqs.~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}.
-The second one expresses the pressure as a function of temperature and density, $P = P(T, \bar{n})$, and is represented by equivalent Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
-These equations, together with the explicit dependency of density on temperature and chemical potential, $\bar{n} = \bar{n}(T, \mu)$, see Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}
-
-	\section{\label{sec:respons_functions}Thermodynamic response functions}
-
-	\subsection{Isothermal compressibility}
-	The isothermal compressibility is defined by
-	\begin{equation}
-		\label{def:isotherm_compres}
-		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}.
-	\end{equation}
-	Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
-	\begin{eqnarray*}
-		K_T & = & - \frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}
-		\\
-		& = & -\rho \left(\frac{\partial \left(\frac{1}{\rho}\right)}{\partial P}\right)_{T,\langle N\rangle}
-		\\
-		& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,\langle N\rangle}
-		\\
-		& = & \frac{1}{\rho} \frac{\left(\partial \rho / \partial \mu\right)_{T}}
-		{\left(\partial P / \partial \mu\right)_{T}},
-	\end{eqnarray*}
-	where $\rho = \langle N \rangle / V$ is the particle number density.
-We have omitted the condition of constant $\langle N \rangle$ in the last line of the above equation since we have explicit dependencies on temperature and chemical potential for both pressure $P = P(T, \mu)$, see Eq.~\eqref{eq:eosMT}, and density $\rho = \rho(T, \mu)$, see Eq.~\eqref{eq:density}.
-	Applying the Gibbs--Duhem equation
-	\begin{equation}
-		N{\rm d}\mu = -S{\rm d}T + V{\rm d}P,
-	\end{equation}
-	at $T = const$ one has 
-	\begin{equation*}
-		{\rm d} P = \rho {\rm d} \mu,
-	\end{equation*}
-	or
-	\begin{equation}
-		\label{eq:rho_dpdm}
-		\rho = \left(\frac{\partial P}{\partial \mu}\right)_T.
-	\end{equation}
-	Substituting this into the last expression for $K_T$, one gets
-	\begin{equation}
-		K_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
-	\end{equation}
-	Finally, from~\eqref{eq:rho_dpdm} it follows that
-	\begin{equation}
-		\left(\frac{\partial \rho}{\partial \mu}\right)_T = \left(\frac{\partial^2 P}{\partial \mu^2}\right)_T
-	\end{equation}
-	and ultimately we arrive at the very useful expression for the isothermal compressibility
-	\begin{equation}
-		K_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T}
-	\end{equation}
-
-	Let us introduce the reduced isothermal compressibility
-	\begin{equation}
-		K^*_T \equiv \frac{\varepsilon K_T}{v}.
-	\end{equation}
-	The quantity $K^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent.
-It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
-	\begin{eqnarray}
-		K^*_T & = & \frac{\varepsilon}{\bar{n}^2} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_T
-		\nonumber\\
-		& = & \frac{\varepsilon^2}{\bar{n}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
-	\end{eqnarray}
-	Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $K^*_T$, with the result expressed as a function of temperature and chemical potential.
-
-	If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the isothermal compressibility are
-	\begin{equation}
-		K_T = \frac{1}{\bar{n}} \left(\frac{\partial P}{\partial \bar{n}}\right)^{-1}_T
-	\end{equation}
-	and 
-	\begin{equation}
-		K^*_T = \frac{1}{\bar{n}} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
-	\end{equation}
-
-	Figure~\ref{fig2a} illustrates the dependency of the compressibility $K^*_T$ on the density $\bar{n}$ for various values of temperature above the critical one.
-The dependency of $K^*_T$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig2b}.
-
-	\begin{figure}[h!]
-		\centering \includegraphics[width=0.5\textwidth]{f2a.pdf}
-		\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
-		}\label{fig2a}
-	\end{figure}
-
-	\begin{figure}[h!]
-		\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
-		\includegraphics[width=0.475\textwidth]{f2c.pdf}
-		\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
-The two figures differ in the scale of $M$.
-The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
-		}\label{fig2b}
-	\end{figure}
-
-	\subsection{Thermal pressure coefficient}
-	The thermal pressure coefficient is defined by
-	\begin{equation}
-		\label{def:therm_pres_coef}
-		\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,\langle N \rangle}.
-	\end{equation}
-	We rewrite $\beta_V$ into a form that is suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
-	\begin{eqnarray}
-		\beta_V & = & \left(\frac{\partial P}{\partial T}\right)_{V, N}
-		\nonumber\\
-		& = & \left(\frac{\partial P}{\partial T}\right)_{\mu} + \left(\frac{\partial P}{\partial \mu}\right)_T \left(\frac{\partial \mu}{\partial T}\right)_{V, N}.
-	\end{eqnarray}
-	Applying the cyclic relation
-	\begin{equation*}
-		\left(\frac{\partial \mu}{\partial T}\right)_{V, N} 
-		\left(\frac{\partial T}{\partial V}\right)_{\mu, N}
-		\left(\frac{\partial V}{\partial \mu}\right)_{T, N}
-		= -1
-	\end{equation*}
-	we obtain
-	\begin{eqnarray*}
-		\left(\frac{\partial \mu}{\partial T}\right)_{V, N} 
-		& = & 
-		- \left(\frac{\partial V}{\partial T}\right)_{\mu, N} 
-		\left(\frac{\partial V}{\partial \mu}\right)^{-1}_{T, N} \\
-		& = & - \left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
-		\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}.		
-	\end{eqnarray*}
-	Substituting this result into the formula for $\beta_V$, we arrive at the final expression for the thermal pressure coefficient
-	\begin{equation}
-		\beta_V = \left(\frac{\partial P}{\partial T}\right)_{\mu} 
-		- \left(\frac{\partial P}{\partial \mu}\right)_T 
-		\left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
-		\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}
-	\end{equation}
-	which is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
-	(NB. Compare this equation with Eq.(17) from~\cite{StrokerMeier2021})
-
-	We introduce the reduced thermal pressure coefficient by
-	\begin{equation}
-		\beta^*_V = \frac{v}{k_{\rm B}}\beta_V.
-	\end{equation}
-	It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
-	\begin{equation}
-		\beta^*_V = \frac{1}{T^*_c} 
-		\left[ \left(\frac{\partial P^*}{\partial \tau}\right)_{\mu} 
-		- \left(\frac{\partial P^*}{\partial \mu}\right)_T 
-		\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
-		\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T} 
-		\right].
-	\end{equation}
-
-	If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the thermal pressure coefficient follow immediately from the definition~\eqref{def:therm_pres_coef}
-	\begin{equation}
-		\beta_V = \left(\frac{\partial P}{\partial T}\right)_\rho
-	\end{equation}
-	and
-	\begin{equation}
-		\beta^*_V = \frac{1}{T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}
-	\end{equation}
-
-	\begin{figure}[h!]
-		\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
-		\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
-		}\label{fig3a}
-	\end{figure}
-	\begin{figure}[h!]
-		\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
-		\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
-		}\label{fig3b}
-	\end{figure}
-	\begin{figure}[h!]
-		\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
-		\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\eta$. 
-		}\label{fig3c}
-	\end{figure}
-
-	Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\bar{n}$ for various values of temperature above the critical one.
-The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig3b}.
-
-	\subsection{Thermal expansion coefficient}
-	The thermal expansion coefficient is defined by
-	\begin{equation}
-		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}.
-	\end{equation}
-	We rewrite $\alpha_P$ into a form suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
-	\begin{eqnarray}
-		\alpha_P & = & \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P, N}
-		\nonumber\\
-		\label{eq:alpha_vs_rho}
-		& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{P, N}
-		\\
-		& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{\mu} 
-		 - \frac{1}{\rho} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
-		 \left(\frac{\partial \mu}{\partial T}\right)_{P, N}.
-	\end{eqnarray}
-	Applying the cyclic relation
-	\begin{equation*}
-		\left(\frac{\partial \mu}{\partial T}\right)_{P, N}
-		\left(\frac{\partial T}{\partial P}\right)_{\mu, N}
-		\left(\frac{\partial P}{\partial \mu}\right)_{T, N}
-		= -1
-	\end{equation*}
-	we get
-	\begin{eqnarray*}
-		\left(\frac{\partial \mu}{\partial T}\right)_{P, N} & = & 
-		- \left(\frac{\partial P}{\partial T}\right)_{\mu}
-		\left(\frac{\partial P}{\partial \mu}\right)^{-1}_{T}.
-	\end{eqnarray*}
-	Substituting the result into the expression for $\alpha_P$, we arrive at the final formula for the thermal expansion coefficient
-	\begin{equation}
-		\alpha_P = -\frac{1}{\rho}\left(\frac{\partial \rho}{\partial T}\right)_{\mu}
-		+ \frac{1}{\rho} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
-		\left(\frac{\partial P}{\partial T}\right)_{\mu}
-		\left(\frac{\partial P}{\partial \mu}\right)^{-1}_{T}
-	\end{equation}
-	which is readily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
-	(NB. Compare this equation with Eqs.(57)-(58) from~\cite{StrokerMeier2021})
-
-	We introduce the reduced thermal expansion coefficient by
-	\begin{equation}
-		\alpha^*_P = \frac{\varepsilon}{k_{\rm B}} \alpha_P.
-	\end{equation}
-	It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
-	\begin{equation}
-		\alpha^*_P = \frac{1}{T^*_c}
-		\left( 
-		-\frac{1}{\bar{n}}\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
-		+ \frac{1}{\bar{n}} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
-		\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
-		\left(\frac{\partial P^*}{\partial \mu}\right)^{-1}_{T} 
-		\right).
-	\end{equation}
-
-	If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then we need to rewrite the definition for $\alpha_P$ accordingly.
-We start with~\eqref{eq:alpha_vs_rho} and apply the cyclic relation
-	\begin{equation}
-		\left(\frac{\partial \rho}{\partial T}\right)_P = - \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T
-	\end{equation}
-	to get for $\alpha_P$
-	\begin{equation}
-		\alpha_P = \frac{1}{\rho} \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T.
-	\end{equation}
-	or for $\alpha^*_P$
-	\begin{equation}
-		\alpha^*_P = \frac{1}{\bar{n} T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
-	\end{equation}
-
-	Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\bar{n}$ for various values of temperature above the critical one.
-The dependency of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Figure~\ref{fig4b}.
-
-	\begin{figure}[h!]
-		\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
-		\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
-		}\label{fig4a}
-	\end{figure}
-
-	\begin{figure}[h!]
-		\centering \includegraphics[width=0.45\textwidth]{f4b.pdf}
-		\includegraphics[width=0.475\textwidth]{f4c.pdf}
-		\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
-The two figures differ in the scale of $M$.
-The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
-		}\label{fig4b}
-	\end{figure}
-
-	\subsection{Relation between response functions}
-	The following thermodynamic identity holds between the calculated response functions
-	\begin{equation}
-		\frac{\alpha_P}{K_T \beta_V} = \frac{\alpha^*_P}{K^*_T \beta^*_V} = 1,
-	\end{equation}
-	which is easily derived from the cyclic relation between $P$, $V$ and $T$.
-In our case, this equality is exactly reproduced by substituting explicit expressions for $K_T$, $\alpha_P$, and $\beta_V$ obtained from the equation of state~\eqref{eq:eosMT} (or~\eqref{eq:eosNT}).
-
-	\newpage
-
-	\section{Conclusions}
-	Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
+	\input{./paper_text.tex}
 

### 2024-09-09 paper_text.tex
separated the main text into a dedicated file

\abstract{Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential. These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble. The calculated quantities are presented graphically as functions of density and chemical potential.
	\\	
	\textbf{Keywords:} Simple fluids, Morse potential, Thermodynamic response functions.
}
\section{Introduction}

In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}. In works~\cite{KozlovskiiDobush2020,PylyukDobush2020,PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} this model was used with a modified Morse potential describing the particle interaction. In particular, the equation of state was obtained in~\cite{KozlovskiiDobush2020} in the zero-mode approximation. This equation of state is used in the current work to calculate thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient.

As the problem was considered in the framework of the grand canonical ensemble, the initial equation of state is formulated in terms of pressure $P$, temperature $T$ and the chemical potential $\mu$, $P = P(T,\mu)$. To leverage this form of the equation of state for calculation of the response functions, the corresponding definitions should be transformed to proper derivatives with respect to temperature and chemical potential~\cite{StrokerMeier2021}. For each response function considered in this paper, we present such transformation in a dedicated subsection. On the other hand, within the approach applied here, the chemical potential can be explicitly expressed via the number particle density $\rho$ and temperature. This gives rise to the equation of state in the form $P = P(T, \rho)$, in which case it is suitable to re-express the response functions in terms of derivatives with respect to temperature and density.

In Section~\ref{sec:potential} we present the modified Morse potential used in our work, and briefly compare it with other possible modifications. Section~\ref{sec:eos} is dedicated to the explicit expressions for the equation of state. In Section~\ref{sec:respons_functions} the expressions for response functions are derived in terms of thermodynamic derivatives suitable for different forms of the equation of state.

\section{\label{sec:potential}The interaction potential}
The potential of interaction between particles is taken in a form of a modified Morse potential
\begin{equation}
	\label{def:mod_morse}
	U(r) = \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
\end{equation}
where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model. Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
\begin{equation}
	C_{H} = \frac{n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
\end{equation}
where $\varepsilon$ is the depth of the potential well at $r=R_0$. This potential is reduced to the ordinary Morse potential~\cite{Morse1929} at $\gamma=2$. For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~\cite{KozlovskiiDobush2020}.

Modifications of the Morse potential were used in other works as well. For example, in~\cite{MartinezValenciaEtAl2013} a repulsive term in a form of a power of $r^{-1}$ was added to the ordinary Morse potential, and the influence of the softness of such a term was investigated on the coordinates of the critical point. The generalized form of the Morse potential was suggested in~\cite{BiswasHamann1985}
\begin{equation}
	U(r) = A_1 {\rm e}^{-\lambda_1 r} + A_2 {\rm e}^{-\lambda_2 r}
\end{equation} 
with application to silicon structural energies, and was also considered in~\cite{Lim2005} as the potential for Be-S and H-Na compounds.

Our modification contains an additional repulsive term, similar to~\cite{MartinezValenciaEtAl2013}, as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential. Including the repulsive term enables us to single out a reference system and apply the method of collective variables to calculating the grand partition function~[REFERENCE NEEDED].

\section{\label{sec:eos}The equation of state}
\subsection{Pressure as a function of temperature and chemical potential}
The equation of state obtained in~\cite[see Eq.(42)]{KozlovskiiDobush2020} reads
\begin{equation}
	\label{eq:eosMT}
	Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
\end{equation}
The quantities in the left-hand side of the equation are $P$, the pressure; $\beta = (k_{\rm B} T)^{-1}$, the inverse temperature; $k_{\rm B}$, the Boltzmann constant; $T$, the temperature; $v$, cell volume. The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential $\mu$. Let us present their expressions explicitly.

First, the quantity $M$ depends linearly on the chemical potential
\begin{align}\label{chem_pot}
	&	M = \frac{\tilde\mu}{W(0)} + g_1 - \frac{g_3}{g_4} \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
	&	\tilde\mu=\mu-\mu^*(1+\tau),
\end{align}
where $\mu^*$ is some positive constant, $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$, $T_c$ is the critical temperature. We will call $M$ the effective chemical potential.

The quantity $W(0)$ is expressed via parameters of the potential~(\ref{def:mod_morse}) as follows
\begin{equation}
	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right],
\end{equation}
where
\begin{align*} 
	& B = 2 \gamma^3 e^{(1-\gamma)R_0/\alpha},
	\nonumber \\
	& A_\gamma = A e^{(n_0-\gamma)R_0/\alpha} \left( \gamma / n_0\right)^3, 
\end{align*}
and $\Phi^{(r)}(0)$ is the Fourier transform of the repulsive part of the potential at $\abs{\vb k}=0$
\begin{equation*}
	\Phi^{(r)}(0) = \varepsilon C_H 8\pi {\rm e}^{\gamma R_0/\alpha} \left(\frac{\alpha}{\gamma R_0}\right)^3.
\end{equation*}

The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a contribution in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$~\cite[see Eq.(24)]{KozlovskiiDobush2020}.

The coefficients $g_n$ are given by the formulas:
\begin{align}
	& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
	& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, \nonumber\\
	& a_4 = -g_4,
\end{align}
where $T_n(p,\alpha^*)$ are the following special functions
\begin{equation}
	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n {\rm e}^{-pm^2}.
\end{equation}
Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
\begin{equation}
	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
\end{equation}

The quantity $\beta_c$ denotes the critical value of the inverse temperature. In~\cite[see Eq.(31)]{KozlovskiiDobush2020} it was found that
\begin{equation*}
	\varepsilon\beta_c = 0.200, \quad \frac{k_{\rm B} T_c}{\varepsilon} = 4.995.
\end{equation*}
We also use the reduced temperature defined as $T = k_{\rm B}T/\varepsilon$, and its critical value $T^*_c = 4.995.$

Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature. The numerical values for other coefficients used in this paper are the same as those in~\cite[see Eqs.(5), (23), and (24)]{KozlovskiiDobush2020}:
\begin{eqnarray}
	\label{params}
	\chi_0 = 0.07, & \quad \gamma = 1.65, \nonumber\\
	n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \nonumber\\
	\alpha^* = 5.0 & \quad p = 1.0.
\end{eqnarray}

The quantity $\tilde D(0)$ entering equations~\eqref{eq:eosMT} and~\eqref{chem_pot} is a function of temperature
\begin{equation}
	\label{def:D0}
	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
\end{equation}
The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite[see Eq.(31)]{KozlovskiiDobush2020}
\begin{equation}
	k_{\rm B}T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
\end{equation}

The function $E_\mu(M, T)$ from the equation \eqref{eq:eosMT} is provided by
\begin{eqnarray}\label{eq:E_mu}
	E_\mu (M, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 - \frac{\beta W(0)}{2} 
	\left(\frac{\tilde\mu}{W(0)} \right)^{2} 
	\nonumber\\
	&& - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
\end{eqnarray}
Here the quantity $N_v$ defines the number of cubic cells in volume $V$ for the initial model.
In the thermodynamic limit, $N_v \to \infty$, and thus the first term can be neglected. The term $\tilde{\mu}/W(0)$ can be expressed in terms of $M$ using~\eqref{chem_pot}. The temperature and the inverse temperature can always be expressed in terms of the reduced temperature and a corresponding critical value:
\begin{equation*}
	T = T_c(1+\tau), \quad \beta = \beta_c (1 + \tau)^{-1}
\end{equation*}

The quantity $\bar{\rho}_0$ is a solution to the following cubic equation
\begin{equation}\label{eq:ro_M}
	M + \tilde D(0) \bar\rho_0 - \frac{a_4}{6} \bar\rho_0^3 = 0.
\end{equation}
For any $\tau > 0$, the latter equation has one real root
\begin{equation}\label{eq:ro_MT}
	\bar \rho_0 = \left(- \frac{3 M}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3 M}{g_4} + \sqrt{Q_t} \right)^{1/3},
\end{equation}
where
\begin{equation}
	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3 M}{g_4}\right)^2, \qquad g_4<0.
\end{equation}
Thus, $\bar{\rho}_0$ is a function of the temperature and the chemical potential.

Let us introduce the reduced pressure
\begin{equation}
	\label{def:reduced_pres}
	P^* \equiv \frac{P v}{\varepsilon}.
\end{equation}
Considering the equation of state~\eqref{eq:eosMT}, $P^*$ is explicitly written as
\begin{equation}
	\label{eq:eosPTM_reduced}
	P^* = (1 + \tau)T^*_c \left( E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4 \right).
\end{equation}
This equation can be easily represented graphically. Figure~\ref{fig1} illustrates the relationship between the reduced pressure $P^*$ and the effective chemical potential $M$ for various values of the reduced temperature $\tau$, at and above the critical temperature. At the critical point $M=0, \tau=0$, $P^*_c = 1.606$.

\subsection{Pressure as a function of temperature and density}
In this work, by density we mean the particle number density $\rho = \langle N \rangle / V$.
In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to $\beta \mu$ 
\begin{eqnarray*}
	\langle N \rangle & = & \left(\frac{\partial \ln\Xi}{\partial \beta \mu}\right)_{T,V} 
	\\
	& = & \left(\frac{\partial (PV)}{\partial \mu}\right)_{T,V}
	\\
	& = & V \left(\frac{\partial P}{\partial \mu}\right)_{T,V}.
\end{eqnarray*}
From this equation it follows
\begin{equation*}
	\frac{\langle N \rangle}{V} = \frac{\langle N \rangle}{v N_v} = \left(\frac{\partial P}{\partial \mu}\right)_{T,V}
\end{equation*}
and thus
\begin{equation}
	\bar{n} \equiv \frac{\langle N \rangle}{V} v = \frac{\langle N \rangle}{N_v} = v \left(\frac{\partial P}{\partial \mu}\right)_{T,V} 
	= \left(\frac{\partial (Pv\beta)}{\partial (\beta \mu)}\right)_{T,V}.
\end{equation}
The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density. In the context of the cell model, on the other hand, it is the average number of particles per cell.
Taking explicit derivatives, we arrive at
\begin{equation}\label{eq:density}
	\bar n = n_g - M + \frac{ \bar \rho_0}{\beta W(0)}.
\end{equation}
The quantity $n_g$ in the equation \eqref{eq:density} is the critical density
\begin{eqnarray}\label{eq:crit_dens}
	n_g & = & g_1 - \frac{g_3}{g_4}\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right) - \frac{1}{6} \frac{g_3^3}{g_4^2} 
	\nonumber\\
	& = & g_1 - \frac{g_2 g_3}{g_4} + \frac{g_3^3}{3g_4^2}
\end{eqnarray}
Its numerical value for parameters~\eqref{params} is
\begin{equation*}
	n_g = 0.978.
\end{equation*}
Equations~\eqref{eq:density} and~\eqref{eq:eosMT} jointly define a parametric relationship between pressure and density, with $M$ serving as the parameter. Figure~\ref{fig1} shows the dependency of the reduced pressure $P^*$ on the density $\bar{n}$ for various values of the reduced temperature $\tau$, at and above the critical temperature.

This dependency can also be expressed explicitly. To achieve this, we combine the equations~\eqref{eq:density} and~\eqref{eq:ro_M} to express the effective chemical potential $M$ as a function of density and temperature:
\begin{equation}\label{eq:M_nT}
	\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g),
\end{equation}
where
\begin{align} \label{eq:ro_nT}
	& \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
	& \alpha_n = \arccos \left( \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber 
\end{align}

At $T>T_c$ the equation of state of a cell fluid model in terms of the density and the temperature has the following form
\begin{equation}\label{eq:eosNT}
	Pv\beta = E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4,
\end{equation}
The quantity $E_\nu (\bar n, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}
\begin{eqnarray}\label{eq:E_nu}
	E_\nu (\bar{n}, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 
	\nonumber\\
	&& - \frac{\beta W(0)}{2} 
	\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
	\nonumber\\
	&& - \frac{g_3}{g_4} {\bar{M}} - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
\end{eqnarray}
For the reduced pressure we write
\begin{equation}
	\label{eq:eosPTn_reduced}
	P^* = (1 + \tau)T^*_c \left(E_\eta (\bar{n},T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\right).
\end{equation}

Figure~1 shows the isotherms for the pressure $P^*$ versus density $\bar{n}$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
\begin{figure}[h!]
	%\centering 
	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function of the density $\bar n$ (on the left-hand side) and a function of the effective chemical potential $M$ (on the right-hand side) at $T \geq T_c$ represented by black lines. Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}. 
	}\label{fig1}
\end{figure}

Thus, in this Section, we presented two forms of the equation of state. The first one expresses the pressure as a function of temperature and chemical potential, $P = P(T, \mu)$, and is represented by equivalent Eqs.~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}. The second one expresses the pressure as a function of temperature and density, $P = P(T, \bar{n})$, and is represented by equivalent Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}. These equations, together with the explicit dependency of density on temperature and chemical potential, $\bar{n} = \bar{n}(T, \mu)$, see Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}

\section{\label{sec:respons_functions}Thermodynamic response functions}

\subsection{Isothermal compressibility}
The isothermal compressibility is defined by
\begin{equation}
	\label{def:isotherm_compres}
	K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}.
\end{equation}
Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
\begin{eqnarray*}
	K_T & = & - \frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}
	\\
	& = & -\rho \left(\frac{\partial \left(\frac{1}{\rho}\right)}{\partial P}\right)_{T,\langle N\rangle}
	\\
	& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,\langle N\rangle}
	\\
	& = & \frac{1}{\rho} \frac{\left(\partial \rho / \partial \mu\right)_{T}}
	{\left(\partial P / \partial \mu\right)_{T}},
\end{eqnarray*}
where $\rho = \langle N \rangle / V$ is the particle number density. We have omitted the condition of constant $\langle N \rangle$ in the last line of the above equation since we have explicit dependencies on temperature and chemical potential for both pressure $P = P(T, \mu)$, see Eq.~\eqref{eq:eosMT}, and density $\rho = \rho(T, \mu)$, see Eq.~\eqref{eq:density}.
Applying the Gibbs--Duhem equation
\begin{equation}
	N{\rm d}\mu = -S{\rm d}T + V{\rm d}P,
\end{equation}
at $T = const$ one has 
\begin{equation*}
	{\rm d} P = \rho {\rm d} \mu,
\end{equation*}
or
\begin{equation}
	\label{eq:rho_dpdm}
	\rho = \left(\frac{\partial P}{\partial \mu}\right)_T.
\end{equation}
Substituting this into the last expression for $K_T$, one gets
\begin{equation}
	K_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
\end{equation}
Finally, from~\eqref{eq:rho_dpdm} it follows that
\begin{equation}
	\left(\frac{\partial \rho}{\partial \mu}\right)_T = \left(\frac{\partial^2 P}{\partial \mu^2}\right)_T
\end{equation}
and ultimately we arrive at the very useful expression for the isothermal compressibility
\begin{equation}
	K_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T}
\end{equation}

Let us introduce the reduced isothermal compressibility
\begin{equation}
	K^*_T \equiv \frac{\varepsilon K_T}{v}.
\end{equation}
The quantity $K^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent. It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
\begin{eqnarray}
	K^*_T & = & \frac{\varepsilon}{\bar{n}^2} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_T
	\nonumber\\
	& = & \frac{\varepsilon^2}{\bar{n}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
\end{eqnarray}
Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $K^*_T$, with the result expressed as a function of temperature and chemical potential.

If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the isothermal compressibility are
\begin{equation}
	K_T = \frac{1}{\bar{n}} \left(\frac{\partial P}{\partial \bar{n}}\right)^{-1}_T
\end{equation}
and 
\begin{equation}
	K^*_T = \frac{1}{\bar{n}} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
\end{equation}

Figure~\ref{fig2a} illustrates the dependency of the compressibility $K^*_T$ on the density $\bar{n}$ for various values of temperature above the critical one. The dependency of $K^*_T$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig2b}.

\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f2a.pdf}
	\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
	}\label{fig2a}
\end{figure}

\begin{figure}[h!]
	\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
	\includegraphics[width=0.475\textwidth]{f2c.pdf}
	\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
	}\label{fig2b}
\end{figure}

\subsection{Thermal pressure coefficient}
The thermal pressure coefficient is defined by
\begin{equation}
	\label{def:therm_pres_coef}
	\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,\langle N \rangle}.
\end{equation}
We rewrite $\beta_V$ into a form that is suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
\begin{eqnarray}
	\beta_V & = & \left(\frac{\partial P}{\partial T}\right)_{V, N}
	\nonumber\\
	& = & \left(\frac{\partial P}{\partial T}\right)_{\mu} + \left(\frac{\partial P}{\partial \mu}\right)_T \left(\frac{\partial \mu}{\partial T}\right)_{V, N}.
\end{eqnarray}
Applying the cyclic relation
\begin{equation*}
	\left(\frac{\partial \mu}{\partial T}\right)_{V, N} 
	\left(\frac{\partial T}{\partial V}\right)_{\mu, N}
	\left(\frac{\partial V}{\partial \mu}\right)_{T, N}
	= -1
\end{equation*}
we obtain
\begin{eqnarray*}
	\left(\frac{\partial \mu}{\partial T}\right)_{V, N} 
	& = & 
	- \left(\frac{\partial V}{\partial T}\right)_{\mu, N} 
	\left(\frac{\partial V}{\partial \mu}\right)^{-1}_{T, N} \\
	& = & - \left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
	\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}.		
\end{eqnarray*}
Substituting this result into the formula for $\beta_V$, we arrive at the final expression for the thermal pressure coefficient
\begin{equation}
	\beta_V = \left(\frac{\partial P}{\partial T}\right)_{\mu} 
	- \left(\frac{\partial P}{\partial \mu}\right)_T 
	\left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
	\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}
\end{equation}
which is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
(NB. Compare this equation with Eq.(17) from~\cite{StrokerMeier2021})

We introduce the reduced thermal pressure coefficient by
\begin{equation}
	\beta^*_V = \frac{v}{k_{\rm B}}\beta_V.
\end{equation}
It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
\begin{equation}
	\label{eq:beta_star_m}
	\beta^*_V = \frac{1}{T^*_c} 
	\left[ \left(\frac{\partial P^*}{\partial \tau}\right)_{\mu} 
	- \left(\frac{\partial P^*}{\partial \mu}\right)_T 
	\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
	\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T} 
	\right].
\end{equation}

If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the thermal pressure coefficient follow immediately from the definition~\eqref{def:therm_pres_coef}
\begin{equation}
	\beta_V = \left(\frac{\partial P}{\partial T}\right)_\rho
\end{equation}
and
\begin{equation}
	\label{eq:beta_star_n}
	\beta^*_V = \frac{1}{T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}
\end{equation}

\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
	}\label{fig3a}
\end{figure}
\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
	}\label{fig3b}
\end{figure}
\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\eta$. 
	}\label{fig3c}
\end{figure}

Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\bar{n}$ for various values of temperature above the critical one. The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig3b}.

\subsection{Thermal expansion coefficient}
The thermal expansion coefficient is defined by
\begin{equation}
	\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}.
\end{equation}
We rewrite $\alpha_P$ into a form suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
\begin{eqnarray}
	\alpha_P & = & \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P, N}
	\nonumber\\
	\label{eq:alpha_vs_rho}
	& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{P, N}
	\\
	& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{\mu} 
	- \frac{1}{\rho} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
	\left(\frac{\partial \mu}{\partial T}\right)_{P, N}.
\end{eqnarray}
Applying the cyclic relation
\begin{equation*}
	\left(\frac{\partial \mu}{\partial T}\right)_{P, N}
	\left(\frac{\partial T}{\partial P}\right)_{\mu, N}
	\left(\frac{\partial P}{\partial \mu}\right)_{T, N}
	= -1
\end{equation*}
we get
\begin{eqnarray*}
	\left(\frac{\partial \mu}{\partial T}\right)_{P, N} & = & 
	- \left(\frac{\partial P}{\partial T}\right)_{\mu}
	\left(\frac{\partial P}{\partial \mu}\right)^{-1}_{T}.
\end{eqnarray*}
Substituting the result into the expression for $\alpha_P$, we arrive at the final formula for the thermal expansion coefficient
\begin{equation}
	\alpha_P = -\frac{1}{\rho}\left(\frac{\partial \rho}{\partial T}\right)_{\mu}
	+ \frac{1}{\rho} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
	\left(\frac{\partial P}{\partial T}\right)_{\mu}
	\left(\frac{\partial P}{\partial \mu}\right)^{-1}_{T}
\end{equation}
which is readily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
(NB. Compare this equation with Eqs.(57)-(58) from~\cite{StrokerMeier2021})

We introduce the reduced thermal expansion coefficient by
\begin{equation}
	\alpha^*_P = \frac{\varepsilon}{k_{\rm B}} \alpha_P.
\end{equation}
It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
\begin{equation}
	\alpha^*_P = \frac{1}{T^*_c}
	\left( 
	-\frac{1}{\bar{n}}\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
	+ \frac{1}{\bar{n}} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
	\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
	\left(\frac{\partial P^*}{\partial \mu}\right)^{-1}_{T} 
	\right).
\end{equation}

If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then we need to rewrite the definition for $\alpha_P$ accordingly. We start with~\eqref{eq:alpha_vs_rho} and apply the cyclic relation
\begin{equation}
	\left(\frac{\partial \rho}{\partial T}\right)_P = - \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T
\end{equation}
to get for $\alpha_P$
\begin{equation}
	\alpha_P = \frac{1}{\rho} \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T.
\end{equation}
or for $\alpha^*_P$
\begin{equation}
	\alpha^*_P = \frac{1}{\bar{n} T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
\end{equation}

Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\bar{n}$ for various values of temperature above the critical one. The dependency of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Figure~\ref{fig4b}.

\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
	}\label{fig4a}
\end{figure}

\begin{figure}[h!]
	\centering \includegraphics[width=0.45\textwidth]{f4b.pdf}
	\includegraphics[width=0.475\textwidth]{f4c.pdf}
	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
	}\label{fig4b}
\end{figure}

\subsection{Relation between response functions}
The following thermodynamic identity holds between the calculated response functions
\begin{equation}
	\frac{\alpha_P}{K_T \beta_V} = \frac{\alpha^*_P}{K^*_T \beta^*_V} = 1,
\end{equation}
which is easily derived from the cyclic relation between $P$, $V$ and $T$. In our case, this equality is exactly reproduced by substituting explicit expressions for $K_T$, $\alpha_P$, and $\beta_V$ obtained from the equation of state~\eqref{eq:eosMT} (or~\eqref{eq:eosNT}).

%\newpage

\section{Conclusions}
Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.

\appendix
\renewcommand{\theequation}{A.\arabic{equation}}
\setcounter{equation}{0}

\section{\label{sec:app-a} Explicit expressions for derivatives}
In this appendix, explicit expressions are presented for derivatives of quantities entering the equation of state, with respect to temperature. This expressions are useful while calculating the response functions in Section~\ref{sec:respons_functions}.

For the quantity $\bar{M}$ from Eq.~\eqref{eq:M_nT} one has
\begin{equation}
	\left( \frac{\partial \bar{M}}{\partial \tau} \right)_{\bar{n}} =
	\frac{k_{\rm B}T_c \rho_n}{W(0)} \frac{1 - \omega_0}{1 + \tau\omega_0},
\end{equation}
where
\begin{equation*}
	\omega_0 = \frac{\chi_0 + A_{\gamma}}{B - 1 + \chi_0}.
\end{equation*}
For $\tilde{D}(0)$ from~\eqref{def:D0} one has
\begin{equation}
	\frac{\partial \tilde{D}(0)}{\partial \tau} = -\frac{k_{\rm B}T_c}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0}.
\end{equation}
While calculating both derivatives, we take into account
\begin{equation}
	\frac{\partial}{\partial \tau} \left[\beta W(0)\right] = -\frac{\beta_c \Phi^{(r)}(0)}{(1+\tau)^2} (B - 1 - A_{\gamma}).
\end{equation}
The derivative of the quantity $E_\nu$ from~\eqref{eq:E_nu} with respect to temperature $\tau$ is
\begin{eqnarray}
	\frac{\partial E_\nu}{\partial \tau} & = &  -\frac{1}{2}\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
	\frac{\partial \beta W(0)}{\partial \tau} 
	\nonumber\\
	&&-\beta W(0)\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)
	\nonumber\\
	&& \times \left(\frac{\partial \bar{M}}{\partial \tau} + \frac{g_3}{g_4}\frac{\partial\tilde{D}(0)}{\partial \tau}\right)
	\nonumber\\
	&& -\frac{g_3}{g_4}\frac{\partial \bar{M}}{\partial \tau} 
	- \frac{g_3^2}{2g_4^2}\frac{\partial \tilde{D}(0)}{\partial \tau}.
\end{eqnarray}
Collecting these all formulas together, we can explicitly calculate $\beta^*_V$ from~\eqref{eq:beta_star_n}
\begin{eqnarray}
	\beta^*_V & = & E_\eta (\bar{n},T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
	\nonumber\\
	&& + (1+\tau) \left(\frac{\partial E_{\nu}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial \tilde{D}(0)}{\partial \tau}\right).
\end{eqnarray}

### 2024-09-09 dobush_et_al_ujp_UTF8.tex
add sty and template files for ujp

\documentclass[fleqn,twoside,twocolumn,nofootinbib,showkeys]{revtex4} % Specifies the document class %,unsortedaddress
%\usepackage[sec]{ujp} % \usepackage[cyr]{ujp} for cyrillic
\usepackage[sec,doi]{ujp_UTF8} % \usepackage[cyr]{ujp_UTF8} for cyrillic

\begin{document}
	\title[Колонтитул: Назва роботи (3-5 слів)/Headline: paper title (3-5 words)]%колонтитул
	{НАЗВА РОБОТИ/PAPER TITLE}%
	\author{Прізвище автора 1/Name of Author 1}%1
	\affiliation{Bogolyubov Institute for Theoretical Physics, Nat. Acad. of Sci. of Ukraine}%інститут 1
	\address{14b, Metrolohichna Str., Kyiv 03143, Ukraine}%адреса 1
	\email{ujp@bitp.kiev.ua}%e-mail 1
	\author{Прізвище автора 2/Name of Author 2}%2
	\affiliation{Department of Mathematics and Computer science, Universiteit Antwerpen}%інститут 2
	\address{Middelheimlaan 1, Antwerpen 2020, Belgium}%адреса 2

	\udk{№ УДК/UDC} \razd{\secix}

	\autorcol{N.N.\hspace*{0.7mm}Author1, N.N.\hspace*{0.7mm}Author2, N.N.\hspace*{0.7mm}Author3 et al.}%

	\setcounter{page}{1}%

	\begin{abstract}
		Аннотація/Abstract
	\end{abstract}

	\keywords{Ключові слова/Keywords.}

	\maketitle

	\section{Вступ/Introduction}

	Текст роботи/Paper text...

	\section{Розділ/Section}

	Для всіх формул вирівнювання ліворуч./All formulas should be shifted to the left.

	Для формул з номером:/For numbered formulas:
	\begin{equation}
	\end{equation}
	Для формул без номерів:/For unnumbered formulas:
	\[
	\]

	Для рисунків:/For figures:%

	%Fig.~1
	\begin{figure}% figure* for wide figure, [h] [!] to change the placement
		\vskip1mm
		%\includegraphics[width=\column]{1_e}
		\vskip-3mm\caption{  }
	\end{figure}

	Для таблиць:/For tables:% Таблиця 5х4

	\begin{table}[b]
		\noindent\caption{Назва таблиці/Table title}\vskip3mm\tabcolsep4.5pt

		\noindent{\footnotesize
			\begin{tabular}{|c|c|c|c|c}
				\hline%
				\multicolumn{1}{|c}{\rule{0pt}{5mm}Назва 1-ї колонки/Title of 1st column}%
				& \multicolumn{1}{|c}{Назва 2-ї колонки/Title of 2nd column}
				& \multicolumn{1}{|c}{Назва 3-ї колонки/Title of 3d column}
				& \multicolumn{1}{|c}{Назва 4-ї колонки/Title of 4th column}
				& \multicolumn{1}{|c|}{Назва 5-ї колонки/Title of 5th column}\\[2mm]%
				\hline%
				\rule{0pt}{5mm}&&&&\\ % Приклад/Example: 1&2&3&4&5\\
				&&&&\\%
				&&&&\\[2mm]%
				\hline
			\end{tabular}
		}
	\end{table}

	\section{Висновки/Conclusions}

	\vskip3mm \textit{Подяка/Acknowledgement.}

	\begin{thebibliography}{99}

		\bibitem{RoSmo} C.~Rovelli, L.~Smolin. Spin networks and quantum
		gravity. \textit{Phys. Phys. D}  {\bf 52}, 5743 (1995). [DOI: https://doi.org].%1

		\bibitem{Sho90} B.W.~Shore. \textit{The Theory of Coherent Atomic Excitation}
		(Wiley,  1990) [ISBN: 978-0471524175].%2

		\bibitem{3}
		\bibitem{4}

		\begin{flushright}
			{\footnotesize Received 26.01.18}
		\end{flushright}
	\end{thebibliography}

	Якщо стаття англ. мовою/For papers in English:

	\vspace*{-5mm}\rezume{%Резюме укр. мовою
		А.А. Автор1, А.А. Автор2, А.А. Автор3 та ін.}{НАЗВА СТАТТІ УКР.
		МОВОЮ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
			с\,л\,о\,в\,а:} ключові слова.}

	Якщо стаття укр. мовою/For papers in Ukrainian:

	\rezumang{%Резюме англ. мовою
		N.N. Author1, N.N. Author2, N.N. Author3 et al.}{PAPER TITLE IN
		ENGLISH}{Annotation text.}{\textit{Keywords:} keywords.}

\end{document}

### 2024-09-09 main_morse_response_functions.tex
implement UJP version

@@
 
-\author{O.A.Dobush, M.P.Kozlovskii, R.V.~Romanik
+\author{O.A.~Dobush, M.P.~Kozlovskii, R.V.~Romanik
 	\\ \small Institute for Condensed Matter Physics, NAS of Ukraine 
@@
 
+	\abstract{Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
+These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble.
+The calculated quantities are presented graphically as functions of density and chemical potential.
+		\\	
+		\textbf{Keywords:} Simple fluids, Morse potential, Thermodynamic response functions.
+	}
+
 	\input{./paper_text.tex}

### 2024-09-09 paper_text.tex
implement UJP version

@@
-\abstract{Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
-These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble.
-The calculated quantities are presented graphically as functions of density and chemical potential.
-	\\	
-	\textbf{Keywords:} Simple fluids, Morse potential, Thermodynamic response functions.
-}
 \section{Introduction}
@@
 \begin{figure}[h!]
-	%\centering 
+	\centering 
 	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
@@
 
-\begin{figure}[h!]
-	\centering \includegraphics[width=0.5\textwidth]{f2a.pdf}
-	\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
-	}\label{fig2a}
+\begin{figure}[htbp]
+	%\centering 
+	\includegraphics[width=0.5\textwidth]{f2a.pdf}
+	%\includegraphics[width=\column]{f2a}
+	%\vskip-3mm
+	\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
+	}
+	\label{fig2a}
 \end{figure}

### 2024-09-09 paper_text.tex
add footnotes to compare formulas; replace <N> with N; improve appendix

@@
 	\label{def:isotherm_compres}
-	K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}.
+	K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T, N}.
 \end{equation}
@@
 \begin{eqnarray*}
-	K_T & = & - \frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,\langle N\rangle}
+	K_T & = & - \frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,N}
 	\\
-	& = & -\rho \left(\frac{\partial \left(\frac{1}{\rho}\right)}{\partial P}\right)_{T,\langle N\rangle}
-	\\
-	& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,\langle N\rangle}
+	& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,N}
 	\\
@@
 \end{equation}
-which is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
-(NB. Compare this equation with Eq.(17) from~\cite{StrokerMeier2021})
+which\footnote{Compare this equation for $\beta_V$ with Eq.(17) from~\cite{StrokerMeier2021}} is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.
 
@@
 \begin{equation}
-	\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,\langle N\rangle}.
+	\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,N}.
 \end{equation}
@@
 \begin{equation}
+	\label{eq:alphaP1}
 	\alpha_P = -\frac{1}{\rho}\left(\frac{\partial \rho}{\partial T}\right)_{\mu}
@@
 \end{equation}
-which is readily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.\\
-(NB. Compare this equation with Eqs.(57)-(58) from~\cite{StrokerMeier2021})
+which\footnote{Compare this equation for $\alpha_P$ with Eqs.(57)-(58) from~\cite{StrokerMeier2021}} is readily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.
 
@@
 \begin{equation}
-	\alpha^*_P = \frac{1}{T^*_c}
-	\left( 
-	-\frac{1}{\bar{n}}\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
-	+ \frac{1}{\bar{n}} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
+	\alpha^*_P = \frac{1}{T^*_c \bar{n}}
+	\left[ 
+	-\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
+	+ \left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
 	\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
 	\left(\frac{\partial P^*}{\partial \mu}\right)^{-1}_{T} 
-	\right).
+	\right].
 \end{equation}
@@
 \section{\label{sec:app-a} Explicit expressions for derivatives}
-In this appendix, explicit expressions are presented for derivatives of quantities entering the equation of state, with respect to temperature.
-This expressions are useful while calculating the response functions in Section~\ref{sec:respons_functions}.
+In this Appendix, we provide an explicit example of differentiating the equation of state, namely~\eqref{eq:eosPTn_reduced}, by deriving the expression for the thermal pressure coefficient $\beta^*_V$ from~\eqref{eq:beta_star_n}.
 

### 2024-09-10 paper_text.tex
improve text; adjusted equations

@@
 
-As the problem was considered in the framework of the grand canonical ensemble, the initial equation of state is formulated in terms of pressure $P$, temperature $T$ and the chemical potential $\mu$, $P = P(T,\mu)$.
+As the problem has been considered in the framework of the grand canonical ensemble, the initial equation of state is formulated in terms of pressure $P$, temperature $T$ and the chemical potential $\mu$, $P = P(T,\mu)$.
 To leverage this form of the equation of state for calculation of the response functions, the corresponding definitions should be transformed to proper derivatives with respect to temperature and chemical potential~\cite{StrokerMeier2021}.
@@
 The potential of interaction between particles is taken in a form of a modified Morse potential
-\begin{equation}
+\begin{eqnarray}
 	\label{def:mod_morse}
-	U(r) = \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
-\end{equation}
+	U(r) & = & \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} \right.
+	\nonumber\\
+	&& + \left. {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
+\end{eqnarray}
 where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model.
-Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
+Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as follows
 \begin{equation}
@@
 
-Modifications of the Morse potential were used in other works as well.
+Modifications of the Morse potential have been used in other works as well.
 For example, in~\cite{MartinezValenciaEtAl2013} a repulsive term in a form of a power of $r^{-1}$ was added to the ordinary Morse potential, and the influence of the softness of such a term was investigated on the coordinates of the critical point.
@@
 
-Our modification contains an additional repulsive term, similar to~\cite{MartinezValenciaEtAl2013}, as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential.
-Including the repulsive term enables us to single out a reference system and apply the method of collective variables to calculating the grand partition function~[REFERENCE NEEDED].
+Our modification contains an additional repulsive term, similarly to~\cite{MartinezValenciaEtAl2013}, as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential.
+Including the repulsive term enables us to single out a reference system (in the reciprocal space) and apply the method of collective variables to calculating the grand partition function~[REFERENCE NEEDED].
 
@@
 \begin{align}
-	& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
-	& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, \nonumber\\
+	& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  
+	\nonumber \\
+	& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, 
+	\nonumber\\
+	& g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, 
+	\nonumber\\
 	& a_4 = -g_4,
@@
 \end{equation*}
-We also use the reduced temperature defined as $T = k_{\rm B}T/\varepsilon$, and its critical value $T^*_c = 4.995.$
+We also use the reduced temperature defined as $T = k_{\rm B}T/\varepsilon$, and thus its critical value $T^*_c = 4.995.$
 
@@
 \begin{eqnarray}\label{eq:E_mu}
-	E_\mu (M, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 - \frac{\beta W(0)}{2} 
+	E_\mu (M, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  
+	\nonumber\\
+	&& +  g_0 - \frac{\beta W(0)}{2} 
 	\left(\frac{\tilde\mu}{W(0)} \right)^{2} 
@@
 Considering the equation of state~\eqref{eq:eosMT}, $P^*$ is explicitly written as
-\begin{equation}
+\begin{eqnarray}
 	\label{eq:eosPTM_reduced}
-	P^* = (1 + \tau)T^*_c \left( E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4 \right).
-\end{equation}
+	P^* & = & (1 + \tau)T^*_c \bigg[ E_\mu(M, T) 
+	\nonumber\\
+	&& + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4
+	\bigg].
+\end{eqnarray}
 This equation can be easily represented graphically.
-Figure~\ref{fig1} illustrates the relationship between the reduced pressure $P^*$ and the effective chemical potential $M$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
+Figure~\ref{fig1} illustrates the relationship between the reduced pressure $P^*$ and the effective chemical potential $M$ for various values of the relative temperature $\tau$, at and above the critical temperature.
 At the critical point $M=0, \tau=0$, $P^*_c = 1.606$.
@@
 In this work, by density we mean the particle number density $\rho = \langle N \rangle / V$.
-In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is a partial derivative of natural logarithm of the grand partition function $\Xi$ with respect to $\beta \mu$
+In the framework of the grand canonical ensemble the average number of particles $\left\langle N \right\rangle$ is found by 
 \begin{eqnarray*}
 	\langle N \rangle & = & \left(\frac{\partial \ln\Xi}{\partial \beta \mu}\right)_{T,V} 
-	\\
-	& = & \left(\frac{\partial (PV)}{\partial \mu}\right)_{T,V}
 	\\
@@
 \begin{equation}
-	\bar{n} \equiv \frac{\langle N \rangle}{V} v = \frac{\langle N \rangle}{N_v} = v \left(\frac{\partial P}{\partial \mu}\right)_{T,V} 
+	\bar{n} \equiv \frac{\langle N \rangle}{V} v = v \left(\frac{\partial P}{\partial \mu}\right)_{T,V} 
 	= \left(\frac{\partial (Pv\beta)}{\partial (\beta \mu)}\right)_{T,V}.
 \end{equation}
-The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density. In the context of the cell model, on the other hand, it is the average number of particles per cell.
+The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density, and is usually denoted by $\rho^*$ in the literature on simple fluids~\cite{HansenMcDonald2013}.
+In the context of the cell model, on the other hand, it is the average number of particles per cell.
 Taking explicit derivatives, we arrive at
@@
 \end{equation}
-The quantity $n_g$ in the equation \eqref{eq:density} is the critical density
+The quantity $n_g$ in the equation \eqref{eq:density} is the critical density~\cite{KozlovskiiDobush2020}
 \begin{eqnarray}\label{eq:crit_dens}
@@
 \end{align}
+The notation $\bar{M}$ represents the effective chemical potential as a function of temperature and density $\bar{n}$, while $M$ represents the effective chemical potential as a function of temperature and chemical potential~$\mu$.
 
@@
 \begin{equation}\label{eq:eosNT}
-	Pv\beta = E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4,
+	Pv\beta = E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4.
 \end{equation}
@@
 For the reduced pressure we write
-\begin{equation}
+\begin{eqnarray}
 	\label{eq:eosPTn_reduced}
-	P^* = (1 + \tau)T^*_c \left(E_\eta (\bar{n},T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\right).
-\end{equation}
+	P^* & = & (1 + \tau)T^*_c \bigg[ E_\eta (\bar{n},T) 
+	\nonumber\\
+	&& + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\bigg].
+\end{eqnarray}
 
-Figure~1 shows the isotherms for the pressure $P^*$ versus density $\bar{n}$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
+Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\bar{n}$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
 \begin{figure}[h!]
@@
 The second one expresses the pressure as a function of temperature and density, $P = P(T, \bar{n})$, and is represented by equivalent Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
-These equations, together with the explicit dependency of density on temperature and chemical potential, $\bar{n} = \bar{n}(T, \mu)$, see Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}
+These equations, together with the explicit dependency of density on temperature and chemical potential, $\bar{n} = \bar{n}(T, \mu)$, Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}.
 
@@
 \end{equation}
-Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
+Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}:
 \begin{eqnarray*}
-	K_T & = & - \frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,N}
-	\\
-	& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,N}
+	K_T	& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,N}
 	\\
 	& = & \frac{1}{\rho} \frac{\left(\partial \rho / \partial \mu\right)_{T}}
-	{\left(\partial P / \partial \mu\right)_{T}},
+	{\left(\partial P / \partial \mu\right)_{T}}.
 \end{eqnarray*}
-where $\rho = \langle N \rangle / V$ is the particle number density.
-We have omitted the condition of constant $\langle N \rangle$ in the last line of the above equation since we have explicit dependencies on temperature and chemical potential for both pressure $P = P(T, \mu)$, see Eq.~\eqref{eq:eosMT}, and density $\rho = \rho(T, \mu)$, see Eq.~\eqref{eq:density}.
+We have omitted the condition of constant $N$ in the last line of the above equation since we have explicit dependencies on temperature and chemical potential for both pressure $P = P(T, \mu)$, Eq.~\eqref{eq:eosMT}, and density $\rho = \rho(T, \mu)$, Eq.~\eqref{eq:density}.
 Applying the Gibbs--Duhem equation
@@
 	\label{def:therm_pres_coef}
-	\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,\langle N \rangle}.
+	\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,N}.
 \end{equation}
@@
 \begin{eqnarray}
-	\beta_V & = & \left(\frac{\partial P}{\partial T}\right)_{V, N}
-	\nonumber\\
-	& = & \left(\frac{\partial P}{\partial T}\right)_{\mu} + \left(\frac{\partial P}{\partial \mu}\right)_T \left(\frac{\partial \mu}{\partial T}\right)_{V, N}.
+	\beta_V	& = & \left(\frac{\partial P}{\partial T}\right)_{\mu} + \left(\frac{\partial P}{\partial \mu}\right)_T \left(\frac{\partial \mu}{\partial T}\right)_{V, N}.
 \end{eqnarray}
@@
 	\label{eq:beta_star_n}
-	\beta^*_V = \frac{1}{T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}
+	\beta^*_V = \frac{1}{T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho}.
 \end{equation}
@@
 \begin{eqnarray}
-	\alpha_P & = & \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P, N}
-	\nonumber\\
 	\label{eq:alpha_vs_rho}
-	& = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{P, N}
+	\alpha_P & = & -\frac{1}{\rho} \left(\frac{\partial \rho}{\partial T}\right)_{P, N}
 	\\
@@
 It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
-\begin{equation}
-	\alpha^*_P = \frac{1}{T^*_c \bar{n}}
+\begin{eqnarray}
+	\alpha^*_P & = & \frac{1}{T^*_c \bar{n}}
 	\left[ 
 	-\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
-	+ \left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
+	\right. \nonumber\\
+	&& + \left.\left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
 	\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
@@
 	\right].
-\end{equation}
+\end{eqnarray}
 
@@
 Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\bar{n}$ for various values of temperature above the critical one.
-The dependency of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Figure~\ref{fig4b}.
+The dependency of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig4b}.
 
@@
 \begin{equation}
+	\label{eq:identity}
 	\frac{\alpha_P}{K_T \beta_V} = \frac{\alpha^*_P}{K^*_T \beta^*_V} = 1,
@@
 Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
+The starting point for these calculations are the equation of state obtained for a cell fluid model within the framework of the grand canonical ensemble in our previous work~\cite{KozlovskiiDobush2020}.
+The dependencies of the calculated response functions on the density and the effective chemical potential are illustrated graphically.
+The thermodynamic identity~\eqref{eq:identity} among these quantities is verified to confirm the self-consistency of the performed calculations.
 

### 2024-09-10 paper_text.tex
add reference to JML 2016; mention entropy as contribution to beta_v

@@
 Our modification contains an additional repulsive term, similarly to~\cite{MartinezValenciaEtAl2013}, as well as introduces parameter $\gamma$, which can vary as opposed to being strictly equal to 2 in the Morse potential.
-Including the repulsive term enables us to single out a reference system (in the reciprocal space) and apply the method of collective variables to calculating the grand partition function~[REFERENCE NEEDED].
+Including the repulsive term enables us to single out a reference system (in the reciprocal space) and apply the method of collective variables to calculating the grand partition function~\cite{KozlovskiiDobush2016}.
 
@@
 which\footnote{Compare this equation for $\beta_V$ with Eq.(17) from~\cite{StrokerMeier2021}} is easily calculated based on Eqs.~\eqref{eq:eosMT} and~\eqref{eq:density}.
+It is also worth noting that the first contribution to $\beta_V$ is essentially the entropy per volume, $S/V = (\partial P / \partial T)_\mu$.
 

### 2024-09-10 paper_text.tex

@@
 	&	M = \frac{\tilde\mu}{W(0)} + g_1 - \frac{g_3}{g_4} \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
-	&	\tilde\mu=\mu-\mu^*(1+\tau),
+	&	\tilde\mu=\mu-\mu_0(1+\tau),
 \end{align}
-where $\mu^*$ is some positive constant, $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$, $T_c$ is the critical temperature. We will call $M$ the effective chemical potential.
+where $\mu_0$ is some positive constant, $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$, $T_c$ is the critical temperature. We will call $M$ the effective chemical potential.
 
@@
 \end{equation}
-Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
+Here $\alpha^*=v e^{\beta_c\mu_0}$, and the parameter $p$ has the form
 \begin{equation}
@@
 \begin{equation}
-	\bar{n} \equiv \frac{\langle N \rangle}{V} v = v \left(\frac{\partial P}{\partial \mu}\right)_{T,V} 
+	\rho^* \equiv \frac{\langle N \rangle}{V} v = v \left(\frac{\partial P}{\partial \mu}\right)_{T,V} 
 	= \left(\frac{\partial (Pv\beta)}{\partial (\beta \mu)}\right)_{T,V}.
 \end{equation}
-The quantity $\bar{n}$, on the one hand, has the meaning of the reduced particle number density, and is usually denoted by $\rho^*$ in the literature on simple fluids~\cite{HansenMcDonald2013}.
-In the context of the cell model, on the other hand, it is the average number of particles per cell.
+The quantity $\rho^*$, on the one hand, is the reduced particle number density, which is the notation commonly used in the literature on simple fluids~\cite{HansenMcDonald2013}.
+In the context of the cell model, on the other hand, it is the average number of particles per cell.\footnote{In our previous works we denoted the reduced number density by $\bar{n}$.
+In the current work we switch to more common notation $\rho^*$.}
 Taking explicit derivatives, we arrive at
 \begin{equation}\label{eq:density}
-	\bar n = n_g - M + \frac{ \bar \rho_0}{\beta W(0)}.
+	\rho^* = n_g - M + \frac{ \bar \rho_0}{\beta W(0)}.
 \end{equation}
@@
 Equations~\eqref{eq:density} and~\eqref{eq:eosMT} jointly define a parametric relationship between pressure and density, with $M$ serving as the parameter.
-Figure~\ref{fig1} shows the dependency of the reduced pressure $P^*$ on the density $\bar{n}$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
+Figure~\ref{fig1} shows the dependency of the reduced pressure $P^*$ on the density $\rho^*$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
 
@@
 \begin{equation}\label{eq:M_nT}
-	\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g),
+	\bar M = \frac{\rho_{n}}{\beta W(0)} - (\rho^* - n_g),
 \end{equation}
@@
 	& \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
-	& \alpha_n = \arccos \left( \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber 
+	& \alpha_n = \arccos \left( \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \rho^*)\right). \nonumber 
 \end{align}
-The notation $\bar{M}$ represents the effective chemical potential as a function of temperature and density $\bar{n}$, while $M$ represents the effective chemical potential as a function of temperature and chemical potential~$\mu$.
+The notation $\bar{M}$ represents the effective chemical potential as a function of temperature and density $\rho^*$, while $M$ represents the effective chemical potential as a function of temperature and chemical potential~$\mu$.
 
@@
 \begin{equation}\label{eq:eosNT}
-	Pv\beta = E_\eta (\bar n,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4.
+	Pv\beta = E_\eta (\rho^*,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4.
 \end{equation}
-The quantity $E_\nu (\bar n, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}
+The quantity $E_\nu (\rho^*, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}
 \begin{eqnarray}\label{eq:E_nu}
-	E_\nu (\bar{n}, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 
+	E_\nu (\rho^*, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 
 	\nonumber\\
@@
 	\label{eq:eosPTn_reduced}
-	P^* & = & (1 + \tau)T^*_c \bigg[ E_\eta (\bar{n},T) 
+	P^* & = & (1 + \tau)T^*_c \bigg[ E_\eta (\rho^*,T) 
 	\nonumber\\
@@
 
-Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\bar{n}$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
+Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\rho^*$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
 \begin{figure}[h!]
@@
 	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
-	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function of the density $\bar n$ (on the left-hand side) and a function of the effective chemical potential $M$ (on the right-hand side) at $T \geq T_c$ represented by black lines.
+	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function of the density $\rho^*$ (on the left-hand side) and a function of the effective chemical potential $M$ (on the right-hand side) at $T \geq T_c$ represented by black lines.
 Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
@@
 The first one expresses the pressure as a function of temperature and chemical potential, $P = P(T, \mu)$, and is represented by equivalent Eqs.~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}.
-The second one expresses the pressure as a function of temperature and density, $P = P(T, \bar{n})$, and is represented by equivalent Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
-These equations, together with the explicit dependency of density on temperature and chemical potential, $\bar{n} = \bar{n}(T, \mu)$, Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}.
+The second one expresses the pressure as a function of temperature and density, $P = P(T, \rho^*)$, and is represented by equivalent Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
+These equations, together with the explicit dependency of density on temperature and chemical potential, $\rho^* = \rho^*(T, \mu)$, Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}.
 
@@
 The quantity $K^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent.
-It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
+It is expressed in terms of the reduced quantities $P^*$ and $\rho^*$ as follows
 \begin{eqnarray}
-	K^*_T & = & \frac{\varepsilon}{\bar{n}^2} \left(\frac{\partial \bar{n}}{\partial \mu}\right)_T
+	K^*_T & = & \frac{\varepsilon}{{\rho^*}^2} \left(\frac{\partial \rho^*}{\partial \mu}\right)_T
 	\nonumber\\
-	& = & \frac{\varepsilon^2}{\bar{n}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
+	& = & \frac{\varepsilon^2}{{\rho^*}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
 \end{eqnarray}
@@
 
-If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the isothermal compressibility are
+If it is preferable to use the equation of state in the form $P=P(T, \rho^*)$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the isothermal compressibility are
 \begin{equation}
-	K_T = \frac{1}{\bar{n}} \left(\frac{\partial P}{\partial \bar{n}}\right)^{-1}_T
+	K_T = \frac{1}{\rho^*} \left(\frac{\partial P}{\partial \rho^*}\right)^{-1}_T
 \end{equation}
@@
 \begin{equation}
-	K^*_T = \frac{1}{\bar{n}} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
+	K^*_T = \frac{1}{\rho^*} \left(\frac{\partial P^*}{\partial \rho^*}\right)^{-1}_T.
 \end{equation}
 
-Figure~\ref{fig2a} illustrates the dependency of the compressibility $K^*_T$ on the density $\bar{n}$ for various values of temperature above the critical one.
+Figure~\ref{fig2a} illustrates the dependency of the compressibility $K^*_T$ on the density $\rho^*$ for various values of temperature above the critical one.
 The dependency of $K^*_T$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig2b}.
@@
 	%\vskip-3mm
-	\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
+	\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
 	}
@@
 	\left(\frac{\partial V}{\partial \mu}\right)^{-1}_{T, N} \\
-	& = & - \left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
-	\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}.		
+	& = & - \left(\frac{\partial \rho^*}{\partial T}\right)_{\mu}
+	\left(\frac{\partial \rho^*}{\partial \mu}\right)^{-1}_{T}.		
 \end{eqnarray*}
@@
 	- \left(\frac{\partial P}{\partial \mu}\right)_T 
-	\left(\frac{\partial \bar{n}}{\partial T}\right)_{\mu}
-	\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T}
+	\left(\frac{\partial \rho^*}{\partial T}\right)_{\mu}
+	\left(\frac{\partial \rho^*}{\partial \mu}\right)^{-1}_{T}
 \end{equation}
@@
 \end{equation}
-It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
+It is expressed in terms of reduced quantities as follows
 \begin{equation}
@@
 	- \left(\frac{\partial P^*}{\partial \mu}\right)_T 
-	\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
-	\left(\frac{\partial \bar{n}}{\partial \mu}\right)^{-1}_{T} 
+	\left(\frac{\partial \rho^*}{\partial \tau}\right)_{\mu}
+	\left(\frac{\partial \rho^*}{\partial \mu}\right)^{-1}_{T} 
 	\right].
@@
 
-If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the thermal pressure coefficient follow immediately from the definition~\eqref{def:therm_pres_coef}
+If it is preferable to use the equation of state in the form $P=P(T, \rho^*)$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then the most suitable expressions for the thermal pressure coefficient follow immediately from the definition~\eqref{def:therm_pres_coef}
 \begin{equation}
@@
 	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
 	}\label{fig3a}
@@
 	\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\eta$. 
+	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
 	}\label{fig3c}
@@
 
-Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\bar{n}$ for various values of temperature above the critical one.
+Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\rho^*$ for various values of temperature above the critical one.
 The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig3b}.
@@
 \end{equation}
-It is expressed in terms of the reduced quantities $P^*$ and $\bar{n}$ as follows
+It is expressed in terms of reduced quantities as follows
 \begin{eqnarray}
-	\alpha^*_P & = & \frac{1}{T^*_c \bar{n}}
+	\alpha^*_P & = & \frac{1}{T^*_c \rho^*}
 	\left[ 
-	-\left(\frac{\partial \bar{n}}{\partial \tau}\right)_{\mu}
+	-\left(\frac{\partial \rho^*}{\partial \tau}\right)_{\mu}
 	\right. \nonumber\\
-	&& + \left.\left(\frac{\partial \bar{n}}{\partial \mu}\right)_{T}
+	&& + \left.\left(\frac{\partial \rho^*}{\partial \mu}\right)_{T}
 	\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
@@
 
-If it is preferable to use the equation of state in the form $P=P(T, \bar{n})$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then we need to rewrite the definition for $\alpha_P$ accordingly.
+If it is preferable to use the equation of state in the form $P=P(T, \rho^*)$, see~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}, then we need to rewrite the definition for $\alpha_P$ accordingly.
 We start with~\eqref{eq:alpha_vs_rho} and apply the cyclic relation
@@
 \begin{equation}
-	\alpha^*_P = \frac{1}{\bar{n} T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho} \left(\frac{\partial P^*}{\partial \bar{n}}\right)^{-1}_T.
+	\alpha^*_P = \frac{1}{\rho^* T^*_c} \left(\frac{\partial P^*}{\partial \tau}\right)_{\rho} \left(\frac{\partial P^*}{\partial \rho^*}\right)^{-1}_T.
 \end{equation}
 
-Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\bar{n}$ for various values of temperature above the critical one.
+Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\rho^*$ for various values of temperature above the critical one.
 The dependency of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig4b}.
@@
 	\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
-	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
 	}\label{fig4a}
@@
 \begin{equation}
-	\left( \frac{\partial \bar{M}}{\partial \tau} \right)_{\bar{n}} =
+	\left( \frac{\partial \bar{M}}{\partial \tau} \right)_{\rho^*} =
 	\frac{k_{\rm B}T_c \rho_n}{W(0)} \frac{1 - \omega_0}{1 + \tau\omega_0},
@@
 \begin{eqnarray}
-	\beta^*_V & = & E_\eta (\bar{n},T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
+	\beta^*_V & = & E_\eta (\rho^*,T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
 	\nonumber\\

### 2024-09-10 dobush_et_al_ujp_UTF8.tex

@@
 
+\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
+\usepackage{amssymb}
+\usepackage{physics}
+%\usepackage{cite} % may be useful for different formats of numerical citation
+\usepackage{hyperref} % for hyperlinks in references
+\usepackage[nameinlink]{cleveref}
+\usepackage{caption} % for \caption*
+\usepackage{amsmath}    % for "\eqref" macro
+\usepackage{graphicx}
+
 \begin{document}
-	\title[Колонтитул: Назва роботи (3-5 слів)/Headline: paper title (3-5 words)]%колонтитул
-	{НАЗВА РОБОТИ/PAPER TITLE}%
-	\author{Прізвище автора 1/Name of Author 1}%1
-	\affiliation{Bogolyubov Institute for Theoretical Physics, Nat. Acad. of Sci. of Ukraine}%інститут 1
-	\address{14b, Metrolohichna Str., Kyiv 03143, Ukraine}%адреса 1
-	\email{ujp@bitp.kiev.ua}%e-mail 1
-	\author{Прізвище автора 2/Name of Author 2}%2
-	\affiliation{Department of Mathematics and Computer science, Universiteit Antwerpen}%інститут 2
-	\address{Middelheimlaan 1, Antwerpen 2020, Belgium}%адреса 2
+	\title[Thermodynamic response functions in a cell fluid model]%колонтитул
+	{THERMODYNAMIC RESPONSE FUNCTIONS IN A CELL FLUID MODEL}%
+	\author{O.A.~Dobush}%1
+	\author{M.P.~Kozlovskii}
+	\author{R.V.~Romanik}
+	\author{I.V.~Pylyuk}
+	\affiliation{Institute for Condensed Matter Physics,\\ Nat. Acad. of Sci. of Ukraine}%інститут 1
+	\address{1, Svientsitskii Str., Lviv 79011, Ukraine}%адреса 1
+	\email{dobush@icmp.lviv.ua}%e-mail 1
+	\email{mpk@icmp.lviv.ua}
+	\email{romanik@icmp.lviv.ua}
+	\email{piv@icmp.lviv.ua}
 
-	\udk{№ УДК/UDC} \razd{\secix}
+	\udk{№ УДК/UDC} \razd{\secv}
 
-	\autorcol{N.N.\hspace*{0.7mm}Author1, N.N.\hspace*{0.7mm}Author2, N.N.\hspace*{0.7mm}Author3 et al.}%
+	\autorcol{O.A.\hspace*{0.7mm}Dobush, M.P.\hspace*{0.7mm}Kozlovskii, R.V.\hspace*{0.7mm}Romanik, I.V.\hspace*{0.7mm}Pylyuk}%
 
@@
 	\begin{abstract}
-		Аннотація/Abstract
+		Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
+These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble.
+The calculated quantities are presented graphically as functions of density and chemical potential.
 	\end{abstract}
 
-	\keywords{Ключові слова/Keywords.}
+	\keywords{Cell model, Morse potential, Thermodynamic response functions}
 
@@
 
-	\section{Вступ/Introduction}
+	\input{./paper_text.tex}
 
-	Текст роботи/Paper text...
+	\vskip3mm \textit{Acknowledgement.}
 
-	\section{Розділ/Section}
-
-	Для всіх формул вирівнювання ліворуч./All formulas should be shifted to the left.
-
-	Для формул з номером:/For numbered formulas:
-	\begin{equation}
-	\end{equation}
-	Для формул без номерів:/For unnumbered formulas:
-	\[
-	\]
-
-	Для рисунків:/For figures:%
-
-	%Fig.~1
-	\begin{figure}% figure* for wide figure, [h] [!] to change the placement
-		\vskip1mm
-		%\includegraphics[width=\column]{1_e}
-		\vskip-3mm\caption{  }
-	\end{figure}
-
-	Для таблиць:/For tables:% Таблиця 5х4
-
-	\begin{table}[b]
-		\noindent\caption{Назва таблиці/Table title}\vskip3mm\tabcolsep4.5pt
-
-		\noindent{\footnotesize
-			\begin{tabular}{|c|c|c|c|c}
-				\hline%
-				\multicolumn{1}{|c}{\rule{0pt}{5mm}Назва 1-ї колонки/Title of 1st column}%
-				& \multicolumn{1}{|c}{Назва 2-ї колонки/Title of 2nd column}
-				& \multicolumn{1}{|c}{Назва 3-ї колонки/Title of 3d column}
-				& \multicolumn{1}{|c}{Назва 4-ї колонки/Title of 4th column}
-				& \multicolumn{1}{|c|}{Назва 5-ї колонки/Title of 5th column}\\[2mm]%
-				\hline%
-				\rule{0pt}{5mm}&&&&\\ % Приклад/Example: 1&2&3&4&5\\
-				&&&&\\%
-				&&&&\\[2mm]%
-				\hline
-			\end{tabular}
-		}
-	\end{table}
-
-	\section{Висновки/Conclusions}
-
-	\vskip3mm \textit{Подяка/Acknowledgement.}
-
-	\begin{thebibliography}{99}
-
-		\bibitem{RoSmo} C.~Rovelli, L.~Smolin. Spin networks and quantum
-		gravity. \textit{Phys. Phys. D}  {\bf 52}, 5743 (1995). [DOI: https://doi.org].%1
-
-		\bibitem{Sho90} B.W.~Shore. \textit{The Theory of Coherent Atomic Excitation}
-		(Wiley,  1990) [ISBN: 978-0471524175].%2
-
-		\bibitem{3}
-		\bibitem{4}
-
-		\begin{flushright}
-			{\footnotesize Received 26.01.18}
-		\end{flushright}
-	\end{thebibliography}
-
-	Якщо стаття англ. мовою/For papers in English:
+	\bibliography{extracted}
 
 	\vspace*{-5mm}\rezume{%Резюме укр. мовою
-		А.А. Автор1, А.А. Автор2, А.А. Автор3 та ін.}{НАЗВА СТАТТІ УКР.
-		МОВОЮ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
-			с\,л\,о\,в\,а:} ключові слова.}
-
-	Якщо стаття укр. мовою/For papers in Ukrainian:
-
-	\rezumang{%Резюме англ. мовою
-		N.N. Author1, N.N. Author2, N.N. Author3 et al.}{PAPER TITLE IN
-		ENGLISH}{Annotation text.}{\textit{Keywords:} keywords.}
+		О.А.~Добуш, М.П.~Козловський, Р.В.~Романік, І.В.~Пилюк}{ТЕРМОДИНАМІЧНІ ФУНКЦІЇ ВІДГУКУ КОМІРКОВОЇ МОДЕЛІ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
+			с\,л\,о\,в\,а:} коміркова модель, потенціал Морзе, термодинамічні функції відгуку.}
 

### 2024-09-10 paper_text.tex
change notation for isothermal compressibility from K_T to \kappa_T

@@
 	\label{def:isotherm_compres}
-	K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T, N}.
+	\kappa_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T, N}.
 \end{equation}
-Let us perform some transformations to rewrite $K_T$ into a form that is more suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}:
+Let us perform some transformations to rewrite $\kappa_T$ into a form that is more suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}:
 \begin{eqnarray*}
-	K_T	& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,N}
+	\kappa_T	& = & \frac{1}{\rho} \left(\frac{\partial \rho}{\partial P} \right)_{T,N}
 	\\
@@
 \end{equation}
-Substituting this into the last expression for $K_T$, one gets
+Substituting this into the last expression for $\kappa_T$, one gets
 \begin{equation}
-	K_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
+	\kappa_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
 \end{equation}
@@
 \begin{equation}
-	K_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T}
+	\kappa_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T}
 \end{equation}
@@
 \begin{equation}
-	K^*_T \equiv \frac{\varepsilon K_T}{v}.
+	\kappa^*_T \equiv \frac{\varepsilon K_T}{v}.
 \end{equation}
-The quantity $K^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent.
+The quantity $\kappa^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent.
 It is expressed in terms of the reduced quantities $P^*$ and $\rho^*$ as follows
 \begin{eqnarray}
-	K^*_T & = & \frac{\varepsilon}{{\rho^*}^2} \left(\frac{\partial \rho^*}{\partial \mu}\right)_T
+	\kappa^*_T & = & \frac{\varepsilon}{{\rho^*}^2} \left(\frac{\partial \rho^*}{\partial \mu}\right)_T
 	\nonumber\\
@@
 \end{eqnarray}
-Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $K^*_T$, with the result expressed as a function of temperature and chemical potential.
+Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $\kappa^*_T$, with the result expressed as a function of temperature and chemical potential.
 
@@
 \begin{equation}
-	K_T = \frac{1}{\rho^*} \left(\frac{\partial P}{\partial \rho^*}\right)^{-1}_T
+	\kappa_T = \frac{1}{\rho^*} \left(\frac{\partial P}{\partial \rho^*}\right)^{-1}_T
 \end{equation}
@@
 \begin{equation}
-	K^*_T = \frac{1}{\rho^*} \left(\frac{\partial P^*}{\partial \rho^*}\right)^{-1}_T.
+	\kappa^*_T = \frac{1}{\rho^*} \left(\frac{\partial P^*}{\partial \rho^*}\right)^{-1}_T.
 \end{equation}
 
-Figure~\ref{fig2a} illustrates the dependency of the compressibility $K^*_T$ on the density $\rho^*$ for various values of temperature above the critical one.
-The dependency of $K^*_T$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig2b}.
+Figure~\ref{fig2a} illustrates the dependency of the compressibility $\kappa^*_T$ on the density $\rho^*$ for various values of temperature above the critical one.
+The dependency of $\kappa^*_T$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig2b}.
 
@@
 	%\vskip-3mm
-	\caption{The reduced isothermal compressibility $K^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
+	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
 	}
@@
 	\includegraphics[width=0.475\textwidth]{f2c.pdf}
-	\vskip-3mm\caption{The reduced isothermal compressibility $K^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+	\vskip-3mm\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
 The two figures differ in the scale of $M$.
@@
 	\label{eq:identity}
-	\frac{\alpha_P}{K_T \beta_V} = \frac{\alpha^*_P}{K^*_T \beta^*_V} = 1,
+	\frac{\alpha_P}{\kappa_T \beta_V} = \frac{\alpha^*_P}{\kappa^*_T \beta^*_V} = 1,
 \end{equation}
 which is easily derived from the cyclic relation between $P$, $V$ and $T$.
-In our case, this equality is exactly reproduced by substituting explicit expressions for $K_T$, $\alpha_P$, and $\beta_V$ obtained from the equation of state~\eqref{eq:eosMT} (or~\eqref{eq:eosNT}).
+In our case, this equality is exactly reproduced by substituting explicit expressions for $\kappa_T$, $\alpha_P$, and $\beta_V$ obtained from the equation of state~\eqref{eq:eosMT} (or~\eqref{eq:eosNT}).
 

### 2024-09-10 paper_text.tex
update figures descriptions

@@
 \section{Introduction}
-
 In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}.
@@
 \begin{equation}\label{eq:density}
-	\rho^* = n_g - M + \frac{ \bar \rho_0}{\beta W(0)}.
+	\rho^* = \rho^*_c - M + \frac{ \bar \rho_0}{\beta W(0)}.
 \end{equation}
-The quantity $n_g$ in the equation \eqref{eq:density} is the critical density~\cite{KozlovskiiDobush2020}
+The quantity $\rho^*_c$ in the equation \eqref{eq:density} is the critical density~\cite{KozlovskiiDobush2020}
 \begin{eqnarray}\label{eq:crit_dens}
-	n_g & = & g_1 - \frac{g_3}{g_4}\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right) - \frac{1}{6} \frac{g_3^3}{g_4^2} 
+	\rho^*_c & = & g_1 - \frac{g_3}{g_4}\left(  g_2 - \frac{1}{2} \frac{g_3^2}{g_4}\right) - \frac{1}{6} \frac{g_3^3}{g_4^2} 
 	\nonumber\\
@@
 \begin{equation*}
-	n_g = 0.978.
+	\rho^*_c = 0.978.
 \end{equation*}
@@
 \begin{equation}\label{eq:M_nT}
-	\bar M = \frac{\rho_{n}}{\beta W(0)} - (\rho^* - n_g),
+	\bar M = \frac{\rho_{n}}{\beta W(0)} - (\rho^* - \rho^*_c),
 \end{equation}
@@
 	& \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
-	& \alpha_n = \arccos \left( \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \rho^*)\right). \nonumber 
+	& \alpha_n = \arccos \left[ \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (\rho^*_c - \rho^*)\right]. \nonumber 
 \end{align}
@@
 
-Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\rho^*$ (left-hand side) and versus the effective chemical potential $M$ (right-hand side).
+Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\rho^*$ (see Fig.~\ref{fig1}a), and versus the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
 \begin{figure}[h!]
@@
 	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
-	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function of the density $\rho^*$ (on the left-hand side) and a function of the effective chemical potential $M$ (on the right-hand side) at $T \geq T_c$ represented by black lines.
+	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines.
 Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
@@
 Figure~\ref{fig2a} illustrates the dependency of the compressibility $\kappa^*_T$ on the density $\rho^*$ for various values of temperature above the critical one.
-The dependency of $\kappa^*_T$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig2b}.
+The dependency of $\kappa^*_T$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig2b}.
 
@@
 The two figures differ in the scale of $M$.
-The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
+Part~(a) covers a wider range of $M$.
+Part~(b) focuses on a range of $M$ around its critical value $0$.
 	}\label{fig2b}
@@
 	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
+The temperature dependence is weak, resulting in multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
 	}\label{fig3a}
@@
 	\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
 	}\label{fig3b}
@@
 Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\rho^*$ for various values of temperature above the critical one.
-The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig~\ref{fig3b}.
+The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig3b}.
+The dependency of $\beta^*_V$ on the relative temperature $\tau$ is displayed in Fig.~\ref{fig3c} for a few values of density.
 
@@
 	\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
-	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
+	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
 	}\label{fig4a}
@@
 The two figures differ in the scale of $M$.
-The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
+Part (a) covers a wider range of $M$.
+Part (b) focuses on a range of $M$ around its critical value~$0$.
 	}\label{fig4b}

### 2024-09-11 paper_text.tex
adjusted figures according to ujp styleguide

@@
 \begin{figure}[h!]
-	\centering 
-	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
-	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
-	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines.
+	%\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
+	%\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
+	\includegraphics[width=\column]{f1a1.pdf} 
+	\includegraphics[width=\column]{f1b1.pdf}
+	\vskip-3mm
+	\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines.
 Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
-	}\label{fig1}
+	}
+	\label{fig1}
 \end{figure}
@@
 \begin{figure}[htbp]
-	%\centering 
-	\includegraphics[width=0.5\textwidth]{f2a.pdf}
-	%\includegraphics[width=\column]{f2a}
-	%\vskip-3mm
+	%\includegraphics[width=0.5\textwidth]{f2a.pdf}
+	\includegraphics[width=\column]{f2a}
+	\vskip-3mm
 	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
@@
 \begin{figure}[h!] 
-	\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
-	\includegraphics[width=0.475\textwidth]{f2c.pdf}
-	\vskip-3mm\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+	%\includegraphics[width=0.45\textwidth]{f2b.pdf}
+	%\includegraphics[width=0.475\textwidth]{f2c.pdf}
+	\includegraphics[width=\column]{f2b.pdf}
+	\includegraphics[width=\column]{f2c.pdf}
+	\vskip-3mm
+	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
 The two figures differ in the scale of $M$.
@@
 Part~(b) focuses on a range of $M$ around its critical value $0$.
-	}\label{fig2b}
+	}
+	\label{fig2b}
 \end{figure}
@@
 \begin{figure}[h!] 
-	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
+	%\includegraphics[width=0.5\textwidth]{f3a.pdf}
+	\includegraphics[width=\column]{f3a.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
 The temperature dependence is weak, resulting in multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
-	}\label{fig3a}
+	}
+	\label{fig3a}
 \end{figure}
 \begin{figure}[h!]
-	\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
-	}\label{fig3b}
+	%\includegraphics[width=0.5\textwidth]{f3b.pdf}
+	\includegraphics[width=\column]{f3b.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
+	}
+	\label{fig3b}
 \end{figure}
 \begin{figure}[h!]
-	\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
-	}\label{fig3c}
+	%\includegraphics[width=0.5\textwidth]{f3c.pdf}
+	\includegraphics[width=\column]{f3c.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
+	}
+	\label{fig3c}
 \end{figure}
@@
 \begin{figure}[h!] 
-	\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
-	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
-	}\label{fig4a}
+	%\includegraphics[width=0.5\textwidth]{f4a.pdf}
+	\includegraphics[width=\column]{f4a.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
+	}
+	\label{fig4a}
 \end{figure}
@@
 \begin{figure}[h!]
-	\centering \includegraphics[width=0.45\textwidth]{f4b.pdf}
-	\includegraphics[width=0.475\textwidth]{f4c.pdf}
-	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+	%\includegraphics[width=0.45\textwidth]{f4b.pdf}
+	%\includegraphics[width=0.475\textwidth]{f4c.pdf}
+	\includegraphics[width=\column]{f4b.pdf}
+	\includegraphics[width=\column]{f4c.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
 The two figures differ in the scale of $M$.
@@
 Part (b) focuses on a range of $M$ around its critical value~$0$.
-	}\label{fig4b}
+	}
+	\label{fig4b}
 \end{figure}

### 2024-09-12 paper_text.tex
add acknowledgement
updates after feedback

--- 2024-09-10 paper_text.tex
@@
 In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}.
-In works~\cite{KozlovskiiDobush2020,PylyukDobush2020,PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} this model was used with a modified Morse potential describing the particle interaction.
+This model was used with the Morse potential in studies~\cite{KozlovskiiDobush2020,PylyukDobush2020} and with a modified Morse potential in~\cite{PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} as potentials describing the particle interaction.
 In particular, the equation of state was obtained in~\cite{KozlovskiiDobush2020} in the zero-mode approximation.
@@
 \subsection{Pressure as a function of temperature and chemical potential}
-The equation of state obtained in~\cite[see Eq.(42)]{KozlovskiiDobush2020} reads
+The equation of state obtained in~\cite{KozlovskiiDobush2020} reads
 \begin{equation}
@@
 
-The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a contribution in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$~\cite[see Eq.(24)]{KozlovskiiDobush2020}.
+The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a contribution in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$~\cite{KozlovskiiDobush2020}.
 
@@
 
-The quantity $\beta_c$ denotes the critical value of the inverse temperature. In~\cite[see Eq.(31)]{KozlovskiiDobush2020} it was found that
+The quantity $\beta_c$ denotes the critical value of the inverse temperature. In~\cite{KozlovskiiDobush2020} it was found that
 \begin{equation*}
@@
 \end{equation*}
-We also use the reduced temperature defined as $T = k_{\rm B}T/\varepsilon$, and thus its critical value $T^*_c = 4.995.$
+We also use the reduced temperature defined as $T^* = k_{\rm B}T/\varepsilon$, and thus its critical value $T^*_c = 4.995.$
 
 Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature.
-The numerical values for other coefficients used in this paper are the same as those in~\cite[see Eqs.(5), (23), and (24)]{KozlovskiiDobush2020}:
+The numerical values for other coefficients used in this paper are the same as those in~\cite[eqs.~(5), (23), and~(24)]{KozlovskiiDobush2020}:
 \begin{eqnarray}
@@
 \end{equation}
-The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite[see Eq.(31)]{KozlovskiiDobush2020}
+The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite{KozlovskiiDobush2020}
 \begin{equation}
@@
 \begin{equation}\label{eq:eosNT}
-	Pv\beta = E_\eta (\rho^*,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4.
+	Pv\beta = E_\rho (\rho^*,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4.
 \end{equation}
-The quantity $E_\nu (\rho^*, T)$ in \eqref{eq:ro_nT} is the function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}
+The quantity $E_\rho (\rho^*, T)$ in \eqref{eq:eosNT} is the same as function $E_\mu (M,T)$ \eqref{eq:E_mu} rewritten in terms of density and temperature taking into account the expression \eqref{eq:M_nT}
 \begin{eqnarray}\label{eq:E_nu}
-	E_\nu (\rho^*, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 
+	E_\rho (\rho^*, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 
 	\nonumber\\
@@
 	\label{eq:eosPTn_reduced}
-	P^* & = & (1 + \tau)T^*_c \bigg[ E_\eta (\rho^*,T) 
+	P^* & = & (1 + \tau)T^*_c \bigg[ E_\rho (\rho^*,T) 
 	\nonumber\\
@@
 \end{equation}
+Explicit calculation for $\beta^*_V$ is presented in Appendix~\ref{sec:app-a}.
 
@@
 	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
-The temperature dependence is weak, resulting in multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
+Multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
 	}\label{fig3a}
@@
 Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\rho^*$ for various values of temperature above the critical one.
+It is interesting to note that the temperature dependence is very weak in this case, and and multiple isotherms collapse onto the same line and are indistinguishable at the scale of the figure.
+This is not a surprised behavior, as similar one is observed for the thermal pressure coefficient of the Lennard-Jones fluid~\cite{YigzaweSadus2013} as well.
 The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig3b}.
@@
 
+\section{Acknowledgement}
+
+This work was supported by the National Research Foundation of Ukraine under the project No. 2023.03/0201 .
+
 \appendix
@@
 \end{equation}
-The derivative of the quantity $E_\nu$ from~\eqref{eq:E_nu} with respect to temperature $\tau$ is
+The derivative of the quantity $E_\rho$ from~\eqref{eq:E_nu} with respect to temperature $\tau$ is
 \begin{eqnarray}
-	\frac{\partial E_\nu}{\partial \tau} & = &  -\frac{1}{2}\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
+	\frac{\partial E_\rho}{\partial \tau} & = &  -\frac{1}{2}\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
 	\frac{\partial \beta W(0)}{\partial \tau} 
@@
 \begin{eqnarray}
-	\beta^*_V & = & E_\eta (\rho^*,T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
+	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
 	\nonumber\\
-	&& + (1+\tau) \left(\frac{\partial E_{\nu}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial \tilde{D}(0)}{\partial \tau}\right).
+	&& + (1+\tau) \left(\frac{\partial E_{\rho}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial \tilde{D}(0)}{\partial \tau}\right).
 \end{eqnarray}

### 2024-09-12 paper_text.tex

@@
 \begin{figure}[h!] 
-	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
+	%\includegraphics[width=0.5\textwidth]{f3a.pdf}
+	\includegraphics[width=\column]{f3a.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
 Multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
-	}\label{fig3a}
+	}
+	\label{fig3a}
 \end{figure}
 \begin{figure}[h!]
-	\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
-	}\label{fig3b}
+	%\includegraphics[width=0.5\textwidth]{f3b.pdf}
+	\includegraphics[width=\column]{f3b.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
+	}
+	\label{fig3b}
 \end{figure}
 \begin{figure}[h!]
-	\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
-	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
-	}\label{fig3c}
+	%\includegraphics[width=0.5\textwidth]{f3c.pdf}
+	\includegraphics[width=\column]{f3c.pdf}
+	\vskip-3mm
+	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
+	}
+	\label{fig3c}
 \end{figure}

### 2024-09-12 paper_text.tex
add final formula for betaV in appendix
change tilde D(0) for d

--- 2024-09-12 paper_text.tex
@@
 	\label{eq:eosMT}
-	Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
+	Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} d \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
 \end{equation}
@@
 \begin{align}\label{chem_pot}
-	&	M = \frac{\tilde\mu}{W(0)} + g_1 - \frac{g_3}{g_4} \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
+	&	M = \frac{\tilde\mu}{W(0)} + g_1 - \frac{g_3}{g_4} d - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
 	&	\tilde\mu=\mu-\mu_0(1+\tau),
@@
 
-The quantity $\tilde D(0)$ entering equations~\eqref{eq:eosMT} and~\eqref{chem_pot} is a function of temperature
+The quantity $d$ entering equations~\eqref{eq:eosMT} and~\eqref{chem_pot} is a function of temperature
 \begin{equation}
 	\label{def:D0}
-	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
+	d = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
 \end{equation}
-The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite{KozlovskiiDobush2020}
+The condition $d = 0$ defines the critical temperature~\cite{KozlovskiiDobush2020}
 \begin{equation}
@@
 	\nonumber\\
-	&& - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
+	&& - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  d - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
 \end{eqnarray}
@@
 \begin{equation}\label{eq:ro_M}
-	M + \tilde D(0) \bar\rho_0 - \frac{a_4}{6} \bar\rho_0^3 = 0.
+	M + d \bar\rho_0 - \frac{a_4}{6} \bar\rho_0^3 = 0.
 \end{equation}
@@
 \begin{equation}
-	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3 M}{g_4}\right)^2, \qquad g_4<0.
+	Q_t = \left(  \frac{2d}{g_4}\right)^3 + \left( -\frac{3 M}{g_4}\right)^2, \qquad g_4<0.
 \end{equation}
@@
 	\nonumber\\
-	&& + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4
+	&& + M \bar \rho_0 + \frac{1}{2} d \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4
 	\bigg].
@@
 \begin{equation}\label{eq:eosNT}
-	Pv\beta = E_\rho (\rho^*,T) + \bar M \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4.
+	Pv\beta = E_\rho (\rho^*,T) + \bar M \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4.
 \end{equation}
@@
 	&& - \frac{\beta W(0)}{2} 
-	\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
+	\left(\bar{M} - g_1 + \frac{g_3}{g_4} d + \frac{g_3^3}{6g_4^2} \right)^{2} 
 	\nonumber\\
-	&& - \frac{g_3}{g_4} {\bar{M}} - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
+	&& - \frac{g_3}{g_4} {\bar{M}} - \frac{g_3^2}{2 g_4^2}  d - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
 \end{eqnarray}
@@
 	\nonumber\\
-	&& + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\bigg].
+	&& + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\bigg].
 \end{eqnarray}
@@
 \end{equation*}
-For $\tilde{D}(0)$ from~\eqref{def:D0} one has
+For $d$ from~\eqref{def:D0} one has
 \begin{equation}
-	\frac{\partial \tilde{D}(0)}{\partial \tau} = -\frac{k_{\rm B}T_c}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0}.
+	\frac{\partial d}{\partial \tau} = -\frac{k_{\rm B}T_c}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0}.
 \end{equation}
@@
 \begin{eqnarray}
-	\frac{\partial E_\rho}{\partial \tau} & = &  -\frac{1}{2}\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)^{2} 
+	\frac{\partial E_\rho}{\partial \tau} & = &  -\frac{1}{2}\left(\bar{M} - g_1 + \frac{g_3}{g_4} d + \frac{g_3^3}{6g_4^2} \right)^{2} 
 	\frac{\partial \beta W(0)}{\partial \tau} 
 	\nonumber\\
-	&&-\beta W(0)\left(\bar{M} - g_1 + \frac{g_3}{g_4} \tilde{D}(0) + \frac{g_3^3}{6g_4^2} \right)
+	&&-\beta W(0)\left(\bar{M} - g_1 + \frac{g_3}{g_4} d + \frac{g_3^3}{6g_4^2} \right)
 	\nonumber\\
-	&& \times \left(\frac{\partial \bar{M}}{\partial \tau} + \frac{g_3}{g_4}\frac{\partial\tilde{D}(0)}{\partial \tau}\right)
+	&& \times \left(\frac{\partial \bar{M}}{\partial \tau} + \frac{g_3}{g_4}\frac{\partial d}{\partial \tau}\right)
 	\nonumber\\
 	&& -\frac{g_3}{g_4}\frac{\partial \bar{M}}{\partial \tau} 
-	- \frac{g_3^2}{2g_4^2}\frac{\partial \tilde{D}(0)}{\partial \tau}.
+	- \frac{g_3^2}{2g_4^2}\frac{\partial d}{\partial \tau}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{\tilde D(0)}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
+	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
 	\nonumber\\
-	&& + (1+\tau) \left(\frac{\partial E_{\rho}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial \tilde{D}(0)}{\partial \tau}\right).
+	&& + (1+\tau) \left(\frac{\partial E_{\rho}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial d}{\partial \tau}\right).
 \end{eqnarray}
+Substituting the expressions for derivatives and grouping similar terms, one finally arrives at
+\begin{eqnarray}
+	&& \beta^*_V  =  E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4 + k_{\rm B} T_c (1+\tau)
+	\nonumber\\
+	&& \times \left( \frac{\beta^2}{2}  \Phi^{(r)}(0) [B - 1 - A_\gamma]	\left(\bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right)^2 \right . \nonumber \\
+	&& \left . + \frac{1}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0} \left\{ \frac{g_3^2}{2 g_4^2} + \frac{\rho_n^2}{2} - \frac{g_3}{g_4} \rho_n  \right . \right . \nonumber \\
+	&& \left . \left . + \beta W(0) \left( \bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right) \left( \frac{g_3}{g_4} - \rho_n \right)    \right\} \right).
+\end{eqnarray}

### 2024-09-12 paper_text.tex
add derivation of kappa_T in Appendix, mentioned it in text

@@
 It is expressed in terms of the reduced quantities $P^*$ and $\rho^*$ as follows
-\begin{eqnarray}
+\begin{eqnarray}\label{eq:kappa_star_m}
 	\kappa^*_T & = & \frac{\varepsilon}{{\rho^*}^2} \left(\frac{\partial \rho^*}{\partial \mu}\right)_T
@@
 Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $\kappa^*_T$, with the result expressed as a function of temperature and chemical potential.
+As an example, in Appendix~\ref{sec:app-a} we provide the derivation of the relation for the isothermal compressibility from the upper line of \eqref{eq:kappa_star_m}.
 
@@
 \end{eqnarray}
+
+As an example, we also give the derivation of the relation for the isothermal compressibility $\kappa^*_T$ from the upper line of \eqref{eq:kappa_star_m} recalling the density $\rho^*$ defined in \eqref{eq:density}.
+
+For the effective chemical potential $M$ from \eqref{chem_pot} one has
+\begin{equation}
+\left(\frac{\partial M}{\partial \mu} \right)_T = \frac{1}{W(0)}.
+\end{equation}
+For the quantity $\bar \rho_0$ from \eqref{eq:ro_MT} one has
+\begin{equation}
+\left(\frac{\partial \bar \rho_0}{\partial \mu} \right)_T = \frac{1}{ g_4 W(0) \sqrt{Q_t}} \left( \bar \rho_0 - 2 \left[ - \frac{3M}{g_4} + \sqrt{Q_t} \right]^{\frac{1}{3}} \right).
+\end{equation}
+Using these two formulas we obtain the isothermal compressibility in explicit form  
+\begin{eqnarray}
+&&	\kappa_T^* = \frac{\epsilon}{\rho^{*2} W(0)} \nonumber \\
+&& \times \left\{  \frac{1}{\beta W(0) g_4 \sqrt{Q_t}} \left( \bar \rho_0 - 2 \left[ - \frac{3M}{g_4} + \sqrt{Q_t} \right]^{\frac{1}{3}} \right) - 1 \right\}.
+\end{eqnarray}

### 2024-09-12 paper_text.tex
edit acknowledgement according to ujp style

--- 2024-09-12 paper_text.tex
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
-	%\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
-	\includegraphics[width=\column]{f1a1.pdf} 
-	\includegraphics[width=\column]{f1b1.pdf}
-	\vskip-3mm
-	\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines.
+	\centering 
+	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
+	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
+	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines.
 Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
-	}
-	\label{fig1}
+	}\label{fig1}
 \end{figure}
@@
 \begin{figure}[htbp]
-	%\includegraphics[width=0.5\textwidth]{f2a.pdf}
-	\includegraphics[width=\column]{f2a}
-	\vskip-3mm
+	%\centering 
+	\includegraphics[width=0.5\textwidth]{f2a.pdf}
+	%\includegraphics[width=\column]{f2a}
+	%\vskip-3mm
 	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.45\textwidth]{f2b.pdf}
-	%\includegraphics[width=0.475\textwidth]{f2c.pdf}
-	\includegraphics[width=\column]{f2b.pdf}
-	\includegraphics[width=\column]{f2c.pdf}
-	\vskip-3mm
-	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+	\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
+	\includegraphics[width=0.475\textwidth]{f2c.pdf}
+	\vskip-3mm\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
 The two figures differ in the scale of $M$.
@@
 Part~(b) focuses on a range of $M$ around its critical value $0$.
-	}
-	\label{fig2b}
+	}\label{fig2b}
 \end{figure}
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.5\textwidth]{f3a.pdf}
-	\includegraphics[width=\column]{f3a.pdf}
-	\vskip-3mm
-	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
+	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
+	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
 Multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
-	}
-	\label{fig3a}
+	}\label{fig3a}
 \end{figure}
 \begin{figure}[h!]
-	%\includegraphics[width=0.5\textwidth]{f3b.pdf}
-	\includegraphics[width=\column]{f3b.pdf}
-	\vskip-3mm
-	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
-	}
-	\label{fig3b}
+	\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
+	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
+	}\label{fig3b}
 \end{figure}
 \begin{figure}[h!]
-	%\includegraphics[width=0.5\textwidth]{f3c.pdf}
-	\includegraphics[width=\column]{f3c.pdf}
-	\vskip-3mm
-	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
-	}
-	\label{fig3c}
+	\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
+	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
+	}\label{fig3c}
 \end{figure}
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.5\textwidth]{f4a.pdf}
-	\includegraphics[width=\column]{f4a.pdf}
-	\vskip-3mm
-	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
-	}
-	\label{fig4a}
+	\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
+	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
+	}\label{fig4a}
 \end{figure}
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.45\textwidth]{f4b.pdf}
-	%\includegraphics[width=0.475\textwidth]{f4c.pdf}
-	\includegraphics[width=\column]{f4b.pdf}
-	\includegraphics[width=\column]{f4c.pdf}
-	\vskip-3mm
-	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
+	\centering \includegraphics[width=0.45\textwidth]{f4b.pdf}
+	\includegraphics[width=0.475\textwidth]{f4c.pdf}
+	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
 The two figures differ in the scale of $M$.
@@
 Part (b) focuses on a range of $M$ around its critical value~$0$.
-	}
-	\label{fig4b}
+	}\label{fig4b}
 \end{figure}
@@
 
-\section{Acknowledgement}
-
-This work was supported by the National Research Foundation of Ukraine under the project No. 2023.03/0201 .
+%\section{Acknowledgement}
+\vskip3mm \textit{This work was supported by the National Research Foundation of Ukraine under the project No.~2023.03/0201.}
 

### 2024-09-12 paper_text.tex
update appendix

--- 2024-09-12 paper_text.tex
@@
 \begin{eqnarray}
+	\label{eq:kappa_star_m1}
 	\kappa^*_T & = & \frac{\varepsilon}{{\rho^*}^2} \left(\frac{\partial \rho^*}{\partial \mu}\right)_T
-	\nonumber\\
+	\\
+	\label{eq:kappa_star_m}
 	& = & \frac{\varepsilon^2}{{\rho^*}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
@@
 Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $\kappa^*_T$, with the result expressed as a function of temperature and chemical potential.
+In Appendix~\ref{sec:app-a}, we provide the derivation of the explicit expression for the isothermal compressibility based on~\eqref{eq:kappa_star_m1}.
 
@@
 \section{\label{sec:app-a} Explicit expressions for derivatives}
-In this Appendix, we provide an explicit example of differentiating the equation of state, namely~\eqref{eq:eosPTn_reduced}, by deriving the expression for the thermal pressure coefficient $\beta^*_V$ from~\eqref{eq:beta_star_n}.
+This Appendix contains two examples of explicit derivation of response functions.
 
+First, we provide an explicit example of differentiating the equation of state, namely~\eqref{eq:eosPTn_reduced}, by deriving the expression for the thermal pressure coefficient $\beta^*_V$ from~\eqref{eq:beta_star_n}.
 For the quantity $\bar{M}$ from Eq.~\eqref{eq:M_nT} one has
@@
 \begin{eqnarray}
-	&& \beta^*_V  =  E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4 + k_{\rm B} T_c (1+\tau)
+	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4 + k_{\rm B} T_c (1+\tau)
 	\nonumber\\
-	&& \times \left( \frac{\beta^2}{2}  \Phi^{(r)}(0) [B - 1 - A_\gamma]	\left(\bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right)^2 \right . \nonumber \\
-	&& \left . + \frac{1}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0} \left\{ \frac{g_3^2}{2 g_4^2} + \frac{\rho_n^2}{2} - \frac{g_3}{g_4} \rho_n  \right . \right . \nonumber \\
-	&& \left . \left . + \beta W(0) \left( \bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right) \left( \frac{g_3}{g_4} - \rho_n \right)    \right\} \right).
+	&& \times \left\{ \frac{\beta^2}{2}  \Phi^{(r)}(0) [B - 1 - A_\gamma]	\left(\bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right)^2 \right . \nonumber \\
+	&& \left . + \frac{1}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0} \left[ \frac{g_3^2}{2 g_4^2} + \frac{\rho_n^2}{2} - \frac{g_3}{g_4} \rho_n  \right . \right . \nonumber \\
+	&& \left . \left . + \beta W(0) \left( \bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right) \left( \frac{g_3}{g_4} - \rho_n \right)    \right] \right\}.
 \end{eqnarray}
+
+Second, we derive the explicit expression for the isothermal compressibility $\kappa^*_T$ using~\eqref{eq:kappa_star_m}, taking the density $\rho^*$ from \eqref{eq:density}.
+For the effective chemical potential $M$ from \eqref{chem_pot} one has
+\begin{equation}
+\left(\frac{\partial M}{\partial \mu} \right)_T = \frac{1}{W(0)}.
+\end{equation}
+For the quantity $\bar \rho_0$ from \eqref{eq:ro_MT} one has
+\begin{equation}
+\left(\frac{\partial \bar \rho_0}{\partial \mu} \right)_T = \frac{1}{ g_4 W(0) \sqrt{Q_t}} \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right].
+\end{equation}
+Using these two formulas we obtain the isothermal compressibility in explicit form  
+\begin{eqnarray}
+	\kappa_T^* & = & \frac{\epsilon}{\rho^{*2} W(0)} \nonumber \\
+	&& \times \left\{  \frac{1}{\beta W(0) g_4 \sqrt{Q_t}} \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right] - 1 \right\}.
+\end{eqnarray}

### 2024-09-12 dobush_et_al_ujp_UTF8.tex
adjusted figures according to ujp styleguide
remove acknowledgement from main tex file
add ukr abstract

@@
 These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble.
-The calculated quantities are presented graphically as functions of density and chemical potential.
+The calculated quantities are presented graphically as functions of density and the effective chemical potential.
 	\end{abstract}
@@
 
-	\vskip3mm \textit{Acknowledgement.}
-
 	\bibliography{extracted}
@@
 	\vspace*{-5mm}\rezume{%Резюме укр. мовою
-		О.А.~Добуш, М.П.~Козловський, Р.В.~Романік, І.В.~Пилюк}{ТЕРМОДИНАМІЧНІ ФУНКЦІЇ ВІДГУКУ КОМІРКОВОЇ МОДЕЛІ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
+		О.А.~Добуш, М.П.~Козловський, Р.В.~Романік, І.В.~Пилюк}{ТЕРМОДИНАМІЧНІ ФУНКЦІЇ ВІДГУКУ КОМІРКОВОЇ МОДЕЛІ} {В роботі преведено розрахунки термодинамічних функцій відгуку - ізотермічної стисливості, термічного коефіцієнта тиску, та термічного коефіцієнта розширення - для системи частинок, які взаємодіють через модифікований потенціал Морзе.
+Ці розрахунки проводились виходячи з рівняння стану отриманого в попередній роботі для коміркової моделі плину в формалізмі великого канонічного ансамблю.
+Залежності отриманих величин від густини і ефективного хімічного потенціалу представлені графічно.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
 			с\,л\,о\,в\,а:} коміркова модель, потенціал Морзе, термодинамічні функції відгуку.}

### 2024-09-13 paper_text.tex
add ukr abstract
update reference to Fig1

@@
 
-Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\rho^*$ (see Fig.~\ref{fig1}a), and versus the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
+Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ as a function of density $\rho^*$ (see Fig.~\ref{fig1}a), and the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
 \begin{figure}[h!]
@@
 \begin{eqnarray}
-	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4 + k_{\rm B} T_c (1+\tau)
+	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
 	\nonumber\\
-	&& \times \left\{ \frac{\beta^2}{2}  \Phi^{(r)}(0) [B - 1 - A_\gamma]	\left(\bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right)^2 \right . \nonumber \\
-	&& \left . + \frac{1}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0} \left[ \frac{g_3^2}{2 g_4^2} + \frac{\rho_n^2}{2} - \frac{g_3}{g_4} \rho_n  \right . \right . \nonumber \\
-	&& \left . \left . + \beta W(0) \left( \bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2} \right) \left( \frac{g_3}{g_4} - \rho_n \right)    \right] \right\}.
+	& + & \left\{ \frac{\beta}{2}  \Phi^{(r)}(0) [B - 1 - A_\gamma]	G_M^2 \right . \nonumber \\
+	& + & \left. \frac{1}{\beta W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0} \left[ \frac{g_3^2}{2 g_4^2} + \frac{\rho_n^2}{2} - \frac{g_3}{g_4} \rho_n  \right . \right . \nonumber \\
+	& + & \left. \left. \beta W(0) G_M \left( \frac{g_3}{g_4} - \rho_n \right)    \right] \right\},
 \end{eqnarray}
+where we introduced notation
+\begin{equation*}
+	G_M = \bar{M} - g_1+ \frac{g_3}{g_4} d + \frac{1}{6} \frac{g_3^3}{g_4^2}.
+\end{equation*}
 
@@
 \begin{eqnarray}
-	\kappa_T^* & = & \frac{\epsilon}{\rho^{*2} W(0)} \nonumber \\
-	&& \times \left\{  \frac{1}{\beta W(0) g_4 \sqrt{Q_t}} \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right] - 1 \right\}.
+	\kappa_T^* & = & \frac{\epsilon}{\rho^{*2} W(0)} \bigg\{ -1
+	\\
+	& + & \left. \frac{Q_t^{-1/2}}{\beta W(0) g_4} \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right]\right\}.
+	\nonumber
 \end{eqnarray}

### 2024-09-13 paper_text.tex
adjust references according to ujp guide

--- 2024-09-13 paper_text.tex
@@
 \end{eqnarray}
+
+\begin{thebibliography}{9}
+	\bibitem{KozitskyKozlovskiiDobush2018book} Y.~Kozitsky, M.~Kozlovskii, O.~Dobush.
+	\href{https://link.springer.com/chapter/10.1007/978-3-319-61109-9_11}{Phase transitions in a continuum curie-weiss system: A quantitative analysis.}, in: L.~A.~Bulavin, A.~V.~Chalyi (Eds.), \textit{Modern Problems of Molecular Physics} (Springer, 2018) [doi: 10.1007/978-3-319-61109-9\_11]
+
+	\bibitem{KozitskyKozlovskiiDobush2020} Y.~Kozitsky, M.~Kozlovskii, O.~Dobush.
+	\href{https://icmp.lviv.ua/journal/zbirnyk.102/23502/abstract.html}{A phase transition in a Curie-Weiss system with binary interactions.}, \textit{Condens.
+	Matter Phys.} \textbf{23}, 23502 (2020) [doi: 10.5488/CMP.23.23502]
+
+	\bibitem{KozlovskiiDobush2020} M.~Kozlovskii, O.~Dobush.
+	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2019631}{Phase
+	behavior of a cell fluid model with modified Morse potential.}, \textit{Ukr. J. Phys.} \textbf{65}, 428 (2020) [doi: 10.15407/ujpe65.5.428]
+
+	\bibitem{PylyukDobush2020} I.~Pylyuk, O.~Dobush.
+\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2020185}{Equation of state of a cell fluid model with allowance for Gaussian fluctuations of the order parameter.}, \textit{Ukr.
+J.
+Phys.} \textbf{65}, 1080 (2020) [doi: 10.15407/ujpe65.12.1080]
+
+	\bibitem{PylyukEtAlJML2023}	I.~Pylyuk, M.~Kozlovskii, O.~Dobush, M.~Dufanets.
+	\href{https://www.sciencedirect.com/science/article/pii/S0167732223011261}{Morse fluids in the immediate vicinity of the critical point: Calculation of thermodynamic coefficients.}, \textit{J.
+Mol.
+Liq.} \textbf{385}, 122322 (2023) [doi: 10.1016/j.molliq.2023.122322]
+
+	\bibitem{PylyukKozlovskiiDobushUJP2023b} I.~Pylyuk, M.~Kozlovskii, O.~Dobush.
+	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2023197}{Analytic calculation of the critical temperature and estimation of the critical region size for a fluid model.}, \textit{Ukr.
+J.
+Phys.} \textbf{68}, 601 (2023) [doi: 10.15407/ujpe68.9.601]
+
+	\bibitem{StrokerMeier2021} P.~Str\"oker, K.~Meier.
+	\href{https://link.aps.org/doi/10.1103/PhysRevE.104.014117}{Classical
+	statistical mechanics in the grand canonical ensemble.}, \textit{Phys. Rev. E} \textbf{104}, 014117 (2021) [doi: 10.1103/PhysRevE.104.014117]
+
+	\bibitem{Morse1929}	P.~M.~Morse. \href{https://link.aps.org/doi/10.1103/PhysRev.34.57}{Diatomic
+	molecules according to the wave mechanics. II. Vibrational levels.}, \textit{Phys.
+	Rev.} \textbf{34}, 57 (1929) [doi: 10.1103/PhysRev.34.57]
+
+	\bibitem{MartinezValenciaEtAl2013} A.~Martínez-Valencia, M.~González-Melchor, P.~Orea, J.~López-Lemus.
+	\href{https://doi.org/10.1080/08927022.2012.702422}{Liquid–vapour interface
+	varying the softness and range of the interaction potential.}, \textit{Molecular
+	Simulation} \textbf{39}, 64 (2013) [doi: 10.1080/08927022.2012.702422]
+
+	\bibitem{BiswasHamann1985} R.~Biswas, D.~R. Hamann.
+	\href{https://link.aps.org/doi/10.1103/PhysRevLett.55.2001}{Interatomic
+	potentials for silicon structural energies.}, \textit{Phys. Rev. Lett.} \textbf{55}, 2001 (1985) [doi: 10.1103/PhysRevLett.55.2001]
+
+	\bibitem{Lim2005} T.-C. Lim. \href{https://acta-arhiv.chem-soc.si/52/52-2-149.htm}{Approximate
+	relationships between the generalized Morse and the extended-Rydberg potential energy functions.}, \textit{Acta Chim. Slov.} \textbf{52}, 149 (2005)
+
+	\bibitem{KozlovskiiDobush2016} M.~Kozlovskii, O.~Dobush.
+	\href{https://www.sciencedirect.com/science/article/pii/S0167732215312101}{Representation of the grand partition function of the cell model: The state equation in the mean-field approximation}, \textit{J.
+Mol.
+Liq.} \textbf{215}, 58 (2016) [doi: j.molliq.2015.12.018]
+
+	\bibitem{HansenMcDonald2013} J.~Hansen, I.~McDonald. \textit{Theory of Simple Liquids: with Applications to Soft Matter} (Academic Press, 2013) [ISBN: 9780123870339]
+
+	\bibitem{YigzaweSadus2013} T.~M. Yigzawe, R.~J. Sadus.
+	\href{https://doi.org/10.1063/1.4803855}{Intermolecular interactions and the thermodynamic properties of supercritical fluids}, \textit{J.
+Chem.
+Phys.} \textbf{138}, 194502 (2013) [doi: 10.1063/1.4803855]
+
+\end{thebibliography}

### 2024-09-13 paper_text.tex
adjust references

@@
 In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}.
-This model was used with the Morse potential in studies~\cite{KozlovskiiDobush2020,PylyukDobush2020} and with a modified Morse potential in~\cite{PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} as potentials describing the particle interaction.
+This model was used with the Morse potential in studies~\cite{PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} and with a modified Morse potential in~\cite{KozlovskiiDobush2020,PylyukDobush2020} as potentials describing the particle interaction.
 In particular, the equation of state was obtained in~\cite{KozlovskiiDobush2020} in the zero-mode approximation.
@@
 
-	\bibitem{HansenMcDonald2013} J.~Hansen, I.~McDonald. \textit{Theory of Simple Liquids: with Applications to Soft Matter} (Academic Press, 2013) [ISBN: 9780123870339]
+	\bibitem{HansenMcDonald2013} J.~Hansen, I.~McDonald. \textit{Theory of Simple Liquids: with Applications to Soft Matter.} 4th Edition (Academic Press, 2013) [ISBN: 9780123870339]
 

### 2024-09-13 paper_text.tex
figs for compilation in draft
add applicability part

@@
 
+Note that the theoretical approach used here has certain limits of applicability.
+The point is that the equations of state \eqref{eq:eosMT} and \eqref{eq:eosNT} of the cell fluid model are derived from calculating the grand partition function in the zero mode approximation of the $\rho^4$-model.
+At one stage of the calculation, we establish an explicit connection between the effective chemical potential $\bar M$ and the density $\rho^*$ by solving the cubic equation, which is derived from combining equations~\eqref{eq:density} and~\eqref{eq:ro_M} (see \cite{KozlovskiiDobush2020}, Section 5).
+This equation has three roots.
+Two solutions are nonphysical because they consequently reflect a decrease in chemical potential with increasing density.
+The third solution, namely \eqref{eq:ro_nT}, indicates the growth of the chemical potential with increasing density, but it is only valid for a limited range of densities $\rho^*_{min} \leqslant \rho^* \leqslant \rho^*_{max}$, where
+	\begin{eqnarray}
+		\rho^*_{min} &=& \rho^*_c - \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}, \\
+		\rho^*_{max} &=& \rho^*_c + \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}. \nonumber
+	\end{eqnarray}
+	The density's marginal values vary depending on the selected parameters $\alpha^*$ and $p$.
+Providing the set of coefficients \eqref{params}, one has $\rho^*_{min} = 0.009$ and $\rho^*_{max} = 1.946$.
+
 Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ as a function of density $\rho^*$ (see Fig.~\ref{fig1}a), and the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
 \begin{figure}[h!]
-	%\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
-	%\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
-	\includegraphics[width=\column]{f1a1.pdf} 
-	\includegraphics[width=\column]{f1b1.pdf}
+	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
+	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
+	%\includegraphics[width=\column]{f1a1.pdf} 
+	%\includegraphics[width=\column]{f1b1.pdf}
 	\vskip-3mm
@@
 \begin{figure}[htbp]
-	%\includegraphics[width=0.5\textwidth]{f2a.pdf}
-	\includegraphics[width=\column]{f2a}
+	\includegraphics[width=0.5\textwidth]{f2a.pdf}
+	%\includegraphics[width=\column]{f2a}
 	\vskip-3mm
@@
 \begin{figure}[h!] 
-	%\includegraphics[width=0.45\textwidth]{f2b.pdf}
-	%\includegraphics[width=0.475\textwidth]{f2c.pdf}
-	\includegraphics[width=\column]{f2b.pdf}
-	\includegraphics[width=\column]{f2c.pdf}
+	\includegraphics[width=0.45\textwidth]{f2b.pdf}
+	\includegraphics[width=0.475\textwidth]{f2c.pdf}
+	%\includegraphics[width=\column]{f2b.pdf}
+	%\includegraphics[width=\column]{f2c.pdf}
 	\vskip-3mm
@@
 \begin{figure}[h!] 
-	%\includegraphics[width=0.5\textwidth]{f3a.pdf}
-	\includegraphics[width=\column]{f3a.pdf}
+	\includegraphics[width=0.5\textwidth]{f3a.pdf}
+	%\includegraphics[width=\column]{f3a.pdf}
 	\vskip-3mm
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.5\textwidth]{f3b.pdf}
-	\includegraphics[width=\column]{f3b.pdf}
+	\includegraphics[width=0.5\textwidth]{f3b.pdf}
+	%\includegraphics[width=\column]{f3b.pdf}
 	\vskip-3mm
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.5\textwidth]{f3c.pdf}
-	\includegraphics[width=\column]{f3c.pdf}
+	\includegraphics[width=0.5\textwidth]{f3c.pdf}
+	%\includegraphics[width=\column]{f3c.pdf}
 	\vskip-3mm
@@
 \begin{figure}[h!] 
-	%\includegraphics[width=0.5\textwidth]{f4a.pdf}
-	\includegraphics[width=\column]{f4a.pdf}
+	\includegraphics[width=0.5\textwidth]{f4a.pdf}
+	%\includegraphics[width=\column]{f4a.pdf}
 	\vskip-3mm
@@
 \begin{figure}[h!]
-	%\includegraphics[width=0.45\textwidth]{f4b.pdf}
-	%\includegraphics[width=0.475\textwidth]{f4c.pdf}
-	\includegraphics[width=\column]{f4b.pdf}
-	\includegraphics[width=\column]{f4c.pdf}
+	\includegraphics[width=0.45\textwidth]{f4b.pdf}
+	\includegraphics[width=0.475\textwidth]{f4c.pdf}
+	%\includegraphics[width=\column]{f4b.pdf}
+	%\includegraphics[width=\column]{f4c.pdf}
 	\vskip-3mm

### 2024-09-13 paper_text.tex
update paragraph on applicability

@@
 
-Note that the theoretical approach used here has certain limits of applicability.
-The point is that the equations of state \eqref{eq:eosMT} and \eqref{eq:eosNT} of the cell fluid model are derived from calculating the grand partition function in the zero mode approximation of the $\rho^4$-model.
-At one stage of the calculation, we establish an explicit connection between the effective chemical potential $\bar M$ and the density $\rho^*$ by solving the cubic equation, which is derived from combining equations~\eqref{eq:density} and~\eqref{eq:ro_M} (see \cite{KozlovskiiDobush2020}, Section 5).
-This equation has three roots.
-Two solutions are nonphysical because they consequently reflect a decrease in chemical potential with increasing density.
-The third solution, namely \eqref{eq:ro_nT}, indicates the growth of the chemical potential with increasing density, but it is only valid for a limited range of densities $\rho^*_{min} \leqslant \rho^* \leqslant \rho^*_{max}$, where
-	\begin{eqnarray}
-		\rho^*_{min} &=& \rho^*_c - \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}, \\
-		\rho^*_{max} &=& \rho^*_c + \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}. \nonumber
-	\end{eqnarray}
-	The density's marginal values vary depending on the selected parameters $\alpha^*$ and $p$.
-Providing the set of coefficients \eqref{params}, one has $\rho^*_{min} = 0.009$ and $\rho^*_{max} = 1.946$.
+The equations of state~\eqref{eq:eosMT} and \eqref{eq:eosNT} are derived in the zero-mode approximation of the $\rho^4$-model, which imposes limits on their applicability.
+Specifically, in terms of density, the equations are  applicable for $\rho^*_{\rm min} \leq \rho^* < \rho^*_{\rm max}$, where $\rho^*_{\rm min}$ and $\rho^*_{\rm max}$ are determined by the parameters $\alpha^*$ and $p$.
+For parameters given in~\eqref{params}, these values were estimated in~\cite{KozlovskiiDobush2020} as $\rho^*_{\rm min} = 0.009$ and $\rho^*_{\rm max} = 1.946$.
 

### 2024-09-13 paper_text.tex
add width=column in includegraphics

--- 2024-09-13 paper_text.tex
@@
 \end{eqnarray}
+
+The equations of state~\eqref{eq:eosMT} and \eqref{eq:eosNT} are derived in the zero-mode approximation of the $\rho^4$-model, which imposes limits on their applicability.
+Specifically, in terms of density, the equations are  applicable for $\rho^*_{\rm min} \leq \rho^* < \rho^*_{\rm max}$, where $\rho^*_{\rm min}$ and $\rho^*_{\rm max}$ are determined by the parameters $\alpha^*$ and $p$.
+For parameters given in~\eqref{params}, these values were estimated in~\cite{KozlovskiiDobush2020} as $\rho^*_{\rm min} = 0.009$ and $\rho^*_{\rm max} = 1.946$.
 

### 2024-09-13 paper_text.tex
add bulavin + references in text, in bib

--- 2024-09-13 paper_text.tex
@@
 \section{Introduction}
+
+Thermodynamic response functions play a crucial role in understanding and characterizing the behavior of physical systems.
+These functions describe how a system responds to changes in its state variables, providing valuable insights into its thermodynamic properties.
+The most widely studied thermodynamic response functions of fluids are isothermal and adiabatic compressibilities, isobaric thermal expansion, isochoric thermal pressure coefficient and heat capacities either at constant pressure or at constant volume.
+Thermodynamic response functions are essential tools for understanding, predicting, and controlling the behavior of physical systems.
+They are used in various scientific and engineering disciplines to model, design, and optimize processes and to gain insights into the fundamental principles governing thermodynamic systems.
+Therefore, a key area of research involves examining the thermodynamic properties of simple fluids and fluid models through theoretical approaches, computer simulations, and experimental studies, covering both subcritical and supercritical regions.~\cite{Johnston2014book,YigzaweSadus2013,Velasco2011,Bulavin2024}.
+
 In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}.
@@
 \begin{thebibliography}{9}
+
+	\bibitem{Johnston2014book} D.~C.~Johnston.
+	\href{https://dx.doi.org/10.1088/978-1-627-05532-1}{Advances in Thermodynamics of the van der {W}aals Fluid}, (Morgan \& Claypool Publishers, 2014) [doi: 10.1088/978-1-627-05532-1]
+
+	\bibitem{YigzaweSadus2013} T.~M. Yigzawe, R.~J. Sadus.
+	\href{https://doi.org/10.1063/1.4803855}{Intermolecular interactions and the thermodynamic properties of supercritical fluids}, \textit{J.
+Chem.
+Phys.} \textbf{138}, 194502 (2013) [doi: 10.1063/1.4803855]
+
+	\bibitem{Velasco2011} I~Velasco, C.~Rivas, J.~F.~Martinez-Lopez {\it et~al.}
+	\href{https://pubs.acs.org/doi/abs/10.1021/jp202317n}{Accurate values of some thermodynamic properties for carbon dioxide, ethane, propane, and some binary mixtures}, \textit{J.
+Phys.
+Chem.
+B} \textbf{115}, 8216 (2011) [doi: 10.1021/jp202317n]
+
+	\bibitem{Bulavin2024} L.~A.~Bulavin, Y.~G.~Rudnikov, A.~V.~Chalyi.
+	\href{https://pubs.aip.org/aip/adv/article/14/8/085213/3307287}{Contributions to the isothermal compressibility coefficient of water near the temperature of 42$^{\circ}$ C}, \textit{AIP Advances} \textbf{14}, 085213 (2024) [doi: 10.1063/5.0205612]
+
 	\bibitem{KozitskyKozlovskiiDobush2018book} Y.~Kozitsky, M.~Kozlovskii, O.~Dobush.
@@
 
-	\bibitem{YigzaweSadus2013} T.~M. Yigzawe, R.~J. Sadus.
-	\href{https://doi.org/10.1063/1.4803855}{Intermolecular interactions and the thermodynamic properties of supercritical fluids}, \textit{J.
-Chem.
-Phys.} \textbf{138}, 194502 (2013) [doi: 10.1063/1.4803855]
-
 \end{thebibliography}

### 2024-09-15 paper_text.tex
small adjustments for references

@@
 
-	\bibitem{Johnston2014book} D.~C.~Johnston.
-	\href{https://dx.doi.org/10.1088/978-1-627-05532-1}{Advances in Thermodynamics of the van der {W}aals Fluid}, (Morgan \& Claypool Publishers, 2014) [doi: 10.1088/978-1-627-05532-1]
+	\bibitem{Johnston2014book} D.C.~Johnston.
+	\textit{\href{https://dx.doi.org/10.1088/978-1-627-05532-1}{Advances in Thermodynamics of the van der {W}aals Fluid.}} (Morgan \& Claypool Publishers, 2014) [doi: 10.1088/978-1-627-05532-1]
 
 	\bibitem{YigzaweSadus2013} T.~M. Yigzawe, R.~J. Sadus.
-	\href{https://doi.org/10.1063/1.4803855}{Intermolecular interactions and the thermodynamic properties of supercritical fluids}, \textit{J.
+	\href{https://doi.org/10.1063/1.4803855}{Intermolecular interactions and the thermodynamic properties of supercritical fluids.} \textit{J.
 Chem.
@@
 
-	\bibitem{Velasco2011} I~Velasco, C.~Rivas, J.~F.~Martinez-Lopez {\it et~al.}
-	\href{https://pubs.acs.org/doi/abs/10.1021/jp202317n}{Accurate values of some thermodynamic properties for carbon dioxide, ethane, propane, and some binary mixtures}, \textit{J.
+	\bibitem{Velasco2011} I~Velasco, C.~Rivas, J.~F.~Martinez-Lopez, S.T.~Blanco, S.~Otin, M.~Artal.
+	\href{https://pubs.acs.org/doi/abs/10.1021/jp202317n}{Accurate values of some thermodynamic properties for carbon dioxide, ethane, propane, and some binary mixtures.} \textit{J.
 Phys.
@@
 	\bibitem{Bulavin2024} L.~A.~Bulavin, Y.~G.~Rudnikov, A.~V.~Chalyi.
-	\href{https://pubs.aip.org/aip/adv/article/14/8/085213/3307287}{Contributions to the isothermal compressibility coefficient of water near the temperature of 42$^{\circ}$ C}, \textit{AIP Advances} \textbf{14}, 085213 (2024) [doi: 10.1063/5.0205612]
+	\href{https://pubs.aip.org/aip/adv/article/14/8/085213/3307287}{Contributions to the isothermal compressibility coefficient of water near the temperature of 42$^{\circ}$ C.} \textit{AIP Advances} \textbf{14}, 085213 (2024) [doi: 10.1063/5.0205612]
 
 	\bibitem{KozitskyKozlovskiiDobush2018book} Y.~Kozitsky, M.~Kozlovskii, O.~Dobush.
-	\href{https://link.springer.com/chapter/10.1007/978-3-319-61109-9_11}{Phase transitions in a continuum curie-weiss system: A quantitative analysis.}, in: L.~A.~Bulavin, A.~V.~Chalyi (Eds.), \textit{Modern Problems of Molecular Physics} (Springer, 2018) [doi: 10.1007/978-3-319-61109-9\_11]
+	\href{https://link.springer.com/chapter/10.1007/978-3-319-61109-9_11}{Phase transitions in a continuum Curie-Weiss system: A quantitative analysis.} In: L.~A.~Bulavin, A.~V.~Chalyi (Eds.), \textit{Modern Problems of Molecular Physics} (Springer, 2018) [doi: 10.1007/978-3-319-61109-9\_11]
 
 	\bibitem{KozitskyKozlovskiiDobush2020} Y.~Kozitsky, M.~Kozlovskii, O.~Dobush.
-	\href{https://icmp.lviv.ua/journal/zbirnyk.102/23502/abstract.html}{A phase transition in a Curie-Weiss system with binary interactions.}, \textit{Condens.
+	\href{https://icmp.lviv.ua/journal/zbirnyk.102/23502/abstract.html}{A phase transition in a Curie-Weiss system with binary interactions.} \textit{Condens.
 	Matter Phys.} \textbf{23}, 23502 (2020) [doi: 10.5488/CMP.23.23502]
@@
 	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2019631}{Phase
-	behavior of a cell fluid model with modified Morse potential.}, \textit{Ukr. J. Phys.} \textbf{65}, 428 (2020) [doi: 10.15407/ujpe65.5.428]
+	behavior of a cell fluid model with modified Morse potential.} \textit{Ukr. J. Phys.} \textbf{65}, 428 (2020) [doi: 10.15407/ujpe65.5.428]
 
 	\bibitem{PylyukDobush2020} I.~Pylyuk, O.~Dobush.
-\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2020185}{Equation of state of a cell fluid model with allowance for Gaussian fluctuations of the order parameter.}, \textit{Ukr.
+\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2020185}{Equation of state of a cell fluid model with allowance for Gaussian fluctuations of the order parameter.} \textit{Ukr.
 J.
@@
 	\bibitem{PylyukEtAlJML2023}	I.~Pylyuk, M.~Kozlovskii, O.~Dobush, M.~Dufanets.
-	\href{https://www.sciencedirect.com/science/article/pii/S0167732223011261}{Morse fluids in the immediate vicinity of the critical point: Calculation of thermodynamic coefficients.}, \textit{J.
+	\href{https://www.sciencedirect.com/science/article/pii/S0167732223011261}{Morse fluids in the immediate vicinity of the critical point: Calculation of thermodynamic coefficients.} \textit{J.
 Mol.
@@
 	\bibitem{PylyukKozlovskiiDobushUJP2023b} I.~Pylyuk, M.~Kozlovskii, O.~Dobush.
-	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2023197}{Analytic calculation of the critical temperature and estimation of the critical region size for a fluid model.}, \textit{Ukr.
+	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2023197}{Analytic calculation of the critical temperature and estimation of the critical region size for a fluid model.} \textit{Ukr.
 J.
@@
 	\href{https://link.aps.org/doi/10.1103/PhysRevE.104.014117}{Classical
-	statistical mechanics in the grand canonical ensemble.}, \textit{Phys. Rev. E} \textbf{104}, 014117 (2021) [doi: 10.1103/PhysRevE.104.014117]
+	statistical mechanics in the grand canonical ensemble.} \textit{Phys. Rev. E} \textbf{104}, 014117 (2021) [doi: 10.1103/PhysRevE.104.014117]
 
 	\bibitem{Morse1929}	P.~M.~Morse. \href{https://link.aps.org/doi/10.1103/PhysRev.34.57}{Diatomic
-	molecules according to the wave mechanics. II. Vibrational levels.}, \textit{Phys.
+	molecules according to the wave mechanics. II. Vibrational levels.} \textit{Phys.
 	Rev.} \textbf{34}, 57 (1929) [doi: 10.1103/PhysRev.34.57]
@@
 	\href{https://doi.org/10.1080/08927022.2012.702422}{Liquid–vapour interface
-	varying the softness and range of the interaction potential.}, \textit{Molecular
+	varying the softness and range of the interaction potential.} \textit{Molecular
 	Simulation} \textbf{39}, 64 (2013) [doi: 10.1080/08927022.2012.702422]
@@
 	\href{https://link.aps.org/doi/10.1103/PhysRevLett.55.2001}{Interatomic
-	potentials for silicon structural energies.}, \textit{Phys. Rev. Lett.} \textbf{55}, 2001 (1985) [doi: 10.1103/PhysRevLett.55.2001]
+	potentials for silicon structural energies.} \textit{Phys. Rev. Lett.} \textbf{55}, 2001 (1985) [doi: 10.1103/PhysRevLett.55.2001]
 
 	\bibitem{Lim2005} T.-C. Lim. \href{https://acta-arhiv.chem-soc.si/52/52-2-149.htm}{Approximate
-	relationships between the generalized Morse and the extended-Rydberg potential energy functions.}, \textit{Acta Chim. Slov.} \textbf{52}, 149 (2005)
+	relationships between the generalized Morse and the extended-Rydberg potential energy functions.} \textit{Acta Chim. Slov.} \textbf{52}, 149 (2005)
 
 	\bibitem{KozlovskiiDobush2016} M.~Kozlovskii, O.~Dobush.
-	\href{https://www.sciencedirect.com/science/article/pii/S0167732215312101}{Representation of the grand partition function of the cell model: The state equation in the mean-field approximation}, \textit{J.
+	\href{https://www.sciencedirect.com/science/article/pii/S0167732215312101}{Representation of the grand partition function of the cell model: The state equation in the mean-field approximation.} \textit{J.
 Mol.

### 2024-09-15 paper_text.tex
make references more consistent
replace dependency with dependence; fix references order

@@
 Equations~\eqref{eq:density} and~\eqref{eq:eosMT} jointly define a parametric relationship between pressure and density, with $M$ serving as the parameter.
-Figure~\ref{fig1} shows the dependency of the reduced pressure $P^*$ on the density $\rho^*$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
+Figure~\ref{fig1} shows the dependence of the reduced pressure $P^*$ on the density $\rho^*$ for various values of the reduced temperature $\tau$, at and above the critical temperature.
 
-This dependency can also be expressed explicitly.
+This dependence can also be expressed explicitly.
 To achieve this, we combine the equations~\eqref{eq:density} and~\eqref{eq:ro_M} to express the effective chemical potential $M$ as a function of density and temperature:
@@
 The second one expresses the pressure as a function of temperature and density, $P = P(T, \rho^*)$, and is represented by equivalent Eqs.~\eqref{eq:eosNT} and~\eqref{eq:eosPTn_reduced}.
-These equations, together with the explicit dependency of density on temperature and chemical potential, $\rho^* = \rho^*(T, \mu)$, Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}.
+These equations, together with the explicit dependence of density on temperature and chemical potential, $\rho^* = \rho^*(T, \mu)$, Eq.~\eqref{eq:density}, are the basis for the calculation of the thermodynamic response functions in the next Section~\ref{sec:respons_functions}.
 
@@
 
-Figure~\ref{fig2a} illustrates the dependency of the compressibility $\kappa^*_T$ on the density $\rho^*$ for various values of temperature above the critical one.
-The dependency of $\kappa^*_T$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig2b}.
+Figure~\ref{fig2a} illustrates the dependence of the compressibility $\kappa^*_T$ on the density $\rho^*$ for various values of temperature above the critical one.
+The dependence of $\kappa^*_T$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig2b}.
 
@@
 
-Figure~\ref{fig3a} shows the dependency of the pressure coefficient $\beta^*_V$ on the density $\rho^*$ for various values of temperature above the critical one.
-It is interesting to note that the temperature dependence is very weak in this case, and and multiple isotherms collapse onto the same line and are indistinguishable at the scale of the figure.
+Figure~\ref{fig3a} shows the dependence of the pressure coefficient $\beta^*_V$ on the density $\rho^*$ for various values of temperature above the critical one.
+It is interesting to note that the temperature dependence is very weak in this case, and multiple isotherms collapse onto the same line and are indistinguishable at the scale of the figure.
 This is not a surprised behavior, as similar one is observed for the thermal pressure coefficient of the Lennard-Jones fluid~\cite{YigzaweSadus2013} as well.
-The dependency of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig3b}.
-The dependency of $\beta^*_V$ on the relative temperature $\tau$ is displayed in Fig.~\ref{fig3c} for a few values of density.
+The dependence of $\beta^*_V$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig3b}.
+The dependence of $\beta^*_V$ on the relative temperature $\tau$ is displayed in Fig.~\ref{fig3c} for a few values of density.
 
@@
 
-Figure~\ref{fig4a} shows the dependency of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\rho^*$ for various values of temperature above the critical one.
-The dependency of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig4b}.
+Figure~\ref{fig4a} shows the dependence of the reduced thermal expansion coefficient $\alpha^*_P$ on the density $\rho^*$ for various values of temperature above the critical one.
+The dependence of $\alpha^*_P$ on the effective chemical potential $M$ is displayed in Fig.~\ref{fig4b}.
 
@@
 
-	\bibitem{YigzaweSadus2013} T.~M. Yigzawe, R.~J. Sadus.
+	\bibitem{YigzaweSadus2013} T.M. Yigzawe, R.J.~Sadus.
 	\href{https://doi.org/10.1063/1.4803855}{Intermolecular interactions and the thermodynamic properties of supercritical fluids.} \textit{J.
@@
 
-	\bibitem{Velasco2011} I~Velasco, C.~Rivas, J.~F.~Martinez-Lopez, S.T.~Blanco, S.~Otin, M.~Artal.
+	\bibitem{Velasco2011} I~Velasco, C.~Rivas, J.F.~Martinez-Lopez, S.T.~Blanco, S.~Otin, M.~Artal.
 	\href{https://pubs.acs.org/doi/abs/10.1021/jp202317n}{Accurate values of some thermodynamic properties for carbon dioxide, ethane, propane, and some binary mixtures.} \textit{J.
@@
 
-	\bibitem{Bulavin2024} L.~A.~Bulavin, Y.~G.~Rudnikov, A.~V.~Chalyi.
+	\bibitem{Bulavin2024} L.A.~Bulavin, Y.G.~Rudnikov, A.V.~Chalyi.
 	\href{https://pubs.aip.org/aip/adv/article/14/8/085213/3307287}{Contributions to the isothermal compressibility coefficient of water near the temperature of 42$^{\circ}$ C.} \textit{AIP Advances} \textbf{14}, 085213 (2024) [doi: 10.1063/5.0205612]
@@
 	Matter Phys.} \textbf{23}, 23502 (2020) [doi: 10.5488/CMP.23.23502]
-
-	\bibitem{KozlovskiiDobush2020} M.~Kozlovskii, O.~Dobush.
-	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2019631}{Phase
-	behavior of a cell fluid model with modified Morse potential.} \textit{Ukr. J. Phys.} \textbf{65}, 428 (2020) [doi: 10.15407/ujpe65.5.428]
-
-	\bibitem{PylyukDobush2020} I.~Pylyuk, O.~Dobush.
-\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2020185}{Equation of state of a cell fluid model with allowance for Gaussian fluctuations of the order parameter.} \textit{Ukr.
-J.
-Phys.} \textbf{65}, 1080 (2020) [doi: 10.15407/ujpe65.12.1080]
 
@@
 Phys.} \textbf{68}, 601 (2023) [doi: 10.15407/ujpe68.9.601]
+
+	\bibitem{KozlovskiiDobush2020} M.~Kozlovskii, O.~Dobush.
+	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2019631}{Phase behavior of a cell fluid model with modified Morse potential.} \textit{Ukr.
+J.
+Phys.} \textbf{65}, 428 (2020) [doi: 10.15407/ujpe65.5.428]
+
+	\bibitem{PylyukDobush2020} I.~Pylyuk, O.~Dobush.
+\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2020185}{Equation of state of a cell fluid model with allowance for Gaussian fluctuations of the order parameter.} \textit{Ukr.
+J.
+Phys.} \textbf{65}, 1080 (2020) [doi: 10.15407/ujpe65.12.1080]
 
@@
 
-	\bibitem{BiswasHamann1985} R.~Biswas, D.~R. Hamann.
+	\bibitem{BiswasHamann1985} R.~Biswas, D.R.~Hamann.
 	\href{https://link.aps.org/doi/10.1103/PhysRevLett.55.2001}{Interatomic
@@
 
-	\bibitem{Lim2005} T.-C. Lim. \href{https://acta-arhiv.chem-soc.si/52/52-2-149.htm}{Approximate
+	\bibitem{Lim2005} T.-C.~Lim. \href{https://acta-arhiv.chem-soc.si/52/52-2-149.htm}{Approximate
 	relationships between the generalized Morse and the extended-Rydberg potential energy functions.} \textit{Acta Chim. Slov.} \textbf{52}, 149 (2005)

### 2024-09-15 paper_text.tex
punctuation

@@
 They are used in various scientific and engineering disciplines to model, design, and optimize processes and to gain insights into the fundamental principles governing thermodynamic systems.
-Therefore, a key area of research involves examining the thermodynamic properties of simple fluids and fluid models through theoretical approaches, computer simulations, and experimental studies, covering both subcritical and supercritical regions.~\cite{Johnston2014book,YigzaweSadus2013,Velasco2011,Bulavin2024}.
+Therefore, a key area of research involves examining the thermodynamic properties of simple fluids and fluid models through theoretical approaches, computer simulations, and experimental studies, covering both subcritical and supercritical regions~\cite{Johnston2014book,YigzaweSadus2013,Velasco2011,Bulavin2024}.
 
@@
 
-In Section~\ref{sec:potential} we present the modified Morse potential used in our work, and briefly compare it with other possible modifications.
+In Section~\ref{sec:potential}, we present the modified Morse potential used in our work, and briefly compare it with other possible modifications.
 Section~\ref{sec:eos} is dedicated to the explicit expressions for the equation of state.
-In Section~\ref{sec:respons_functions} the expressions for response functions are derived in terms of thermodynamic derivatives suitable for different forms of the equation of state.
+In Section~\ref{sec:respons_functions}, the expressions for response functions are derived in terms of thermodynamic derivatives suitable for different forms of the equation of state.
 
@@
 Here the quantity $N_v$ defines the number of cubic cells in volume $V$ for the initial model.
-In the thermodynamic limit, $N_v \to \infty$, and thus the first term can be neglected.
+In the thermodynamic limit, $N_v \to \infty$, and thus, the first term can be neglected.
 The term $\tilde{\mu}/W(0)$ can be expressed in terms of $M$ using~\eqref{chem_pot}.
@@
 \begin{equation*}
-	T = T_c(1+\tau), \quad \beta = \beta_c (1 + \tau)^{-1}
+	T = T_c(1+\tau), \quad \beta = \beta_c (1 + \tau)^{-1}.
 \end{equation*}
@@
 \begin{equation}
-	\kappa_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T}
+	\kappa_T = \frac{1}{\rho^2} \left(\frac{\partial \rho}{\partial \mu}\right)_{T} .
 \end{equation}
@@
 \begin{equation}
-	\left(\frac{\partial \rho}{\partial \mu}\right)_T = \left(\frac{\partial^2 P}{\partial \mu^2}\right)_T
+	\left(\frac{\partial \rho}{\partial \mu}\right)_T = \left(\frac{\partial^2 P}{\partial \mu^2}\right)_T ,
 \end{equation}
@@
 \begin{equation}
-	\kappa_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T}
+	\kappa_T = \frac{1}{\rho^2} \left(\frac{\partial^2 P}{\partial \mu^2}\right)_{T} .
 \end{equation}
@@
 \end{equation}
-We rewrite $\beta_V$ into a form that is suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced}
+We rewrite $\beta_V$ into a form that is suitable for the equation of state $P=P(T,\mu)$, see~\eqref{eq:eosMT} and~\eqref{eq:eosPTM_reduced},
 \begin{eqnarray}
@@
 \begin{equation}
-	\alpha_P = \frac{1}{\rho} \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T.
+	\alpha_P = \frac{1}{\rho} \left(\frac{\partial P}{\partial T}\right)_{\rho} \left(\frac{\partial P}{\partial \rho}\right)^{-1}_T ,
 \end{equation}

### 2024-09-15 ArXiv_morse_response_functions.tex
tex file for arXiv.org + preview pdf of our preprint

--- 2024-09-15 paper_text.tex
@@
+\documentclass[12pt,a4paper]{article}
+
+\usepackage[english]{babel}
+\usepackage[T2A]{fontenc}
+\usepackage[cp1251]{inputenc}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{amssymb}
+\usepackage{color}
+\usepackage{amsfonts}
+\usepackage{wrapfig}
+\usepackage{caption}
+
+\usepackage{hyperref}
+\usepackage{physics}
+
+\textheight=26cm
+\textwidth=17cm
+\hoffset=0pt
+\voffset=0cm
+\oddsidemargin=0cm
+\topmargin=-60pt
+\footskip=30pt
+\renewcommand{\baselinestretch}{1}
+
+%\textheight=24cm
+%\textwidth=17cm
+%\hoffset=0pt
+%\voffset=-20mm
+%\oddsidemargin=0cm
+%\topmargin=0pt
+%\footskip=30pt
+%\renewcommand{\baselinestretch}{1}
+
+\begin{document}
+
+	\binoppenalty=10000
+	\relpenalty=10000
+
+\begin{center}
+	\textbf{\Large{Thermodynamic response functions in a cell fluid model}}
+\end{center}
+
+\vspace{0.3cm}
+
+\begin{center}
+ O.A.~Dobush\footnote{e-mail:  dobush@icmp.lviv.ua}, M.P.~Kozlovskii, R.V.~Romanik\footnote{e-mail:  romanik@icmp.lviv.ua}, I.V.~Pylyuk 
+\end{center}
+
+\begin{center}
+	Institute for Condensed Matter Physics of the National Academy of Sciences of
+	Ukraine \\ 1, Svientsitskii Street, 79011 Lviv, Ukraine
+\end{center}
+
+	 \vspace{0.2cm}
+
+	\begin{center}
+ \small \textbf{Abstract} 
+	\end{center}
+
+	\small Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential.
+These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble.
+The calculated quantities are presented graphically as functions of density and the effective chemical potential.
+	\\
+	\textbf{Keywords:} simple fluids, Morse potential, thermodynamic response functions
+
+	\normalsize 
 \section{Introduction}
@@
 	\label{def:mod_morse}
-	U(r) & = & \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} \right.
-	\nonumber\\
-	&& + \left. {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
+	U(r) & = & \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha}  +  {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
 \end{eqnarray}
@@
 The quantities in the left-hand side of the equation are $P$, the pressure; $\beta = (k_{\rm B} T)^{-1}$, the inverse temperature; $k_{\rm B}$, the Boltzmann constant; $T$, the temperature; $v$, cell volume.
-The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential $\mu$.
+The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential~$\mu$.
 Let us present their expressions explicitly.
@@
 	\label{params}
-	\chi_0 = 0.07, & \quad \gamma = 1.65, \nonumber\\
-	n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \nonumber\\
-	\alpha^* = 5.0 & \quad p = 1.0.
+	&& \chi_0 = 0.07,  \quad \gamma = 1.65, \nonumber\\
+	&& n_0 = 1.521,  \quad R_0/\alpha = 2.9544, \nonumber\\
+	&& \alpha^* = 5.0  \qquad p = 1.0.
 \end{eqnarray}
@@
 \begin{eqnarray}\label{eq:E_mu}
-	E_\mu (M, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  
-	\nonumber\\
-	&& +  g_0 - \frac{\beta W(0)}{2} 
+	E_\mu (M, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}   +  g_0 - \frac{\beta W(0)}{2} 
 	\left(\frac{\tilde\mu}{W(0)} \right)^{2} 
@@
 	\label{eq:eosPTM_reduced}
-	P^* & = & (1 + \tau)T^*_c \bigg[ E_\mu(M, T) 
-	\nonumber\\
-	&& + M \bar \rho_0 + \frac{1}{2} d \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4
+	P^* & = & (1 + \tau)T^*_c \bigg[ E_\mu(M, T)  + M \bar \rho_0 + \frac{1}{2} d \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4
 	\bigg].
@@
 \begin{eqnarray}\label{eq:E_nu}
-	E_\rho (\rho^*, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0 
-	\nonumber\\
-	&& - \frac{\beta W(0)}{2} 
+	E_\rho (\rho^*, T) & = & - \frac{\ln (2\pi \beta W(0))}{2 N_v}  +  g_0  - \frac{\beta W(0)}{2} 
 	\left(\bar{M} - g_1 + \frac{g_3}{g_4} d + \frac{g_3^3}{6g_4^2} \right)^{2} 
@@
 	\label{eq:eosPTn_reduced}
-	P^* & = & (1 + \tau)T^*_c \bigg[ E_\rho (\rho^*,T) 
-	\nonumber\\
-	&& + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\bigg].
+	P^* & = & (1 + \tau)T^*_c \bigg[ E_\rho (\rho^*,T)  + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4\bigg].
 \end{eqnarray}
@@
 \begin{figure}[h!]
-	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
+	\centering
+	\includegraphics[width=0.45\textwidth]{f1a1.pdf} 
 	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
@@
 	%\includegraphics[width=\column]{f1b1.pdf}
-	\vskip-3mm
+%	\vskip-3mm	
+    \captionsetup{width=0.9\textwidth}
 	\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines.
@@
 \begin{figure}[htbp]
-	\includegraphics[width=0.5\textwidth]{f2a.pdf}
+	\centering
+	\includegraphics[width=0.465\textwidth]{f2a.pdf}
 	%\includegraphics[width=\column]{f2a}
-	\vskip-3mm
+    \captionsetup{width=0.9\textwidth}
 	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
@@
 \begin{figure}[h!] 
+	\centering
 	\includegraphics[width=0.45\textwidth]{f2b.pdf}
-	\includegraphics[width=0.475\textwidth]{f2c.pdf}
+	\includegraphics[width=0.461\textwidth]{f2c.pdf}
 	%\includegraphics[width=\column]{f2b.pdf}
 	%\includegraphics[width=\column]{f2c.pdf}
-	\vskip-3mm
+	\captionsetup{width=0.9\textwidth}
 	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
@@
 \begin{figure}[h!] 
-	\includegraphics[width=0.5\textwidth]{f3a.pdf}
+	\centering
+	\includegraphics[width=0.45\textwidth]{f3a.pdf}
 	%\includegraphics[width=\column]{f3a.pdf}
-	\vskip-3mm
+	\captionsetup{width=0.9\textwidth}
 	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$).
@@
 \begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{f3b.pdf}
+	\centering
+	\includegraphics[width=0.45\textwidth]{f3b.pdf}
 	%\includegraphics[width=\column]{f3b.pdf}
-	\vskip-3mm
+	\captionsetup{width=0.9\textwidth}
 	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
@@
 \begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{f3c.pdf}
+	\centering
+	\includegraphics[width=0.45\textwidth]{f3c.pdf}
 	%\includegraphics[width=\column]{f3c.pdf}
-	\vskip-3mm
+	\captionsetup{width=0.9\textwidth}
 	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
@@
 \begin{figure}[h!] 
-	\includegraphics[width=0.5\textwidth]{f4a.pdf}
+	\centering
+	\includegraphics[width=0.45\textwidth]{f4a.pdf}
 	%\includegraphics[width=\column]{f4a.pdf}
-	\vskip-3mm
+	\captionsetup{width=0.9\textwidth}
 	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
@@
 \begin{figure}[h!]
+	\centering
 	\includegraphics[width=0.45\textwidth]{f4b.pdf}
-	\includegraphics[width=0.475\textwidth]{f4c.pdf}
+	\includegraphics[width=0.471\textwidth]{f4c.pdf}
 	%\includegraphics[width=\column]{f4b.pdf}
 	%\includegraphics[width=\column]{f4c.pdf}
-	\vskip-3mm
+	\captionsetup{width=0.9\textwidth}
 	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$.
@@
 	\frac{\partial E_\rho}{\partial \tau} & = &  -\frac{1}{2}\left(\bar{M} - g_1 + \frac{g_3}{g_4} d + \frac{g_3^3}{6g_4^2} \right)^{2} 
-	\frac{\partial \beta W(0)}{\partial \tau} 
+	\frac{\partial \beta W(0)}{\partial \tau} -\beta W(0)\left(\bar{M} - g_1 + \frac{g_3}{g_4} d + \frac{g_3^3}{6g_4^2} \right)
 	\nonumber\\
-	&&-\beta W(0)\left(\bar{M} - g_1 + \frac{g_3}{g_4} d + \frac{g_3^3}{6g_4^2} \right)
-	\nonumber\\
-	&& \times \left(\frac{\partial \bar{M}}{\partial \tau} + \frac{g_3}{g_4}\frac{\partial d}{\partial \tau}\right)
-	\nonumber\\
-	&& -\frac{g_3}{g_4}\frac{\partial \bar{M}}{\partial \tau} 
+	&& \times \left(\frac{\partial \bar{M}}{\partial \tau} + \frac{g_3}{g_4}\frac{\partial d}{\partial \tau}\right) -\frac{g_3}{g_4}\frac{\partial \bar{M}}{\partial \tau} 
 	- \frac{g_3^2}{2g_4^2}\frac{\partial d}{\partial \tau}.
@@
 \begin{eqnarray}
-	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
-	\nonumber\\
-	&& + (1+\tau) \left(\frac{\partial E_{\rho}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial d}{\partial \tau}\right).
+	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4 + (1+\tau) \left(\frac{\partial E_{\rho}}{\partial \tau} + \frac{\partial \bar{M}}{\partial \tau}\rho_{n} + \frac{\rho_n^2}{2}\frac{\partial d}{\partial \tau}\right).
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4
-	\nonumber\\
-	& + & \left\{ \frac{\beta}{2}  \Phi^{(r)}(0) [B - 1 - A_\gamma]	G_M^2 \right . \nonumber \\
-	& + & \left. \frac{1}{\beta W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0} \left[ \frac{g_3^2}{2 g_4^2} + \frac{\rho_n^2}{2} - \frac{g_3}{g_4} \rho_n  \right . \right . \nonumber \\
-	& + & \left. \left. \beta W(0) G_M \left( \frac{g_3}{g_4} - \rho_n \right)    \right] \right\},
+	\beta^*_V & = & E_\rho (\rho^*,T) + \bar{M} \rho_{n} + \frac{d}{2} \rho_{n}^2 - \frac{a_4}{24} \rho_{n}^4 +  \left\{ \frac{\beta}{2}  \Phi^{(r)}(0) [B - 1 - A_\gamma]	G_M^2 \right . \nonumber \\
+	& + & \left.
+\frac{1}{\beta W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0} \left[ \frac{g_3^2}{2 g_4^2} + \frac{\rho_n^2}{2} - \frac{g_3}{g_4} \rho_n  +  \beta W(0) G_M \left( \frac{g_3}{g_4} - \rho_n \right)    \right] \right\},
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\kappa_T^* & = & \frac{\epsilon}{\rho^{*2} W(0)} \bigg\{ -1
-	\\
-	& + & \left. \frac{Q_t^{-1/2}}{\beta W(0) g_4} \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right]\right\}.
-	\nonumber
+	\kappa_T^* & = & \frac{\epsilon}{\rho^{*2} W(0)} \left\{   \frac{Q_t^{-1/2}}{\beta W(0) g_4} \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right] -1 \right\}.
 \end{eqnarray}
@@
 
-	\bibitem{MartinezValenciaEtAl2013} A.~Martínez-Valencia, M.~González-Melchor, P.~Orea, J.~López-Lemus.
+	\bibitem{MartinezValenciaEtAl2013} A.~Mart?nez-Valencia, M.~Gonz?lez-Melchor, P.~Orea, J.~L?pez-Lemus.
 	\href{https://doi.org/10.1080/08927022.2012.702422}{Liquid–vapour interface
@@
 \end{thebibliography}
+
+\end{document}

### 2024-09-15 paper_text.tex
add ISBN to the Johnston book on vdW fluids

@@
 	\bibitem{Johnston2014book} D.C.~Johnston.
-	\textit{\href{https://dx.doi.org/10.1088/978-1-627-05532-1}{Advances in Thermodynamics of the van der {W}aals Fluid.}} (Morgan \& Claypool Publishers, 2014) [doi: 10.1088/978-1-627-05532-1]
+	\textit{\href{https://dx.doi.org/10.1088/978-1-627-05532-1}{Advances in Thermodynamics of the van der {W}aals Fluid.}} (Morgan \& Claypool Publishers, 2014) [doi: 10.1088/978-1-627-05532-1][ISBN: 978-1-627-05532-1]
 
